### 2023-06-09 paper.tex
html and pdf render for template file

% !TeX root = RJwrapper.tex
\title{ToOoOlTiPs: An R Package for Customizable Tooltips in Interactive Graphics}
\author{by Quietest Quokka and Bounciest Bilby}

\maketitle

\abstract{%
An abstract of less than 150 words.
}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Interactive data graphics provides plots that allow users to interact them. One of the most basic types of interaction is through tooltips, where users are provided additional information about elements in the plot by moving the cursor over the plot.

This paper will first review some R packages on interactive graphics and their tooltip implementations. A new package \CRANpkg{ToOoOlTiPs} that provides customized tooltips for plot, is introduced. Some example plots will then be given to showcase how these tooltips help users to better read the graphics.

\hypertarget{background}{%
\section{Background}\label{background}}

Some packages on interactive graphics include \CRANpkg{plotly} (Sievert 2020) that interfaces with Javascript for web-based interactive graphics, \CRANpkg{crosstalk} (Cheng and Sievert 2021) that specializes cross-linking elements across individual graphics. The recent R Journal paper \CRANpkg{tsibbletalk} (Wang and Cook 2021) provides a good example of including interactive graphics into an article for the journal. It has both a set of linked plots, and also an animated gif example, illustrating linking between time series plots and feature summaries.

\hypertarget{customizing-tooltip-design-with}{%
\section{\texorpdfstring{Customizing tooltip design with \pkg{ToOoOlTiPs}}{Customizing tooltip design with }}\label{customizing-tooltip-design-with}}

\pkg{ToOoOlTiPs} is a packages for customizing tooltips in interactive graphics, it features these possibilities.

\hypertarget{a-gallery-of-tooltips-examples}{%
\section{A gallery of tooltips examples}\label{a-gallery-of-tooltips-examples}}

The \CRANpkg{palmerpenguins} data (Horst, Hill, and Gorman 2020) features three penguin species which has a lovely illustration by Alison Horst in Figure \ref{fig:penguins-alison}.

\begin{figure}
\includegraphics[width=1\linewidth,height=0.3\textheight]{penguins} \caption{Artwork by \@allison\_horst}\label{fig:penguins-alison}
\end{figure}

Table \ref{tab:penguins-tab-static} prints at the first few rows of the \texttt{penguins} data:

\begin{table}

\caption{\label{tab:penguins-tab-static}A basic table}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l|l|r|r|r|r|l|r}
\hline
species & island & bill\_length\_mm & bill\_depth\_mm & flipper\_length\_mm & body\_mass\_g & sex & year\\
\hline
Adelie & Torgersen & 39.1 & 18.7 & 181 & 3750 & male & 2007\\
\hline
Adelie & Torgersen & 39.5 & 17.4 & 186 & 3800 & female & 2007\\
\hline
Adelie & Torgersen & 40.3 & 18.0 & 195 & 3250 & female & 2007\\
\hline
Adelie & Torgersen & NA & NA & NA & NA & NA & 2007\\
\hline
Adelie & Torgersen & 36.7 & 19.3 & 193 & 3450 & female & 2007\\
\hline
Adelie & Torgersen & 39.3 & 20.6 & 190 & 3650 & male & 2007\\
\hline
\end{tabular}
\end{table}

Figure \ref{fig:penguins-ggplot} shows an plot of the penguins data, made using the \CRANpkg{ggplot2} package.

\begin{verbatim}
penguins %>% 
  ggplot(aes(x = bill_depth_mm, y = bill_length_mm, 
             color = species)) + 
  geom_point()
\end{verbatim}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/penguins-ggplot-1.pdf}
\caption{\label{fig:penguins-ggplot}A basic non-interactive plot made with the ggplot2 package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. Visit the online article to access the interactive version made with the plotly package.}
\end{figure}

\hypertarget{summary}{%
\section{Summary}\label{summary}}

We have displayed various tooltips that are available in the package \pkg{ToOoOlTiPs}.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-crosstalk}{}}%
Cheng, Joe, and Carson Sievert. 2021. \emph{{crosstalk}: Inter-Widget Interactivity for HTML Widgets}. \url{https://CRAN.R-project.org/package=crosstalk}.

\leavevmode\vadjust pre{\hypertarget{ref-palmerpenguins}{}}%
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020. \emph{{palmerpenguins}: Palmer Archipelago (Antarctica) Penguin Data}. \url{https://allisonhorst.github.io/palmerpenguins/}.

\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
Sievert, Carson. 2020. \emph{{Interactive Web-Based Data Visualizatio}n with r, Plotly, and Shiny}. Chapman; Hall/CRC. \url{https://plotly-r.com}.

\leavevmode\vadjust pre{\hypertarget{ref-RJ-2021-050}{}}%
Wang, Earo, and Dianne Cook. 2021. {``Conversations in Time: Interactive Visualisation to Explore Structured Temporal Data.''} \emph{The R Journal}. \url{https://doi.org/10.32614/RJ-2021-050}.

\end{CSLReferences}

\bibliography{RJreferences.bib}

\address{%
Quietest Quokka\\
University of Little Mates\\%
Department of Letter Q\\ Somewhere, Australia\\
%
\url{https://www.britannica.com/animal/quokka}\\%
\textit{ORCiD: \href{https://orcid.org/0000-1721-1511-1101}{0000-1721-1511-1101}}\\%
\href{mailto:qquo@ulm.edu}{\nolinkurl{qquo@ulm.edu}}%
}

\address{%
Bounciest Bilby\\
University of Little Mates\\%
Department of Letter B\\ Somewhere, Australia\\
%
\url{https://www.britannica.com/animal/bilby}\\%
\textit{ORCiD: \href{https://orcid.org/0000-0002-0912-0225}{0000-0002-0912-0225}}\\%
\href{mailto:bbil@ulm.edu}{\nolinkurl{bbil@ulm.edu}}%
}

### 2023-06-09 paper.R

@@ -1,0 +1,37 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit paper.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+library(plotly)
+library(ggplot2)
+library(palmerpenguins)
+
+
+## ----penguins-alison, out.width = "100%", out.height = "30%", fig.cap = "Artwork by \\@allison\\_horst", fig.alt="A picture of three different penguins with their species: Chinstrap, Gentoo, and Adelie. "----
+knitr::include_graphics("penguins.png")
+
+
+## ----penguins-tab-interactive, eval = knitr::is_html_output(), layout = "l-body-outset"----
+#> knitr::kable(head(penguins), format = "html", caption = "A basic table")
+
+
+## ----penguins-tab-static, eval = knitr::is_latex_output()---------------------
+knitr::kable(head(penguins), format = "latex", caption = "A basic table") %>% 
+  kableExtra::kable_styling(font_size = 7)
+
+
+## ----penguins-plotly, echo = TRUE, fig.height = 5, fig.cap="A basic interactive plot made with the plotly package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. When hovering on a point, a tooltip will show the exact value of the bill depth and length for that point, along with the species name.", include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.alt = "A scatterplot of bill length against bill depth, both measured in millimetre. The three species are shown in different colours and loosely forms three clusters. Adelie has small bill length and large bill depth, Gentoo has small bill depth but large bill length, and Chinstrap has relatively large bill depth and bill length."----
+#> p <- penguins %>%
+#>   ggplot(aes(x = bill_depth_mm, y = bill_length_mm,
+#>              color = species)) +
+#>   geom_point()
+#> ggplotly(p)
+
+
+## ----penguins-ggplot, echo = TRUE, fig.height = 5, fig.cap="A basic non-interactive plot made with the ggplot2 package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. Visit the online article to access the interactive version made with the plotly package.", include=knitr::is_latex_output(), eval=knitr::is_latex_output()----
+penguins %>% 
[…]

### 2023-06-12 paper.Rmd
initial draft of intro

---
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
date: "`r Sys.Date()`"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Marcus W. Beck
    affiliation: Tampa Bay Estuary Program
    address:
    - 263 13th Ave S
    - St. Petersburg, Florida, USA 33701
    url: https://tbep.org
    orcid: 0000-0002-4996-0059
    email:  mbeck@tbep.org
  - name: Benjamen Wetherill
    url: https://www.acasak.com/
    email: bwetherill@acasak.co
    affiliation: ACASAK Consulting
    address:
    - Boston, Massachusetts, USA
    orcid: 0000-0002-0912-0225
  - name: Jillian Carr
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: Jillian.Carr@umb.edu
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
  - name: Pamela DiBona
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: pamela.dibona@state.ma.us
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
```

# Introduction

Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources. In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of surface waters.  Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance. These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected ad hoc from a variety of sources, where the former is atypical for most surface water bodies.  Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest. Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.

Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.  A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database. Common QC checks for in situ field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).  An adequate number of QC samples must also be included in the dataset as a measure of "completeness".  These checks are often compiled in a single report for comparison to applicable standards.  For example, precision of duplicate samples for a given parameter must not vary 10%.   For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review by the appropriate regulatory agency.  This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.

The R statistical programming language offers a valuable software infrastructure for developing tools to improve the QC of water quality data.  The use of R with document generation systems offered through packages like \CRANpkg{knitr} and \CRANpkg{rmarkdown} can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.  These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.  This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements.  Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} offer insightful approaches to visualize numerous water quality records in a single graph. Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.

This paper describes the MassWateR package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.  The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to Massachusetts Department of Environmental Protection and data submitted to the national WQX database.  Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses are applied universally to data collected at locations elsewhere.  As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of imported water quality data and submission to WQX as the largest source of water monitoring data in the US.

# Background

To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data.  However, there are several that can be used to retrieve and analysis data from existing sources.  The \CRANpkg{dataRetrieval} package in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.

Existing workflows or packages

Good tools for data extraction - dataRetrieval, NADA package, https://cran.r-project.org/web/views/Hydrology.html

Building the community of practice...

# Requirements for using MassWateR

Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort

# Read

# Quality Control

# Analysis

# Data submission

# Building a community and future work

MassWater in other locations, expansion elsewhere

Inclusion of historical data

Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.

# Summary

# Acknowledgments

### 2023-06-12 paper.tex
initial draft of intro

@@
 % !TeX root = RJwrapper.tex
-\title{ToOoOlTiPs: An R Package for Customizable Tooltips in Interactive Graphics}
-\author{by Quietest Quokka and Bounciest Bilby}
+\title{MassWateR: Improving quality control, analysis, and sharing of water quality data}
+\author{by Marcus W. Beck, Benjamen Wetherill, Jillian Carr, and Pamela DiBona}
 
@@
 
-Interactive data graphics provides plots that allow users to interact them.
-One of the most basic types of interaction is through tooltips, where users are provided additional information about elements in the plot by moving the cursor over the plot.
+Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
+In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of surface waters.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
+These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected ad hoc from a variety of sources, where the former is atypical for most surface water bodies.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest.
+Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
 
-This paper will first review some R packages on interactive graphics and their tooltip implementations.
-A new package \CRANpkg{ToOoOlTiPs} that provides customized tooltips for plot, is introduced.
-Some example plots will then be given to showcase how these tooltips help users to better read the graphics.
+Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
+Common QC checks for in situ field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
+An adequate number of QC samples must also be included in the dataset as a measure of ``completeness''.
+These checks are often compiled in a single report for comparison to applicable standards.
+For example, precision of duplicate samples for a given parameter must not vary 10\%.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review by the appropriate regulatory agency.
+This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
+
+The R statistical programming language offers a valuable software infrastructure for developing tools to improve the QC of water quality data.
+The use of R with document generation systems offered through packages like \CRANpkg{knitr} and \CRANpkg{rmarkdown} can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
+These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.
+This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements.
+Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} offer insightful approaches to visualize numerous water quality records in a single graph.
+Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
+
+This paper describes the MassWateR package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
+The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
+Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses are applied universally to data collected at locations elsewhere.
+As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of imported water quality data and submission to WQX as the largest source of water monitoring data in the US.
 
@@
 
-Some packages on interactive graphics include \CRANpkg{plotly} (Sievert 2020) that interfaces with Javascript for web-based interactive graphics, \CRANpkg{crosstalk} (Cheng and Sievert 2021) that specializes cross-linking elements across individual graphics.
-The recent R Journal paper \CRANpkg{tsibbletalk} (Wang and Cook 2021) provides a good example of including interactive graphics into an article for the journal.
-It has both a set of linked plots, and also an animated gif example, illustrating linking between time series plots and feature summaries.
+To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data.
+However, there are several that can be used to retrieve and analysis data from existing sources.
+The \CRANpkg{dataRetrieval} package in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
 
-\hypertarget{customizing-tooltip-design-with}{%
-\section{\texorpdfstring{Customizing tooltip design with \pkg{ToOoOlTiPs}}{Customizing tooltip design with }}\label{customizing-tooltip-design-with}}
+Existing workflows or packages
 
-\pkg{ToOoOlTiPs} is a packages for customizing tooltips in interactive graphics, it features these possibilities.
+Good tools for data extraction - dataRetrieval, NADA package, \url{https://cran.r-project.org/web/views/Hydrology.html}
 
-\hypertarget{a-gallery-of-tooltips-examples}{%
-\section{A gallery of tooltips examples}\label{a-gallery-of-tooltips-examples}}
+Building the community of practice\ldots{}
 
-The \CRANpkg{palmerpenguins} data (Horst, Hill, and Gorman 2020) features three penguin species which has a lovely illustration by Alison Horst in Figure \ref{fig:penguins-alison}.
+\hypertarget{requirements-for-using-masswater}{%
+\section{Requirements for using MassWateR}\label{requirements-for-using-masswater}}
 
-\begin{figure}
-\includegraphics[width=1\linewidth,height=0.3\textheight]{penguins} \caption{Artwork by \@allison\_horst}\label{fig:penguins-alison}
-\end{figure}
+Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
 
-Table \ref{tab:penguins-tab-static} prints at the first few rows of the \texttt{penguins} data:
+\hypertarget{read}{%
+\section{Read}\label{read}}
 
-\begin{table}
+\hypertarget{quality-control}{%
+\section{Quality Control}\label{quality-control}}
 
-\caption{\label{tab:penguins-tab-static}A basic table}
-\centering
-\fontsize{7}{9}\selectfont
-\begin{tabular}[t]{l|l|r|r|r|r|l|r}
-\hline
-species & island & bill\_length\_mm & bill\_depth\_mm & flipper\_length\_mm & body\_mass\_g & sex & year\\
-\hline
-Adelie & Torgersen & 39.1 & 18.7 & 181 & 3750 & male & 2007\\
-\hline
-Adelie & Torgersen & 39.5 & 17.4 & 186 & 3800 & female & 2007\\
-\hline
-Adelie & Torgersen & 40.3 & 18.0 & 195 & 3250 & female & 2007\\
-\hline
-Adelie & Torgersen & NA & NA & NA & NA & NA & 2007\\
-\hline
-Adelie & Torgersen & 36.7 & 19.3 & 193 & 3450 & female & 2007\\
-\hline
-Adelie & Torgersen & 39.3 & 20.6 & 190 & 3650 & male & 2007\\
-\hline
-\end{tabular}
-\end{table}
+\hypertarget{analysis}{%
+\section{Analysis}\label{analysis}}
 
-Figure \ref{fig:penguins-ggplot} shows an plot of the penguins data, made using the \CRANpkg{ggplot2} package.
+\hypertarget{data-submission}{%
+\section{Data submission}\label{data-submission}}
 
-\begin{verbatim}
-penguins %>% 
-  ggplot(aes(x = bill_depth_mm, y = bill_length_mm, 
-             color = species)) + 
-  geom_point()
-\end{verbatim}
+\hypertarget{building-a-community-and-future-work}{%
+\section{Building a community and future work}\label{building-a-community-and-future-work}}
 
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/penguins-ggplot-1.pdf}
-\caption{\label{fig:penguins-ggplot}A basic non-interactive plot made with the ggplot2 package on palmer penguin data.
-Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis.
-Visit the online article to access the interactive version made with the plotly package.}
-\end{figure}
+MassWater in other locations, expansion elsewhere
+
+Inclusion of historical data
+
+Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.
 
@@
 
-We have displayed various tooltips that are available in the package \pkg{ToOoOlTiPs}.
+\hypertarget{acknowledgments}{%
+\section{Acknowledgments}\label{acknowledgments}}
 
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-crosstalk}{}}%
-Cheng, Joe, and Carson Sievert. 2021. \emph{{crosstalk}: Inter-Widget Interactivity for HTML Widgets}. \url{https://CRAN.R-project.org/package=crosstalk}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmerpenguins}{}}%
-Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020. \emph{{palmerpenguins}: Palmer Archipelago (Antarctica) Penguin Data}. \url{https://allisonhorst.github.io/palmerpenguins/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-plotly}{}}%
-Sievert, Carson. 2020. \emph{{Interactive Web-Based Data Visualizatio}n with r, Plotly, and Shiny}. Chapman; Hall/CRC. \url{https://plotly-r.com}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RJ-2021-050}{}}%
-Wang, Earo, and Dianne Cook. 2021. {``Conversations in Time: Interactive Visualisation to Explore Structured Temporal Data.''} \emph{The R Journal}. \url{https://doi.org/10.32614/RJ-2021-050}.
-
-\end{CSLReferences}
+\section{References}\label{references}}
 
@@
 \address{%
-Quietest Quokka\\
-University of Little Mates\\%
-Department of Letter Q\\ Somewhere, Australia\\
+Marcus W. Beck\\
+Tampa Bay Estuary Program\\%
+263 13th Ave S\\ St.~Petersburg, Florida, USA 33701\\
 %
-\url{https://www.britannica.com/animal/quokka}\\%
-\textit{ORCiD: \href{https://orcid.org/0000-1721-1511-1101}{0000-1721-1511-1101}}\\%
-\href{mailto:qquo@ulm.edu}{\nolinkurl{qquo@ulm.edu}}%
+\url{https://tbep.org}\\%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-4996-0059}{0000-0002-4996-0059}}\\%
+\href{mailto:mbeck@tbep.org}{\nolinkurl{mbeck@tbep.org}}%
 }
@@
 \address{%
-Bounciest Bilby\\
-University of Little Mates\\%
-Department of Letter B\\ Somewhere, Australia\\
+Benjamen Wetherill\\
+ACASAK Consulting\\%
+Boston, Massachusetts, USA\\
 %
-\url{https://www.britannica.com/animal/bilby}\\%
+\url{https://www.acasak.com/}\\%
 \textit{ORCiD: \href{https://orcid.org/0000-0002-0912-0225}{0000-0002-0912-0225}}\\%
-\href{mailto:bbil@ulm.edu}{\nolinkurl{bbil@ulm.edu}}%
+\href{mailto:bwetherill@acasak.co}{\nolinkurl{bwetherill@acasak.co}}%
 }
+
+\address{%
+Jillian Carr\\
+Massachusetts Bays National Estuary Partnership\\%
+University of Massachusetts Boston, 100 Morrissey Blvd\\ Boston, Massachusetts, USA 02125\\
+%
+\url{https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership}\\%
+%
+\href{mailto:Jillian.Carr@umb.edu}{\nolinkurl{Jillian.Carr@umb.edu}}%
+}
+
+\address{%
+Pamela DiBona\\
+Massachusetts Bays National Estuary Partnership\\%
+University of Massachusetts Boston, 100 Morrissey Blvd\\ Boston, Massachusetts, USA 02125\\
+%
+\url{https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership}\\%
+%
+\href{mailto:pamela.dibona@state.ma.us}{\nolinkurl{pamela.dibona@state.ma.us}}%
+}

### 2023-06-12 paper.R

@@ -3,35 +3,5 @@
 
 ## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-library(plotly)
-library(ggplot2)
-library(palmerpenguins)
-
-
-## ----penguins-alison, out.width = "100%", out.height = "30%", fig.cap = "Artwork by \\@allison\\_horst", fig.alt="A picture of three different penguins with their species: Chinstrap, Gentoo, and Adelie. "----
-knitr::include_graphics("penguins.png")
-
-
-## ----penguins-tab-interactive, eval = knitr::is_html_output(), layout = "l-body-outset"----
-#> knitr::kable(head(penguins), format = "html", caption = "A basic table")
-
-
-## ----penguins-tab-static, eval = knitr::is_latex_output()---------------------
-knitr::kable(head(penguins), format = "latex", caption = "A basic table") %>% 
-  kableExtra::kable_styling(font_size = 7)
-
-
-## ----penguins-plotly, echo = TRUE, fig.height = 5, fig.cap="A basic interactive plot made with the plotly package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. When hovering on a point, a tooltip will show the exact value of the bill depth and length for that point, along with the species name.", include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.alt = "A scatterplot of bill length against bill depth, both measured in millimetre. The three species are shown in different colours and loosely forms three clusters. Adelie has small bill length and large bill depth, Gentoo has small bill depth but large bill length, and Chinstrap has relatively large bill depth and bill length."----
-#> p <- penguins %>%
-#>   ggplot(aes(x = bill_depth_mm, y = bill_length_mm,
-#>              color = species)) +
-#>   geom_point()
-#> ggplotly(p)
-
-
-## ----penguins-ggplot, echo = TRUE, fig.height = 5, fig.cap="A basic non-interactive plot made with the ggplot2 package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. Visit the online article to access the interactive version made with the plotly package.", include=knitr::is_latex_output(), eval=knitr::is_latex_output()----
-penguins %>% 
-  ggplot(aes(x = bill_depth_mm, y = bill_length_mm, 
-             color = species)) + 
-  geom_point()
+library(MassWateR)
 

### 2023-06-13 paper.Rmd
adding some refs to intro

@@
 
-Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
-In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of surface waters.
+Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources [@Schiff16].
+In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+Similarly, the Water Framework Directive adopted in 2000 provides a framework for the protection of aquatic resources in member states of the European Union.
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
-These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected ad hoc from a variety of sources, where the former is atypical for most surface water bodies.
+These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected *ad hoc* from a variety of sources, where the former is atypical for most surface water bodies.
 Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest.
@@
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
-Common QC checks for in situ field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
+Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
 An adequate number of QC samples must also be included in the dataset as a measure of "completeness".
-These checks are often compiled in a single report for comparison to applicable standards.
-For example, precision of duplicate samples for a given parameter must not vary 10%.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review by the appropriate regulatory agency.
-This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
+These checks are often compiled in a single report for review by appropriate regulatory agencies.
+For example, precision of duplicate samples for a given parameter must not vary 5% and at least 10% of the data should be dedicated to these checks as a measure of completeness.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review  This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
 
-The R statistical programming language offers a valuable software infrastructure for developing tools to improve the QC of water quality data.
-The use of R with document generation systems offered through packages like \CRANpkg{knitr} and \CRANpkg{rmarkdown} can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
+The R statistical programming language offers a valuable software platform for developing tools to improve the QC of water quality data.
+The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.
-This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements.
-Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} offer insightful approaches to visualize numerous water quality records in a single graph.
+This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
+Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] offer useful approaches to visualize numerous water quality records in a single graph.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
@@
 This paper describes the MassWateR package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
-The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
-Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses are applied universally to data collected at locations elsewhere.
-As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of imported water quality data and submission to WQX as the largest source of water monitoring data in the US.
+The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
+Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected at locations elsewhere.
+As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water monitoring data in the US.
 
@@
 However, there are several that can be used to retrieve and analysis data from existing sources.
-The \CRANpkg{dataRetrieval} package in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+The \CRANpkg{dataRetrieval} package [@DeCicco22] in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
 

### 2023-06-13 paper.tex
adding some refs to intro

@@
 
-Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
-In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of surface waters.
+Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources (Schiff et al.
+2016).
+In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+Similarly, the Water Framework Directive adopted in 2000 provides a framework for the protection of aquatic resources in member states of the European Union.
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
-These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected ad hoc from a variety of sources, where the former is atypical for most surface water bodies.
+These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected \emph{ad hoc} from a variety of sources, where the former is atypical for most surface water bodies.
 Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest.
@@
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
-Common QC checks for in situ field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
+Common QC checks for \emph{in situ} field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
 An adequate number of QC samples must also be included in the dataset as a measure of ``completeness''.
-These checks are often compiled in a single report for comparison to applicable standards.
-For example, precision of duplicate samples for a given parameter must not vary 10\%.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review by the appropriate regulatory agency.
-This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
+These checks are often compiled in a single report for review by appropriate regulatory agencies.
+For example, precision of duplicate samples for a given parameter must not vary 5\% and at least 10\% of the data should be dedicated to these checks as a measure of completeness.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
 
-The R statistical programming language offers a valuable software infrastructure for developing tools to improve the QC of water quality data.
-The use of R with document generation systems offered through packages like \CRANpkg{knitr} and \CRANpkg{rmarkdown} can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
+The R statistical programming language offers a valuable software platform for developing tools to improve the QC of water quality data.
+The use of R with document generation systems offered through packages like \CRANpkg{knitr} (Xie 2015) and \CRANpkg{rmarkdown} (Allaire et al.
+2023) can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.
-This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements.
-Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} offer insightful approaches to visualize numerous water quality records in a single graph.
+This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
+Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} (Wickham 2016) offer useful approaches to visualize numerous water quality records in a single graph.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
@@
 However, there are several that can be used to retrieve and analysis data from existing sources.
-The \CRANpkg{dataRetrieval} package in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+The \CRANpkg{dataRetrieval} package (De Cicco et al.
+2022) in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
 
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Allaire23}{}}%
+Allaire, JJ, Yihui Xie, Christophe Dervieux, Jonathan McPherson, Javier Luraschi, Kevin Ushey, Aron Atkins, et al.
+2023.
+\emph{Rmarkdown: Dynamic Documents for r}.
+\url{https://github.com/rstudio/rmarkdown}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-DeCicco22}{}}%
+De Cicco, Laura A., David Lorenz, Robert M.
+Hirsch, William Watkins, and Mike Johnson.
+2022.
+\emph{dataRetrieval: R Packages for Discovering and Retrieving Water Data Available from u.s.
+Federal Hydrologic Web Services} (version 2.7.12).
+Reston, VA: U.S.
+Geological Survey; U.S.
+Geological Survey.
+\url{https://doi.org/10.5066/P9X4L3GE}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schiff16}{}}%
+Schiff, Ken, PR Trowbridge, ET Sherwood, Peter Tango, and Rich A Batiuk.
+2016.
+{``Regional Monitoring Programs in the United States: Synthesis of Four Case Studies from Pacific, Atlantic, and Gulf Coasts.''} \emph{Regional Studies in Marine Science} 4: A1--7.
+\url{https://doi.org/10.1016/j.rsma.2015.11.007}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham16}{}}%
+Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Xie15}{}}%
+Xie, Yihui. 2015. \emph{Dynamic Documents with {R} and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{https://yihui.org/knitr/}.
+
+\end{CSLReferences}
 

### 2023-06-14 paper.Rmd
adding refs to intro, working on package requirements

@@
 
-Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources [@Schiff16].
-In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive adopted in 2000 provides a framework for the protection of aquatic resources in member states of the European Union.
+Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
+In the United States, water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
-These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected *ad hoc* from a variety of sources, where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest.
+These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets [@Schiff16; @Tango13], or data collected *ad hoc* from multiple assessment endpoints [@Stein09; @Behmel16; @Kumpel20], where the former is atypical for most surface water bodies.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest [@Buytaert14; Kelly22].
 Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
@@
 The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
-These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.
+These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
@@
 
-# Background
+# Requirements for using \CRANpkg{MassWateR}
 
-To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data.
-However, there are several that can be used to retrieve and analysis data from existing sources.
-The \CRANpkg{dataRetrieval} package [@DeCicco22] in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
+However, there are several that can be used to retrieve and analysis data from existing sources (see the CRAN \ctv{Hydrology} Task View).
+In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+This package leverages a robust API to query existing water quality data in the WQP.
+As such, data retrieval using existing web services is much simpler than data submission to a similar resource, as data formatting requirements do not apply when retrieving data.
+Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like \CRANpkg{dataRetrieval} by increasing the amount of data that can be accessed through the WQP.
+The \CRANpkg{MassWateR} package was developed to provide this benefit.
 
-Existing workflows or packages
+Users can engage with \CRANpkg{MassWateR} to achieve different goals.
+This design was purposeful based on likely differences in needs among the user community.
+Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
+That is, QC reporting is not a requirement to submit to WQX, whereas state institutions require it for regulatory assessment.
+Users may also simply have a need to understand trends or to summarize their data, while also wanted to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
+Figure xx demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
+The functions allow a user to engage with their data several, including 1) screening data for quality control, 2) summarizing quality control results, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
 
-Good tools for data extraction - dataRetrieval, NADA package, https://cran.r-project.org/web/views/Hydrology.html
-
-Building the community of practice...
-
-# Requirements for using MassWateR
-
+No matter the user need, all data inputs to MassWateR must follow a strict format.  
 Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
@@
 
+All developers hope that their package is used by the intended audience.  To ensure this for MassWateR, a community of practice was...
+
+Building the community of practice...
+
 MassWater in other locations, expansion elsewhere

### 2023-06-14 paper.tex
adding refs to intro, working on package requirements

@@
 
-Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources (Schiff et al.
-2016).
-In the United States, most water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive adopted in 2000 provides a framework for the protection of aquatic resources in member states of the European Union.
+Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
+In the United States, water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
-These standards are often developed at the state-level either using existing databases from long-term monitoring datasets, or data collected \emph{ad hoc} from a variety of sources, where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest.
+These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets (Schiff et al.
+2016; Tango and Batiuk 2013), or data collected \emph{ad hoc} from multiple assessment endpoints (Stein and Cadien 2009; Behmel et al.
+2016; Kumpel et al.
+2020), where the former is atypical for most surface water bodies.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest {[}Buytaert et al.
+(2014); Kelly22{]}.
 Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
@@
 2023) can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
-These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency.
+These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
@@
 
-\hypertarget{background}{%
-\section{Background}\label{background}}
+\hypertarget{requirements-for-using}{%
+\section{\texorpdfstring{Requirements for using \CRANpkg{MassWateR}}{Requirements for using }}\label{requirements-for-using}}
 
-To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data.
-However, there are several that can be used to retrieve and analysis data from existing sources.
-The \CRANpkg{dataRetrieval} package (De Cicco et al.
-2022) in particular has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
+However, there are several that can be used to retrieve and analysis data from existing sources (see the CRAN \ctv{Hydrology} Task View).
+In particular, the \CRANpkg{dataRetrieval} package (De Cicco et al.
+2022) has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+This package leverages a robust API to query existing water quality data in the WQP.
+As such, data retrieval using existing web services is much simpler than data submission to a similar resource, as data formatting requirements do not apply when retrieving data.
+Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like \CRANpkg{dataRetrieval} by increasing the amount of data that can be accessed through the WQP.
+The \CRANpkg{MassWateR} package was developed to provide this benefit.
 
-Existing workflows or packages
+Users can engage with \CRANpkg{MassWateR} to achieve different goals.
+This design was purposeful based on likely differences in needs among the user community.
+Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
+That is, QC reporting is not a requirement to submit to WQX, whereas state institutions require it for regulatory assessment.
+Users may also simply have a need to understand trends or to summarize their data, while also wanted to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
+Figure xx demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
+The functions allow a user to engage with their data several, including 1) screening data for quality control, 2) summarizing quality control results, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
 
-Good tools for data extraction - dataRetrieval, NADA package, \url{https://cran.r-project.org/web/views/Hydrology.html}
-
-Building the community of practice\ldots{}
-
-\hypertarget{requirements-for-using-masswater}{%
-\section{Requirements for using MassWateR}\label{requirements-for-using-masswater}}
-
+No matter the user need, all data inputs to MassWateR must follow a strict format.\\
 Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
@@
 \section{Building a community and future work}\label{building-a-community-and-future-work}}
+
+All developers hope that their package is used by the intended audience. To ensure this for MassWateR, a community of practice was\ldots{}
+
+Building the community of practice\ldots{}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Behmel16}{}}%
+Behmel, Sonja, Mathieu Damour, Ralf Ludwig, and MJ Rodriguez.
+2016.
+{``Water Quality Monitoring Strategies---a Review and Future Perspectives.''} \emph{Science of the Total Environment} 571: 1312--29.
+\url{https://doi.org/10.1016/j.scitotenv.2016.06.235}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Buytaert14}{}}%
+Buytaert, Wouter, Zed Zulkafli, Sam Grainger, Luis Acosta, Tilashwork C Alemie, Johan Bastiaensen, Bert De Bièvre, et al.
+2014.
+{``Citizen Science in Hydrology and Water Resources: Opportunities for Knowledge Generation, Ecosystem Service Management, and Sustainable Development.''} \emph{Frontiers in Earth Science} 2: 26.
+\url{https://doi.org/10.3389/feart.2014.00026}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-DeCicco22}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kumpel20}{}}%
+Kumpel, Emily, Clara MacLeod, Kara Stuart, Alicea Cock-Esteb, Ranjiv Khush, and Rachel Peletz.
+2020.
+{``From Data to Decisions: Understanding Information Flows Within Regulatory Water Quality Monitoring Programs.''} \emph{Npj Clean Water} 3 (1): 38.
+\url{https://doi.org/10.1038/s41545-020-00084-0}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Schiff16}{}}%
@@
 \url{https://doi.org/10.1016/j.rsma.2015.11.007}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stein09}{}}%
+Stein, Eric D, and Donald B Cadien.
+2009.
+{``Ecosystem Response to Regulatory and Management Actions: The Southern California Experience in Long-Term Monitoring.''} \emph{Marine Pollution Bulletin} 59 (4-7): 91--100.
+\url{https://doi.org/10.1016/j.marpolbul.2009.02.025}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tango13}{}}%
+Tango, Peter J, and Richard A Batiuk.
+2013.
+{``Deriving {C}hesapeake {B}ay Water Quality Standards.''} \emph{JAWRA Journal of the American Water Resources Association} 49 (5): 1007--24.
+\url{https://doi.org/10.1111/jawr.12108}.
 

### 2023-06-16 paper.Rmd
addl refs to intro

@@
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
-Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for regulatory applications or inclusion in a consolidated database [@Arndt22].
+Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks) [@Wilde02].
 An adequate number of QC samples must also be included in the dataset as a measure of "completeness".
@@
 For example, precision of duplicate samples for a given parameter must not vary 5% and at least 10% of the data should be dedicated to these checks as a measure of completeness.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review  This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
+This process is time-consuming and prone to errors, often limiting the amount of useful information that is used for regulatory assessments or submitted to formal databases.
 
@@
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
-Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] offer useful approaches to visualize numerous water quality records in a single graph.
+Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] offer useful approaches to visualize numerous water quality records in a single graph.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
 
-This paper describes the MassWateR package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
+This paper describes the \CRANpkg{MassWateR} package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
 The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
-Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected at locations elsewhere.
-As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water monitoring data in the US.
+Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected elsewhere.
+As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water quality monitoring data in the US.
 
@@
 In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
-This package leverages a robust API to query existing water quality data in the WQP.
+This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
 As such, data retrieval using existing web services is much simpler than data submission to a similar resource, as data formatting requirements do not apply when retrieving data.
@@
 Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
-That is, QC reporting is not a requirement to submit to WQX, whereas state institutions require it for regulatory assessment.
-Users may also simply have a need to understand trends or to summarize their data, while also wanted to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
+That is, QC reporting is not a requirement to submit to WQX, whereas state institutions require this reporting for regulatory assessment.
+Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
 Figure xx demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
@@
 
-No matter the user need, all data inputs to MassWateR must follow a strict format.  
+No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.  
 Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
@@
 
-All developers hope that their package is used by the intended audience.  To ensure this for MassWateR, a community of practice was...
+All developers hope that their package is used by the intended audience.  To ensure this for \CRANpkg{MassWateR}, a community of practice was...
 

### 2023-06-16 paper.tex
addl refs to intro

@@
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for inclusion in a consolidated database.
-Common QC checks for \emph{in situ} field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks).
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for regulatory applications or inclusion in a consolidated database (Arndt et al.
+2022).
+Common QC checks for \emph{in situ} field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks) (Wilde and U.S.
+Geological Survey 2002).
 An adequate number of QC samples must also be included in the dataset as a measure of ``completeness''.
@@
 For example, precision of duplicate samples for a given parameter must not vary 5\% and at least 10\% of the data should be dedicated to these checks as a measure of completeness.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review This process is time-consuming and prone to errors, often limiting the amount of useful information that is submitted to formal databases.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
+This process is time-consuming and prone to errors, often limiting the amount of useful information that is used for regulatory assessments or submitted to formal databases.
 
@@
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
-Moreover, many environmental resource managers have the need to analysis status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} (Wickham 2016) offer useful approaches to visualize numerous water quality records in a single graph.
+Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} (Wickham 2016) offer useful approaches to visualize numerous water quality records in a single graph.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
 
-This paper describes the MassWateR package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
+This paper describes the \CRANpkg{MassWateR} package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
 The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
-Although the initial conception of MassWateR was meant to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected at locations elsewhere.
-As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water monitoring data in the US.
+Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected elsewhere.
+As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water quality monitoring data in the US.
 
@@
 2022) has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
-This package leverages a robust API to query existing water quality data in the WQP.
+This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
 As such, data retrieval using existing web services is much simpler than data submission to a similar resource, as data formatting requirements do not apply when retrieving data.
@@
 
-No matter the user need, all data inputs to MassWateR must follow a strict format.\\
+No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.\\
 Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
@@
 
-All developers hope that their package is used by the intended audience. To ensure this for MassWateR, a community of practice was\ldots{}
+All developers hope that their package is used by the intended audience. To ensure this for \CRANpkg{MassWateR}, a community of practice was\ldots{}
 
@@
 \url{https://github.com/rstudio/rmarkdown}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Arndt22}{}}%
+Arndt, Julia, Julia S Kirchner, Kevin S Jewell, Michael P Schluesener, Arne Wick, Thomas A Ternes, and Lars Duester.
+2022.
+{``Making Waves: Time for Chemical Surface Water Quality Monitoring to Catch up with Its Technical Potential.''} \emph{Water Research} 213: 118168.
+\url{https://doi.org/10.1016/j.watres.2022.118168}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wilde02}{}}%
+Wilde, Franceska D., and U.S.
+Geological Survey.
+2002.
+{``Chapter A5.
+Processing of Water Samples.''} Techniques of Water-Resources Investigations 09-A5.
+Version 2.2, Revised February 2009.
+Reston, VA: U.S.
+Geological Survey.
+\url{https://doi.org/10.3133/twri09A5}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Xie15}{}}%

### 2023-06-16 paper.Rmd
workflow figure added

@@
 Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
-Figure xx demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
-The functions allow a user to engage with their data several, including 1) screening data for quality control, 2) summarizing quality control results, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
+Figure \@ref(fig:workflow) demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
+The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
+
+```{r workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.
+A user can apply one to any of the four steps depending on their need.
+The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.
+The second step can be used to create a QC report for submission to a regulatory agency.
+The third step can create a formatted table for WQX submission.
+The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+All steps require a formatted input file.
+WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'}
+knitr::include_graphics('figs/workflow.png')
+```
 

### 2023-06-16 paper.tex
workflow figure added

@@
 Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
-Figure xx demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
-The functions allow a user to engage with their data several, including 1) screening data for quality control, 2) summarizing quality control results, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
+Figure \ref{fig:workflow} demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
+The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figs/workflow} \caption{Workflow demonstrating how a user could engage with the \CRANpkg{MassWateR} package.
+A user can apply one to any of the four steps depending on their need.
+The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.
+The second step can be used to create a QC report for submission to a regulatory agency.
+The third step can create a formatted table for WQX submission.
+The fourth step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+All steps require a formatted input file.
+WQX: Water Quality Exchange; QC: Quality Control.}\label{fig:workflow}
+\end{figure}
 

### 2023-06-16 paper.R

@@ -5,3 +5,7 @@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 library(MassWateR)
 
+
+## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.  A user can apply one to any of the four steps depending on their need.  The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.  The second step can be used to create a QC report for submission to a regulatory agency.  The third step can create a formatted table for WQX submission.  The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.  All steps require a formatted input file.  WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
+knitr::include_graphics('figs/workflow.png')
+

### 2023-06-16 paper.Rmd
more text in requirements section

@@
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets [@Schiff16; @Tango13], or data collected *ad hoc* from multiple assessment endpoints [@Stein09; @Behmel16; @Kumpel20], where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest [@Buytaert14; Kelly22].
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest [@Buytaert14; @Kelly22].
 Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
@@
 No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.
-Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
+Developing a workflow to accommodate data inputs from the dozens of potential users that organize data using different formats would have been impractical.
+As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
+Several [resources](https://massbays-tech.github.io/MassWateR/RESOURCES.html) are provided on the package web page to assist potential users in this effort.
+These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
+
+The required data files for using are shown in table xx, including the steps in the workflow in Figure \@ref(fig:workflow) when a file is required.
+The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
+These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.
+Additionally, the `readMWRresultsview()` function...
 

### 2023-06-16 paper.tex
more text in requirements section

@@
 2020), where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest {[}Buytaert et al.
-(2014); Kelly22{]}.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest (Buytaert et al.
+2014; Kelly-Quinn et al.
+2022).
 Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
@@
 
-No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.\\
-Make a case for a unified format, cannot cater to all, input checks are meant assist in this effort
+No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.
+Developing a workflow to accommodate data inputs from the dozens of potential users that organize data using different formats would have been impractical.
+As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
+Several \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{resources} are provided on the package web page to assist potential users in this effort.
+These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
+
+The required data files for using are shown in table xx, including the steps in the workflow in Figure \ref{fig:workflow} when a file is required.
+The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
+These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.
+Additionally, the \texttt{readMWRresultsview()} function\ldots{}
 
@@
 \url{https://doi.org/10.5066/P9X4L3GE}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kelly22}{}}%
+Kelly-Quinn, M, JN Biggs, S Brooks, P Fortuño, S Hegarty, JI Jones, and F Regan.
+2022.
+{``Opportunities, Approaches and Challenges to the Engagement of Citizens in Filling Small Water Body Data Gaps.''} \emph{Hydrobiologia}, 1--21.
+\url{https://doi.org/10.1007/s10750-022-04973-y}.
 

### 2023-06-17 paper.Rmd
file requirements table added but woring with pdf render

@@
 library(MassWateR)
+library(flextable)
+library(here)
+
+load(file = here('tabs/filerequirements.RData'))
 ```
@@
 
-The required data files for using are shown in table xx, including the steps in the workflow in Figure \@ref(fig:workflow) when a file is required.
+The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
 The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
@@
 Additionally, the `readMWRresultsview()` function...
+
+```{r}
+filerequirements
+```
 

### 2023-06-17 paper.tex
file requirements table added but woring with pdf render

@@
 
-The required data files for using are shown in table xx, including the steps in the workflow in Figure \ref{fig:workflow} when a file is required.
+The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
 The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
@@
 Additionally, the \texttt{readMWRresultsview()} function\ldots{}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.70in}|p{3.00in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}}
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Data\ analysis}}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-1.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-2.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-3.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-4.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-5.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-6.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-7.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-8.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-9.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-10.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-11.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-12.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-13.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/unnamed-chunk-1-14.png}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
 

### 2023-06-17 R/tabs.R

@@ -1,0 +1,34 @@
+library(flextable)
+library(tidyverse)
+library(here)
+
+# file inputs ---------------------------------------------------------------------------------
+
+chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
+
+totab <- tibble(
+  `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
+  `Description` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
+  `QC screening` = c('r', 'r', 'r', 'r', ''), 
+  `QC reporting` = c('r', 'r', 'r', '', ''),
+  `WQX formatting` = c('r', 'r', '', 'r', 'r'),
+  `Data analysis` = c('r', 'r', '', 'r', '')
+) %>% 
+  mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
+
+colind <- apply(totab[, 3:6], 2, function(x) which(x != ''))
+imgsz <- 0.15
+tab <- flextable(totab) %>%
+  colformat_image(j = 3, i = colind[[1]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 4, i = colind[[2]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 5, i = colind[[3]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 6, i = colind[[4]], width = imgsz, height = imgsz) %>% 
+  width(j = 2, width = 3) %>%
+  width(j = c(1, 3:6), width = 3.5 / 5) %>% 
+  bold(part = 'header') %>%
+  colformat_double(digits = 2) %>%
+  valign(valign = 'top', part = 'header') %>%
+  align(j = 3:6, align = 'center', part = 'all')
+
+filerequirements <- tab
+save(filerequirements, file = here('tabs/filerequirements.RData'))

### 2023-06-17 paper.R

@@ -4,8 +4,16 @@
 ## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 library(MassWateR)
+library(flextable)
+library(here)
+
+load(file = here('tabs/filerequirements.RData'))
 
 
 ## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.  A user can apply one to any of the four steps depending on their need.  The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.  The second step can be used to create a QC report for submission to a regulatory agency.  The third step can create a formatted table for WQX submission.  The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.  All steps require a formatted input file.  WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
 knitr::include_graphics('figs/workflow.png')
+
+
+## -----------------------------------------------------------------------------
+filerequirements
 

### 2023-06-29 paper.Rmd
trying gt table, widths do not work on pdf

@@
 bibliography: RJreferences.bib
-
+preamble: \usepackage{amsmath, booktabs, caption, longtable}
 ---
@@
 library(MassWateR)
-library(flextable)
+library(gt)
 library(here)
@@
 
-```{r}
+```{r, eval = knitr::is_html_output()}
 filerequirements
+```
+```{r, eval = knitr::is_latex_output()}
+filerequirements %>% tab_options(table.width = pct(90))
 ```

### 2023-06-29 paper.tex
trying gt table, widths do not work on pdf

--- 2023-06-16 paper.tex
@@
 Additionally, the \texttt{readMWRresultsview()} function\ldots{}
+
+\begin{longtable}{llllll}
+\toprule
+Formatted file & Description & QC screening & QC reporting & WQX formatting & Data analysis \\ 
+\midrule
+Results & Water quality results organized by sample location and date & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> \\
+DQO accuracy & Summary of data quality objectives that describe quality control accuracy for data in the results file & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> \\
+DQO frequency and completeness & Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> &  &  \\
+Sites & A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> &  & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> \\
+WQX metadata & A wqx metadata file required for generating output to facilitate data upload to WQX &  &  & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> &  \\
+\bottomrule
+\end{longtable}
 

### 2023-06-29 R/tabs.R

@@ -1,10 +1,8 @@
-library(flextable)
+library(gt)
 library(tidyverse)
 library(here)
 
 # file inputs ---------------------------------------------------------------------------------
-
-chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
 
 totab <- tibble(
   `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
@@ -13,22 +11,45 @@ totab <- tibble(
   `QC reporting` = c('r', 'r', 'r', '', ''),
   `WQX formatting` = c('r', 'r', '', 'r', 'r'),
   `Data analysis` = c('r', 'r', '', 'r', '')
-) %>% 
-  mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
+)
 
 colind <- apply(totab[, 3:6], 2, function(x) which(x != ''))
-imgsz <- 0.15
-tab <- flextable(totab) %>%
-  colformat_image(j = 3, i = colind[[1]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 4, i = colind[[2]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 5, i = colind[[3]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 6, i = colind[[4]], width = imgsz, height = imgsz) %>% 
-  width(j = 2, width = 3) %>%
-  width(j = c(1, 3:6), width = 3.5 / 5) %>% 
-  bold(part = 'header') %>%
-  colformat_double(digits = 2) %>%
-  valign(valign = 'top', part = 'header') %>%
-  align(j = 3:6, align = 'center', part = 'all')
+imgfun <- function(x){
+  local_image(
+    filename = here(list.files('tabs', pattern = 'check', full.names = T)),
+    height = 10
+  )
+}
+tab <- gt(totab) %>%
+  text_transform(
+    locations = cells_body(columns = 3, rows = colind[[1]]),
+    fn = imgfun
+  ) %>% 
+  text_transform(
+    locations = cells_body(columns = 4, rows = colind[[2]]),
+    fn = imgfun
+  ) %>% 
+  text_transform(
+    locations = cells_body(columns = 5, rows = colind[[3]]),
+    fn = imgfun
+  ) %>% 
+  text_transform(
[…]

### 2023-06-29 paper.R

@@ -4,7 +4,7 @@
 ## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 library(MassWateR)
-library(flextable)
+library(gt)
 library(here)
 
 load(file = here('tabs/filerequirements.RData'))
@@ -14,6 +14,9 @@ load(file = here('tabs/filerequirements.RData'))
 knitr::include_graphics('figs/workflow.png')
 
 
-## -----------------------------------------------------------------------------
-filerequirements
+## ---- eval = knitr::is_html_output()------------------------------------------
+#> filerequirements
+
+## ---- eval = knitr::is_latex_output()-----------------------------------------
+filerequirements %>% tab_options(table.width = pct(90))
 

### 2023-06-30 paper.Rmd
adding some more text about file requirements and read functions

--- 2023-06-17 paper.Rmd
@@
 No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.
-Developing a workflow to accommodate data inputs from the dozens of potential users that organize data using different formats would have been impractical.
+Developing a workflow to accommodate data inputs from the dozens of potential users from different organizations that use different data formats would have been impractical.
 As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
@@
 The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
-These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.
-Additionally, the `readMWRresultsview()` function...
+These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.
+The largest input file required for all parts of the workflow in Figure \@ref(fig:workflow) is the results file.
+This file includes all water quality monitoring data to be used with the package.
+As such, the formatting requirements are the most burdensome for potential uses and additional functions are available to assist with formatting.
 
@@
 
+The following sections describe the basic approach to using functions in \CRANpkg{MassWateR} for any of the processes in the workflow.
+The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
+Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
+Each prefix also includes `MWR` to avoid namespace conflicts with other packages.
+
+* `read`: Read input files
+* `check`: Check input files formatting issues, used internally to the read functions 
+* `form`: Format input files for downstream functions, used internally to the read functions once the checks have passed
+* `anlz`: Analyze imported data
+* `tab`: Create formatted tables for QC analysis
+* `qc`: QC functions for summarizing QC results, used internally to the table functions
+* `util`: Various utility functions that accomplish routine tasks
+
+Additionally, functions may often include a suffix that describes the relevant file that is used as input or otherwise evaluated in a downstream function.
+
+* `results`: The results input file
+* `acc`: The data quality objectives file for accuracy
+* `frecom`: The data quality objectives file for frequency and completeness
+* `sites`: The site metadata file
+* `wqx`: The Water Quality Exchange metadata file
+
 # Read
+
+The primary task of the `read` functions is to ensure all imported files follow the required format for the package.
+The `read` functions use the `read_excel` function from the \CRANpkg{readxl} package as Excel files are the expected format for all inputs.
+The `read` functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant `check` functions inside the `read` function.
+There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
+Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check and the function is exited.
+The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
+As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass.
+Again, this design was purposeful as many monitoring agencies or groups collect data differently and a standard input format for the package was the best option to .
+This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+A user only needs to format their data once to use the package.
+
+Figure showing iterative workflow to data import
 

### 2023-07-02 paper.Rmd
read section done

@@
 
+table xx
 ```{r}
-filerequirements
+# filerequirements
 ```
@@
 * `read`: Read input files
-* `check`: Check input files formatting issues, used internally to the read functions 
+* `check`: Check input files for formatting issues, used internally to the read functions 
 * `form`: Format input files for downstream functions, used internally to the read functions once the checks have passed
@@
 * `qc`: QC functions for summarizing QC results, used internally to the table functions
-* `util`: Various utility functions that accomplish routine tasks
+* `util`: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
 
@@
 * `sites`: The site metadata file
-* `wqx`: The Water Quality Exchange metadata file
+* `wqx`: The WQX metadata file
 
-# Read
+# \CRANpkg{MassWateR} functions
+
+## Read
 
@@
 There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
-Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check and the function is exited.
+Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
 The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
-As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass.
-Again, this design was purposeful as many monitoring agencies or groups collect data differently and a standard input format for the package was the best option to .
+As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \@ref(fig:importflow)).
+Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
 This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
@@
 
-Figure showing iterative workflow to data import
+```{r importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.
+All read functions import an Excel file and the imported file is then passed to a check function.
+The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'}
+knitr::include_graphics('figs/importflow.png')
+```
 
-# Quality Control
+A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that are performed and that all checks were successful.
+Below demonstrates what would be shown for the results file using an example dataset included with the package.
+A total of fifteen checks are applied to the results file.
 
-# Analysis
+```{r, echo = T, message = T}
+library(MassWateR)
 
-# Data submission
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+```
+
+The following shows a typical error that might be returned if a check fails importing the results file.
+The `resdat` object is an imported results file that has passed all checks, but incorrect entries are added to the `chk` object to demonstrate the error that is returned if a user would have attempted to import this file.
+The `checkMWRresults()` function is run inside the `readMWRresults()` function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the `Activity Type` column are found.
+In this example, a user would need to change the entries in rows 4 and 135 of the `Activity Type` column in their Excel file to fix the issue and import the file again as in Figure \@ref(fig:importflow).
+The online [vignette](https://massbays-tech.github.io/MassWateR/articles/inputs.html#data-import-and-checks) specifies the valid entries.
+
+```{r, error = T, echo = T, message = T}
+chk <- resdat
+chk[4, 2] <- "Sample"
+chk[135, 2] <- "Field"
+checkMWRresults(chk)
+```
+
+The `readMWRresultsview()` function is also available to assist with troubleshooting formatting issues for the results file.
+This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
+The output is similar to running `apply(resdat, 2, unique)` in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
+
+After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
+In the latter case, a path or data object can be used as input for each file.
+For the former approach, the beginning of a script for using the package could appear as follows.
+Example files included with the package are imported, whereas a user will specify paths to their own files.
+
+```{r, results = 'hide', echo = T}
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+# import dqo accuracy data
+accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
+accdat <- readMWRacc(accpth)
+
+# import dqo frequency and completeness data
+frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
+frecomdat <- readMWRfrecom(frecompth)
+
+# import site data
+sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
+sitdat <- readMWRsites(sitpth)
+
+# import WQX meta data
+wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
+wqxdat <- readMWRwqx(wqxpth)
+
+# a list of input data frames
+fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
+```
+
+The object `fsetls` can then be used as input to downstream functions.
+
+A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
+The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
+On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
+The list includes `r nrow(paramsMWR)` different parameters, each with multiple valid units of measurement.
+Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
+It is not an unreasonable expectation for users to provide only one unit of measurement per parameter as processing laboratories typically have a standard reporting format based on the same methodology used for estimating concentrations of water quality parameters.
+
+## Quality Control
+
+## Analysis
+
+## Data submission
 

### 2023-07-02 paper.tex
read section done

--- 2023-06-16 paper.tex
@@
 
-The required data files for using are shown in table xx, including the steps in the workflow in Figure \ref{fig:workflow} when a file is required.
+The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
 The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
-These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential.
-Additionally, the \texttt{readMWRresultsview()} function\ldots{}
+These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.
+The largest input file required for all parts of the workflow in Figure \ref{fig:workflow} is the results file.
+This file includes all water quality monitoring data to be used with the package.
+As such, the formatting requirements are the most burdensome for potential uses and additional functions are available to assist with formatting.
+
+table xx
+
+The following sections describe the basic approach to using functions in \CRANpkg{MassWateR} for any of the processes in the workflow.
+The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
+Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
+Each prefix also includes \texttt{MWR} to avoid namespace conflicts with other packages.
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{read}: Read input files
+\item
+  \texttt{check}: Check input files for formatting issues, used internally to the read functions
+\item
+  \texttt{form}: Format input files for downstream functions, used internally to the read functions once the checks have passed
+\item
+  \texttt{anlz}: Analyze imported data
+\item
+  \texttt{tab}: Create formatted tables for QC analysis
+\item
+  \texttt{qc}: QC functions for summarizing QC results, used internally to the table functions
+\item
+  \texttt{util}: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
+\end{itemize}
+
+Additionally, functions may often include a suffix that describes the relevant file that is used as input or otherwise evaluated in a downstream function.
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{results}: The results input file
+\item
+  \texttt{acc}: The data quality objectives file for accuracy
+\item
+  \texttt{frecom}: The data quality objectives file for frequency and completeness
+\item
+  \texttt{sites}: The site metadata file
+\item
+  \texttt{wqx}: The WQX metadata file
+\end{itemize}
+
+\hypertarget{functions}{%
+\section{\texorpdfstring{\CRANpkg{MassWateR} functions}{ functions}}\label{functions}}
 
 \hypertarget{read}{%
-\section{Read}\label{read}}
+\subsection{Read}\label{read}}
+
+The primary task of the \texttt{read} functions is to ensure all imported files follow the required format for the package.
+The \texttt{read} functions use the \texttt{read\_excel} function from the \CRANpkg{readxl} package as Excel files are the expected format for all inputs.
+The \texttt{read} functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant \texttt{check} functions inside the \texttt{read} function.
+There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
+Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
+The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
+As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \ref{fig:importflow}).
+Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
+This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+A user only needs to format their data once to use the package.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.
+All read functions import an Excel file and the imported file is then passed to a check function.
+The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.}\label{fig:importflow}
+\end{figure}
+
+A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that are performed and that all checks were successful.
+Below demonstrates what would be shown for the results file using an example dataset included with the package.
+A total of fifteen checks are applied to the results file.
+
+\begin{verbatim}
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+\end{verbatim}
+
+\begin{verbatim}
+#> Running checks on results data...
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking column names... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking all required columns are present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking valid Activity Types... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Start Date formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking depth data present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking for non-numeric values in Activity Depth/Height Measure... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Depth/Height Unit... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Relative Depth Name formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking values in Activity Depth/Height Measure > 1 m / 3.3 ft... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Characteristic Name formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Result Values... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking QC Reference Values... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking for missing entries for Result Unit... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking if more than one unit per Characteristic Name... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking acceptable units for each entry in Characteristic Name... OK
+\end{verbatim}
+
+\begin{verbatim}
+#> 
+#> All checks passed!
+\end{verbatim}
+
+The following shows a typical error that might be returned if a check fails importing the results file.
+The \texttt{resdat} object is an imported results file that has passed all checks, but incorrect entries are added to the \texttt{chk} object to demonstrate the error that is returned if a user would have attempted to import this file.
+The \texttt{checkMWRresults()} function is run inside the \texttt{readMWRresults()} function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the \texttt{Activity\ Type} column are found.
+In this example, a user would need to change the entries in rows 4 and 135 of the \texttt{Activity\ Type} column in their Excel file to fix the issue and import the file again as in Figure \ref{fig:importflow}.
+The online \href{https://massbays-tech.github.io/MassWateR/articles/inputs.html\#data-import-and-checks}{vignette} specifies the valid entries.
+
+\begin{verbatim}
+chk <- resdat
+chk[4, 2] <- "Sample"
+chk[135, 2] <- "Field"
+checkMWRresults(chk)
+\end{verbatim}
+
+\begin{verbatim}
+#> Running checks on results data...
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking column names... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking all required columns are present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#> Error:   Checking valid Activity Types...
+#>  Incorrect Activity Type found: Sample, Field in row(s) 4, 135
+\end{verbatim}
+
+The \texttt{readMWRresultsview()} function is also available to assist with troubleshooting formatting issues for the results file.
+This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
+The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
+
+After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
+In the latter case, a path or data object can be used as input for each file.
+For the former approach, the beginning of a script for using the package could appear as follows.
+Example files included with the package are imported, whereas a user will specify paths to their own files.
+
+\begin{verbatim}
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+# import dqo accuracy data
+accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
+accdat <- readMWRacc(accpth)
+
+# import dqo frequency and completeness data
+frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
+frecomdat <- readMWRfrecom(frecompth)
+
+# import site data
+sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
+sitdat <- readMWRsites(sitpth)
+
+# import WQX meta data
+wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
+wqxdat <- readMWRwqx(wqxpth)
+
+# a list of input data frames
+fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
+\end{verbatim}
+
+The object \texttt{fsetls} can then be used as input to downstream functions.
+
+A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
+The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
+On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
+The list includes 43 different parameters, each with multiple valid units of measurement.
+Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
+It is not an unreasonable expectation for users to provide only one unit of measurement per parameter as processing laboratories typically have a standard reporting format based on the same methodology used for estimating concentrations of water quality parameters.
 
 \hypertarget{quality-control}{%
-\section{Quality Control}\label{quality-control}}
+\subsection{Quality Control}\label{quality-control}}
 
 \hypertarget{analysis}{%
-\section{Analysis}\label{analysis}}
+\subsection{Analysis}\label{analysis}}
 
 \hypertarget{data-submission}{%
-\section{Data submission}\label{data-submission}}
+\subsection{Data submission}\label{data-submission}}
 

### 2023-07-02 paper.R

@@ -15,5 +15,51 @@ knitr::include_graphics('figs/workflow.png')
 
 
 ## -----------------------------------------------------------------------------
-filerequirements
+# filerequirements
+
+
+## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'----
+knitr::include_graphics('figs/importflow.png')
+
+
+## ---- echo = T, message = T---------------------------------------------------
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+
+## ---- error = T, echo = T, message = T----------------------------------------
+chk <- resdat
+chk[4, 2] <- "Sample"
+chk[135, 2] <- "Field"
+checkMWRresults(chk)
+
+
+## ---- results = 'hide', echo = T----------------------------------------------
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+# import dqo accuracy data
+accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
+accdat <- readMWRacc(accpth)
+
+# import dqo frequency and completeness data
+frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
+frecomdat <- readMWRfrecom(frecompth)
+
+# import site data
+sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
+sitdat <- readMWRsites(sitpth)
+
+# import WQX meta data
+wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
+wqxdat <- readMWRwqx(wqxpth)
+
+# a list of input data frames
+fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
 

### 2023-07-04 paper.Rmd
added outlier text and examples

@@
 This file includes all water quality monitoring data to be used with the package.
-As such, the formatting requirements are the most burdensome for potential uses and additional functions are available to assist with formatting.
+As such, the formatting requirements are the most burdensome for potential users and additional functions are available to assist with formatting.
 
@@
 
-Additionally, functions may often include a suffix that describes the relevant file that is used as input or otherwise evaluated in a downstream function.
+Additionally, functions may often include a suffix that describes the relevant file used as input or otherwise evaluated in a downstream function.
 
@@
 
-## Read
+## Read and check files
 
 The primary task of the `read` functions is to ensure all imported files follow the required format for the package.
-The `read` functions use the `read_excel` function from the \CRANpkg{readxl} package as Excel files are the expected format for all inputs.
+Excel files are the expected format for all inputs and the `read` functions use the `read_excel` function from the \CRANpkg{readxl} package [@Wickham23].
 The `read` functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant `check` functions inside the `read` function.
@@
 Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
-It is not an unreasonable expectation for users to provide only one unit of measurement per parameter as processing laboratories typically have a standard reporting format based on the same methodology used for estimating concentrations of water quality parameters.
+It is not an unreasonable expectation for users to provide only one unit of measurement per parameter.
+Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
 
-## Quality Control
+An additional set of functions can be used to check for outliers in the results file.
+Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
+Identifying and potentially removing or correcting outliers is a critical part of quality control.
+The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct outliers.
+
+The `anlzMWRoutlier()` function uses the results file and data quality objectives for accuracy to plot potential outliers by month.
+The accuracy file is used to automatically identify the y-axis scaling (as arithmetic or log) and to replace concentrations with appropriate values for those labelled as beyond detection.
+Outliers are defined using the standard definition of 1.5 times the interquartile range (the 25th to 75th percentile) of a parameter and can be visually identified as points above or below the whiskers in the boxplots.
+The station name for a point is also shown.
+The `param` specifies the water quality parameter to evaluate and the `group` argument specifies how the boxplots are grouped (by year, month, week, or station).
+In the following example, three stations are identified as potential outliers for the respective month.
+
+```{r, fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
+```
+
+The outliers in the above plot can also be viewed as tabular output using `outliers = TRUE` to aid in their identification.
+
+```{r, echo = T}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
+```
+
+A user can also evaluate outliers for every water quality parameter in the results file.
+The `anlzMWRoutlierall()` function creates a Word document with images of boxplots for every parameter created with `anlzMWRoutlier()`.
+Images for each parameter can also be created as standalone files.
+The `param` argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
+The following shows how to use the function by creating a single Word file or individual image files in the working directory.
+
+```{r, echo = T, eval = F}
+# create word output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', output_dir = getwd())
+
+# create png output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', output_dir = getwd())
+```
+
+As in Figure \@ref(fig:importflow), a user can identify outliers from the results, modify the file in Excel, and import the file again for further QC reporting or analysis.
+
+## Quality Control reporting
+
+The quality control functions in \CRANpkg{MassWateR}
 

### 2023-07-04 paper.tex
added outlier text and examples

@@
 
-\hypertarget{read}{%
-\subsection{Read}\label{read}}
+\hypertarget{read-and-check-files}{%
+\subsection{Read and check files}\label{read-and-check-files}}
 
 The primary task of the \texttt{read} functions is to ensure all imported files follow the required format for the package.
-The \texttt{read} functions use the \texttt{read\_excel} function from the \CRANpkg{readxl} package as Excel files are the expected format for all inputs.
+Excel files are the expected format for all inputs and the \texttt{read} functions use the \texttt{read\_excel} function from the \CRANpkg{readxl} package (Wickham and Bryan 2023).
 The \texttt{read} functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant \texttt{check} functions inside the \texttt{read} function.
@@
 Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
-It is not an unreasonable expectation for users to provide only one unit of measurement per parameter as processing laboratories typically have a standard reporting format based on the same methodology used for estimating concentrations of water quality parameters.
+It is not an unreasonable expectation for users to provide only one unit of measurement per parameter.
+Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
 
-\hypertarget{quality-control}{%
-\subsection{Quality Control}\label{quality-control}}
+An additional set of functions can be used to check for outliers in the results file.
+Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
+Identifying and potentially removing or correcting outliers is a critical part of quality control.
+The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct outliers.
+
+The \texttt{anlzMWRoutlier()} function uses the results file and data quality objectives for accuracy to plot potential outliers by month.
+The accuracy file is used to automatically identify the y-axis scaling (as arithmetic or log) and to replace concentrations with appropriate values for those labelled as beyond detection.
+Outliers are defined using the standard definition of 1.5 times the interquartile range (the 25th to 75th percentile) of a parameter and can be visually identified as points above or below the whiskers in the boxplots.
+The station name for a point is also shown.
+The \texttt{param} specifies the water quality parameter to evaluate and the \texttt{group} argument specifies how the boxplots are grouped (by year, month, week, or station).
+In the following example, three stations are identified as potential outliers for the respective month.
+
+\begin{verbatim}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1}
+
+The outliers in the above plot can also be viewed as tabular output using \texttt{outliers\ =\ TRUE} to aid in their identification.
+
+\begin{verbatim}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
+\end{verbatim}
+
+\begin{verbatim}
+#> # A tibble: 3 x 6
+#>   `Monitoring Location ID` `Activity Start Date` `Activity Start Time`
+#>   <chr>                    <date>                <chr>                
+#> 1 ELZ-004                  2022-05-15            06:50                
+#> 2 HOP-011                  2022-05-15            06:55                
+#> 3 ELZ-004                  2022-09-11            07:20                
+#> # i 3 more variables: `Characteristic Name` <chr>, `Result Value` <dbl>,
+#> #   `Result Unit` <chr>
+\end{verbatim}
+
+A user can also evaluate outliers for every water quality parameter in the results file.
+The \texttt{anlzMWRoutlierall()} function creates a Word document with images of boxplots for every parameter created with \texttt{anlzMWRoutlier()}.
+Images for each parameter can also be created as standalone files.
+The \texttt{param} argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
+The following shows how to use the function by creating a single Word file or individual image files in the working directory.
+
+\begin{verbatim}
+# create word output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', output_dir = getwd())
+
+# create png output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', output_dir = getwd())
+\end{verbatim}
+
+As in Figure \ref{fig:importflow}, a user can identify outliers from the results, modify the file in Excel, and import the file again for further QC reporting or analysis.
+
+\hypertarget{quality-control-reporting}{%
+\subsection{Quality Control reporting}\label{quality-control-reporting}}
+
+The quality control functions in \CRANpkg{MassWateR}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham23}{}}%
+Wickham, Hadley, and Jennifer Bryan. 2023. \emph{Readxl: Read Excel Files}. \url{https://CRAN.R-project.org/package=readxl}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wilde02}{}}%

### 2023-07-04 paper.R

@@ -63,3 +63,19 @@ wqxdat <- readMWRwqx(wqxpth)
 # a list of input data frames
 fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
 
+
+## ---- fig.height = 3, fig.width = 6, echo = T, out.width = '100%'-------------
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
+
+
+## ---- echo = T----------------------------------------------------------------
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
+
+
+## ---- echo = T, eval = F------------------------------------------------------
+#> # create word output
+#> anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', output_dir = getwd())
+#> 
+#> # create png output
+#> anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', output_dir = getwd())
+

### 2023-07-04 paper.Rmd
started qc review section

@@
 
-# import dqo accuracy data
+# import accuracy data
 accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
@@
 
-# import dqo frequency and completeness data
+# import frequency and completeness data
 frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
@@
 
-The quality control functions in \CRANpkg{MassWateR}
+The quality control functions in \CRANpkg{MassWateR} are designed to create a single report that compares the water quality data in the results file (`resdat`) to data quality objectives in the accuracy (`accdat`) and frequency and completeness (`frecomdat`) files.
+In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
+The QC checks for frequency and completeness evaluate if a sufficient number of records in the results file satisfy the accuracy checks and that sufficient QC data have been collected.
+The values in the `accdat` and `frecomdat` inputs are collectively described as data quality objectives (DQOs), such that the QC samples in `resdat` must satisfy these objectives to be considered accurate and precise data for use in regulatory or other assessments by water quality professionals.
+
+The `qcMWRreview()` function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the `accdat` and `frecomdat` input files.
+This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describe relevant evaluations for the QC assessment.
+The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
+A user can then further edit the Word document as needed.
+The first two pages of the QC report are shown in Figure \@ref(fig:qcex).
+
+```{r, echo = T, eval = F}
+qcMWRreview(fset = fsetls, output_dir = getwd())
+```
+
+```{r qcex, fig.cap = "The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+The first page shows the data quality objectives for accuracy, frequency, and completeness.
+The second page shows QC results for frequency and completeness.
+Parameters shown in red or marked as 'MISS' failed the data quality objectives.
+Users can edit the Word file as needed, e.g., entering the organization name or adding additional notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '100%'}
+knitr::include_graphics('figs/qcex.png')
+```
+
+The QC report is built using several functions that can be used individually as needed.
+In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] table objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
+For example, the `tabMWRacc()` function evaluates accuracy checks for field duplicates, lab duplicates, field blanks, lab blanks, and lab spikes/instrument checks for QC records in the results file based on DQOs in the accuracy file.
+The function can return a summary of all checks as follows:
+
+```{r, echo = T}
+tabMWRacc(fset = fsetls, type = "summary")
+```
+
+The table shows the types and amounts of QC checks applied to each parameter and which of those checks did not satisfy the DQOs in the accuracy file.
+For example, there were four field duplicate records for ammonia in the results file and only one of those records included a duplicate value outside of the acceptable range, i.e., there was a 75% acceptance rate for the four field duplicate records.
+This same table can be viewed relative to the applicable frequency rate for the amount of passing checks considered to be appropriate for the QC records as identified in the frequency and completeness DQO file.
+
+```{r, echo = T}
+tabMWRacc(fset = fsetls, type = "percent")
+```
+
+The cellsin red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
+All other parameters and checks in green had enough QC records to satisify the DQOs.
+Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicate for dissolved oxygen.
+The empty cells are typically for QC checks that do not readily apply to a parameter.
+For example, dissolved oxygen is measured in the field with monitoring equipment with no lab processing, such that lab QC checks are not relevant.
+
+Detailed information about the QC checks for an individual parameter can be obtained...
 

### 2023-07-04 paper.tex
started qc review section

@@
 
-The quality control functions in \CRANpkg{MassWateR}
+The quality control functions in \CRANpkg{MassWateR} are designed to create a single report that compares the water quality data in the results file (\texttt{resdat}) to data quality objectives in the accuracy (\texttt{accdat}) and frequency and completeness (\texttt{frecomdat}) files.
+In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
+The QC checks for frequency and completeness evaluate if a sufficient number of records in the results file satisfy the accuracy checks and that sufficient QC data have been collected.
+The values in the \texttt{accdat} and \texttt{frecomdat} inputs are collectively described as data quality objectives (DQOs), such that the QC samples in \texttt{resdat} must satisfy these objectives to be considered accurate and precise data for use in regulatory or other assessments by water quality professionals.
+
+The \texttt{qcMWRreview()} function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the \texttt{accdat} and \texttt{frecomdat} input files.
+This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describe relevant evaluations for the QC assessment.
+The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
+A user can then further edit the Word document as needed.
+The first two pages of the QC report are shown in Figure \ref{fig:qcex}.
+
+\begin{verbatim}
+qcMWRreview(fset = fsetls, output_dir = getwd())
+\end{verbatim}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figs/qcex} \caption{The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+The first page shows the data quality objectives for accuracy, frequency, and completeness.
+The second page shows QC results for frequency and completeness.
+Parameters shown in red or marked as 'MISS' failed the data quality objectives.
+Users can edit the Word file as needed, e.g., entering the organization name or adding additional notes.}\label{fig:qcex}
+\end{figure}
+
+The QC report is built using several functions that can be used individually as needed.
+In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) table objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
+For example, the \texttt{tabMWRacc()} function evaluates accuracy checks for field duplicates, lab duplicates, field blanks, lab blanks, and lab spikes/instrument checks for QC records in the results file based on DQOs in the accuracy file.
+The function can return a summary of all checks as follows:
+
+\begin{verbatim}
+tabMWRacc(fset = fsetls, type = "summary")
+\end{verbatim}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{2.44in}|p{1.41in}|p{1.82in}|p{1.52in}|p{1.26in}}
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\%\ Acceptance}}} \\
+
+\ascline{1.5pt}{666666}{1-5}\endfirsthead
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\%\ Acceptance}}} \\
+
+\ascline{1.5pt}{666666}{1-5}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{75\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DO}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{80\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{94\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{16}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{91\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{86\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Spikes\ /\ Instrument\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{9}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{90\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{20}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{19}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\ \%}}} \\
+
+\ascline{1.5pt}{666666}{1-5}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The table shows the types and amounts of QC checks applied to each parameter and which of those checks did not satisfy the DQOs in the accuracy file.
+For example, there were four field duplicate records for ammonia in the results file and only one of those records included a duplicate value outside of the acceptable range, i.e., there was a 75\% acceptance rate for the four field duplicate records.
+This same table can be viewed relative to the applicable frequency rate for the amount of passing checks considered to be appropriate for the QC records as identified in the frequency and completeness DQO file.
+
+\begin{verbatim}
+tabMWRacc(fset = fsetls, type = "percent")
+\end{verbatim}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{1.41in}|p{1.30in}|p{1.22in}|p{1.04in}|p{0.96in}|p{1.81in}}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{75\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{86\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{DO}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{90\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{94\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{80\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{91\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{95\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The cellsin red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
+All other parameters and checks in green had enough QC records to satisify the DQOs.
+Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicate for dissolved oxygen.
+The empty cells are typically for QC checks that do not readily apply to a parameter.
+For example, dissolved oxygen is measured in the field with monitoring equipment with no lab processing, such that lab QC checks are not relevant.
+
+Detailed information about the QC checks for an individual parameter can be obtained\ldots{}
 
@@
 \url{https://doi.org/10.5066/P9X4L3GE}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gohel23}{}}%
+Gohel, David, and Panagiotis Skintzos. 2023. \emph{Flextable: Functions for Tabular Reporting}. \url{https://CRAN.R-project.org/package=flextable}.
 

### 2023-07-04 paper.R

@@ -44,11 +44,11 @@ library(MassWateR)
 respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
 resdat <- readMWRresults(respth)
 
-# import dqo accuracy data
+# import accuracy data
 accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
 accdat <- readMWRacc(accpth)
 
-# import dqo frequency and completeness data
+# import frequency and completeness data
 frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
 frecomdat <- readMWRfrecom(frecompth)
 
@@ -78,4 +78,20 @@ anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
 #> 
 #> # create png output
 #> anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', output_dir = getwd())
+
+
+## ---- echo = T, eval = F------------------------------------------------------
+#> qcMWRreview(fset = fsetls, output_dir = getwd())
+
+
+## ----qcex, fig.cap = "The first two pages of the quality control report that evaluates the results data relative to data quality objectives.  The first page shows the data quality objectives for accuracy, frequency, and completeness.  The second page shows QC results for frequency and completeness.  Parameters shown in red or marked as 'MISS' failed the data quality objectives.  Users can edit the Word file as needed, e.g., entering the organization name or adding additional notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '100%'----
+knitr::include_graphics('figs/qcex.png')
+
+
+## ---- echo = T----------------------------------------------------------------
+tabMWRacc(fset = fsetls, type = "summary")
+
+
+## ---- echo = T----------------------------------------------------------------
+tabMWRacc(fset = fsetls, type = "percent")
 

### 2023-07-05 paper.Rmd
trying conditional chunk eval for flextable

@@
 
-The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
+The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:`r ifelse(knitr::is_html_output(), 'filreqhtml', 'filreqpdf')`), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
 The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
@@
 
-table xx
-```{r}
-# filerequirements
+```{r filreqhtml, eval = knitr::is_html_output()}
+filerequirements
+```
+```{r filreqpdf, eval = knitr::is_latex_output(), results = 'asis'}
+flextable_to_rmd(filerequirements)
 ```

### 2023-07-05 paper.tex
trying conditional chunk eval for flextable

--- 2023-07-02 paper.tex
@@
 
-The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
+The required data files for using \CRANpkg{MassWateR} are shown in Table \ref{tab:filreqpdf}, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
 The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
@@
 This file includes all water quality monitoring data to be used with the package.
-As such, the formatting requirements are the most burdensome for potential uses and additional functions are available to assist with formatting.
+As such, the formatting requirements are the most burdensome for potential users and additional functions are available to assist with formatting.
 
-table xx
+\setlength{\tabcolsep}{0pt}
 
-The following sections describe the basic approach to using functions in \CRANpkg{MassWateR} for any of the processes in the workflow.
-The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
-Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
-Each prefix also includes \texttt{MWR} to avoid namespace conflicts with other packages.
+\renewcommand*{\arraystretch}{1.5}
 
-\begin{itemize}
-\tightlist
-\item
-  \texttt{read}: Read input files
-\item
-  \texttt{check}: Check input files for formatting issues, used internally to the read functions
-\item
-  \texttt{form}: Format input files for downstream functions, used internally to the read functions once the checks have passed
-\item
-  \texttt{anlz}: Analyze imported data
-\item
-  \texttt{tab}: Create formatted tables for QC analysis
-\item
-  \texttt{qc}: QC functions for summarizing QC results, used internally to the table functions
-\item
-  \texttt{util}: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
-\end{itemize}
+\providecommand{\ascline}[3]{\noalign{\global\Oldarrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
 
-Additionally, functions may often include a suffix that describes the relevant file that is used as input or otherwise evaluated in a downstream function.
+\begin{longtable}[c]{|p{0.70in}|p{3.00in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}}
 
-\begin{itemize}
-\tightlist
-\item
-  \texttt{results}: The results input file
-\item
-  \texttt{acc}: The data quality objectives file for accuracy
-\item
-  \texttt{frecom}: The data quality objectives file for frequency and completeness
-\item
-  \texttt{sites}: The site metadata file
-\item
-  \texttt{wqx}: The WQX metadata file
-\end{itemize}
+\caption{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
 
-\hypertarget{functions}{%
-\section{\texorpdfstring{\CRANpkg{MassWateR} functions}{ functions}}\label{functions}}
+\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
 
-\hypertarget{read}{%
-\subsection{Read}\label{read}}
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
 
-The primary task of the \texttt{read} functions is to ensure all imported files follow the required format for the package.
-The \texttt{read} functions use the \texttt{read\_excel} function from the \CRANpkg{readxl} package as Excel files are the expected format for all inputs.
-The \texttt{read} functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant \texttt{check} functions inside the \texttt{read} function.
-There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
-Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
-The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
-As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \ref{fig:importflow}).
-Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
-This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
-A user only needs to format their data once to use the package.
+\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
 
-\begin{figure}
-\includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.
-All read functions import an Excel file and the imported file is then passed to a check function.
-The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.}\label{fig:importflow}
-\end{figure}
+\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
 
-A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that are performed and that all checks were successful.
-Below demonstrates what would be shown for the results file using an example dataset included with the package.
-A total of fifteen checks are applied to the results file.
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
 
-\begin{verbatim}
-library(MassWateR)
+\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}\endhead
 
-# import results data
-respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
-resdat <- readMWRresults(respth)
-\end{verbatim}
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-1.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-2.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-3.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-4.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\begin{verbatim}
-#> Running checks on results data...
-\end{verbatim}
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-5.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-6.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-7.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-8.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\begin{verbatim}
-#>  Checking column names... OK
-\end{verbatim}
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-9.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-10.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\begin{verbatim}
-#>  Checking all required columns are present... OK
-\end{verbatim}
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-11.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-12.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-13.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\begin{verbatim}
-#>  Checking valid Activity Types... OK
-\end{verbatim}
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\begin{verbatim}
-#>  Checking Activity Start Date formats... OK
-\end{verbatim}
+\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
 
-\begin{verbatim}
-#>  Checking depth data present... OK
-\end{verbatim}
+\end{longtable}
 
-\begin{verbatim}
-#>  Checking for non-numeric values in Activity Depth/Height Measure... OK
-\end{verbatim}
+\arrayrulecolor[HTML]{000000}
 
-\begin{verbatim}
-#>  Checking Activity Depth/Height Unit... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking Activity Relative Depth Name formats... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking values in Activity Depth/Height Measure > 1 m / 3.3 ft... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking Characteristic Name formats... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking Result Values... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking QC Reference Values... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking for missing entries for Result Unit... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking if more than one unit per Characteristic Name... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking acceptable units for each entry in Characteristic Name... OK
-\end{verbatim}
-
-\begin{verbatim}
-#> 
-#> All checks passed!
-\end{verbatim}
-
-The following shows a typical error that might be returned if a check fails importing the results file.
-The \texttt{resdat} object is an imported results file that has passed all checks, but incorrect entries are added to the \texttt{chk} object to demonstrate the error that is returned if a user would have attempted to import this file.
-The \texttt{checkMWRresults()} function is run inside the \texttt{readMWRresults()} function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the \texttt{Activity\ Type} column are found.
-In this example, a user would need to change the entries in rows 4 and 135 of the \texttt{Activity\ Type} column in their Excel file to fix the issue and import the file again as in Figure \ref{fig:importflow}.
-The online \href{https://massbays-tech.github.io/MassWateR/articles/inputs.html\#data-import-and-checks}{vignette} specifies the valid entries.
-
-\begin{verbatim}
-chk <- resdat
-chk[4, 2] <- "Sample"
-chk[135, 2] <- "Field"
-checkMWRresults(chk)
-\end{verbatim}
-
-\begin{verbatim}
-#> Running checks on results data...
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking column names... OK
-\end{verbatim}
-
-\begin{verbatim}
-#>  Checking all required columns are present... OK
-\end{verbatim}
-
-\begin{verbatim}
-#> Error:   Checking valid Activity Types...
-#>  Incorrect Activity Type found: Sample, Field in row(s) 4, 135
-\end{verbatim}
-
-The \texttt{readMWRresultsview()} function is also available to assist with troubleshooting formatting issues for the results file.
-This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
-The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
-
-After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
-This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
-In the latter case, a path or data object can be used as input for each file.
-For the former approach, the beginning of a script for using the package could appear as follows.
-Example files included with the package are imported, whereas a user will specify paths to their own files.
-
-\begin{verbatim}
-library(MassWateR)
-
-# import results data
-respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
-resdat <- readMWRresults(respth)
-
-# import dqo accuracy data
-accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
-accdat <- readMWRacc(accpth)
-
-# import dqo frequency and completeness data
-frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
-frecomdat <- readMWRfrecom(frecompth)
-
-# import site data
-sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
-sitdat <- readMWRsites(sitpth)
-
-# import WQX meta data
-wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
-wqxdat <- readMWRwqx(wqxpth)
-
-# a list of input data frames
-fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
-\end{verbatim}
-
-The object \texttt{fsetls} can then be used as input to downstream functions.
-
-A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
-On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
-The list includes 43 different parameters, each with multiple valid units of measurement.
-Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
-It is not an unreasonable expectation for users to provide only one unit of measurement per parameter as processing laboratories typically have a standard reporting format based on the same methodology used for estimating concentrations of water quality parameters.
-
-\hypertarget{quality-control}{%
-\subsection{Quality Control}\label{quality-control}}
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-\hypertarget{data-submission}{%
-\subsection{Data submission}\label{data-submission}}
-
-\hypertarget{building-a-community-and-future-work}{%
-\section{Building a community and future work}\label{building-a-community-and-future-work}}
-
-All developers hope that their package is used by the intended audience. To ensure this for \CRANpkg{MassWateR}, a community of practice was\ldots{}
-
-Building the community of practice\ldots{}
-
-MassWater in other locations, expansion elsewhere
-
-Inclusion of historical data
-
-Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.
-
-\hypertarget{summary}{%
-\section{Summary}\label{summary}}
+\renewcommand*{\arraystretch}{1}
 

### 2023-07-05 R/tabs.R

@@ -28,7 +28,13 @@ tab <- flextable(totab) %>%
   bold(part = 'header') %>%
   colformat_double(digits = 2) %>%
   valign(valign = 'top', part = 'header') %>%
-  align(j = 3:6, align = 'center', part = 'all')
+  align(j = 3:6, align = 'center', part = 'all') %>% 
+  set_caption(
+    as_paragraph(
+      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow.", props = fp_text_default(font.family = "Arial"))
+              ), 
+    word_stylename = "Table Caption"
+    )
 
 filerequirements <- tab
 save(filerequirements, file = here('tabs/filerequirements.RData'))

### 2023-07-05 paper.R

@@ -14,84 +14,6 @@ load(file = here('tabs/filerequirements.RData'))
 knitr::include_graphics('figs/workflow.png')
 
 
-## -----------------------------------------------------------------------------
-# filerequirements
-
-
-## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'----
-knitr::include_graphics('figs/importflow.png')
-
-
-## ---- echo = T, message = T---------------------------------------------------
-library(MassWateR)
-
-# import results data
-respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
-resdat <- readMWRresults(respth)
-
-
-## ---- error = T, echo = T, message = T----------------------------------------
-chk <- resdat
-chk[4, 2] <- "Sample"
-chk[135, 2] <- "Field"
-checkMWRresults(chk)
-
-
-## ---- results = 'hide', echo = T----------------------------------------------
-library(MassWateR)
-
-# import results data
-respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
-resdat <- readMWRresults(respth)
-
-# import accuracy data
-accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
-accdat <- readMWRacc(accpth)
-
-# import frequency and completeness data
-frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
-frecomdat <- readMWRfrecom(frecompth)
-
-# import site data
-sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
-sitdat <- readMWRsites(sitpth)
-
-# import WQX meta data
-wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
-wqxdat <- readMWRwqx(wqxpth)
-
-# a list of input data frames
-fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
-
-
-## ---- fig.height = 3, fig.width = 6, echo = T, out.width = '100%'-------------
[…]

### 2023-07-07 paper.Rmd
finished qc section

@@
 Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
-Each prefix also includes `MWR` to avoid namespace conflicts with other packages.
+Each prefix also includes `MWR` to avoid namespace conflicts with other packages (e.g., `readMWR`).
 
@@
 Parameters shown in red or marked as 'MISS' failed the data quality objectives.
-Users can edit the Word file as needed, e.g., entering the organization name or adding additional notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '100%'}
-knitr::include_graphics('figs/qcex.png')
+Users can edit the Word file as needed, e.g., entering the organization name or adding notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '50%', fig.show='hold'}
+knitr::include_graphics('figs/qcreview1.png')
+knitr::include_graphics('figs/qcreview2.png')
 ```
@@
 
-The cellsin red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
-All other parameters and checks in green had enough QC records to satisify the DQOs.
+The cells in red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
+All other parameters and checks in green had enough QC records to satisfy the DQOs.
 Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicate for dissolved oxygen.
@@
 
-Detailed information about the QC checks for an individual parameter can be obtained...
+Detailed information about the QC checks for an individual parameter can be obtained by changing the arguments to any of the `tab` functions.
+For example, the results for every field blank check and every parameter can be obtained as follows by changing the `type` and `accchk` arguments.
+This is the same information that is summarized using `type = "summary"` or `type = "percent"`.
+
+```{r}
+tabMWRacc(res = resdat, acc = accdat, frecom = frecomdat, type = "individual", 
+          accchk = "Field Blanks", warn = FALSE)
+```
+
+The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
+Only one sample sample for total phosphorus (TP) was at or above the threshold on July 17th.
+
+Additional functions for creating QC tables include `tabMWRfre()` for assessing if a sufficient number of QC samples are available and `tabMWRcom()` for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
+As with all the QC functions, these can be used individually within an R session to quickly view QC results or the `qcMWRreview()` function can be used to create a complete report that combines results from the individual functions.
+The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
 
 ## Analysis
+
+The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
+Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom routines.
+As such, the analysis function were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
 

### 2023-07-07 paper.tex
finished qc section

--- 2023-07-04 paper.tex
@@
 
-table xx
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.70in}|p{3.00in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}}
+
+\caption{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-1.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-2.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-3.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-4.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-5.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-6.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-7.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-8.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-9.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-10.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-11.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-12.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-13.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
 
@@
 Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
-Each prefix also includes \texttt{MWR} to avoid namespace conflicts with other packages.
+Each prefix also includes \texttt{MWR} to avoid namespace conflicts with other packages (e.g., \texttt{readMWR}).
 
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{figs/qcex} \caption{The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+\includegraphics[width=0.5\linewidth]{figs/qcreview1} \includegraphics[width=0.5\linewidth]{figs/qcreview2} \caption{The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
 The first page shows the data quality objectives for accuracy, frequency, and completeness.
@@
 Parameters shown in red or marked as 'MISS' failed the data quality objectives.
-Users can edit the Word file as needed, e.g., entering the organization name or adding additional notes.}\label{fig:qcex}
+Users can edit the Word file as needed, e.g., entering the organization name or adding notes.}\label{fig:qcex}
 \end{figure}
@@
 \begin{longtable}[c]{|p{2.44in}|p{1.41in}|p{1.82in}|p{1.52in}|p{1.26in}}
-
-\ascline{1.5pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\%\ Acceptance}}} \\
-
-\ascline{1.5pt}{666666}{1-5}\endfirsthead
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Spike/Check\ Accuracy}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
 \hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endhead
@@
 
-Detailed information about the QC checks for an individual parameter can be obtained\ldots{}
+Detailed information about the QC checks for an individual parameter can be obtained by changing the arguments to any of the \texttt{tab} functions.
+For example, the results for every field blank check and every parameter can be obtained as follows by changing the \texttt{type} and \texttt{accchk} arguments.
+This is the same information that is summarized using \texttt{type\ =\ "summary"} or \texttt{type\ =\ "percent"}.
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{1.00in}|p{1.07in}|p{0.55in}|p{0.91in}|p{1.21in}|p{0.83in}}
+
+\caption{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Hit/Miss}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-13}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-18}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-01}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-29}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{MISS}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
+Only one sample sample for total phosphorus (TP) was at or above the threshold on July 17th.
+
+Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if a sufficient number of QC samples are available and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
+As with all the QC functions, these can be used individually within an R session to quickly view QC results or the \texttt{qcMWRreview()} function can be used to create a complete report that combines results from the individual functions.
+The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
 
@@
 \subsection{Analysis}\label{analysis}}
+
+The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
+Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom routines.
+As such, the analysis function were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
 

### 2023-07-07 paper.R

@@ -17,3 +17,90 @@ knitr::include_graphics('figs/workflow.png')
 ## ----filreqhtml, eval = knitr::is_html_output()-------------------------------
 #> filerequirements
 
+## ----filreqpdf, eval = knitr::is_latex_output(), results = 'asis'-------------
+flextable_to_rmd(filerequirements)
+
+
+## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'----
+knitr::include_graphics('figs/importflow.png')
+
+
+## ---- echo = T, message = T---------------------------------------------------
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+
+## ---- error = T, echo = T, message = T----------------------------------------
+chk <- resdat
+chk[4, 2] <- "Sample"
+chk[135, 2] <- "Field"
+checkMWRresults(chk)
+
+
+## ---- results = 'hide', echo = T----------------------------------------------
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+# import accuracy data
+accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
+accdat <- readMWRacc(accpth)
+
+# import frequency and completeness data
+frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
+frecomdat <- readMWRfrecom(frecompth)
+
+# import site data
+sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
+sitdat <- readMWRsites(sitpth)
+
+# import WQX meta data
+wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
+wqxdat <- readMWRwqx(wqxpth)
+
+# a list of input data frames
[…]

### 2023-07-09 paper.Rmd
flextable issue fixed by adding latex dependencies

@@
 bibliography: RJreferences.bib
-
+preamble: |
+  \usepackage{multirow}
+  \usepackage{multicol}
+  \usepackage{colortbl}
+  \usepackage{hhline}
+  \newlength\Oldarrayrulewidth
+  \newlength\Oldtabcolsep
+  \usepackage{longtable}
+  \usepackage{array}
+  \usepackage{hyperref}
+  \usepackage{float}
+  \usepackage{wrapfig}\usepackage{longtable}
 ---
@@
 
+add_latex_dep()
 load(file = here('tabs/filerequirements.RData'))
@@
 
-The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:`r ifelse(knitr::is_html_output(), 'filreqhtml', 'filreqpdf')`), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
+The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filereq), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
 The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
@@
 
-```{r filreqhtml, eval = knitr::is_html_output()}
+```{r filreq}
 filerequirements
-```
-```{r filreqpdf, eval = knitr::is_latex_output(), results = 'asis'}
-flextable_to_rmd(filerequirements)
 ```

### 2023-07-09 paper.tex
flextable issue fixed by adding latex dependencies

@@
 
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+
 \ascline{1.5pt}{666666}{1-6}\endhead
@@
 
+\ascline{1.5pt}{666666}{1-5}\endfirsthead
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 2.44in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.52in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.26in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\%\ Acceptance}}} \\
+
 \ascline{1.5pt}{666666}{1-5}\endhead
@@
 \begin{longtable}[c]{|p{1.41in}|p{1.30in}|p{1.22in}|p{1.04in}|p{0.96in}|p{1.81in}}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.04in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.96in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.81in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
 
@@
 \caption{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.21in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.83in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Hit/Miss}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
 

### 2023-07-09 paper.R

@@ -7,6 +7,7 @@ library(MassWateR)
 library(flextable)
 library(here)
 
+add_latex_dep()
 load(file = here('tabs/filerequirements.RData'))
 
 

### 2023-07-10 paper.Rmd
added analysis section

@@
 library(flextable)
+library(dplyr)
 library(here)
 
-add_latex_dep()
+flextable::set_flextable_defaults(font.size = 7, padding = 0)
+
 load(file = here('tabs/filerequirements.RData'))
@@
 This paper describes the \CRANpkg{MassWateR} package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
-The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection and data submitted to the national WQX database.
+The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection (MADEP) and data submitted to the national WQX database.
 Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected elsewhere.
@@
 
-The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filereq), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
+The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filreq), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
 The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
@@
 ```{r filreq}
-filerequirements
+filerequirements %>% fontsize(part = 'all', size = 9)
 ```
@@
 ```{r, echo = T}
-anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", 
+  outliers = TRUE)
 ```
@@
 # create word output
-anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', output_dir = getwd())
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', 
+  output_dir = getwd())
 
 # create png output
-anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', output_dir = getwd())
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', 
+  output_dir = getwd())
 ```
@@
 The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
-Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom routines.
-As such, the analysis function were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
+Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom visualization routines.
+As such, the analysis functions were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
+Several default settings described below allow further customization of the output as desired by the user.
+The four primary analysis functions can be used to analyze seasonal trends, trends by date, date by site, and spatially using maps.
+
+Seasonal trends can be evaluated using the `anlzMWRseason()` function that summarizes results for a single parameter using boxplots or barplots with seasonal groups assigned to months or weeks of the year.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Below demonstrates a jittered boxplot of dissolved oxygen observations by month.
+
+```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
+  group = "month", type = "jitterbox")
+```
+
+The arguments specify different options available for the plot, including which parameter to plot in the results file (`param`), the type of threshold lines to show (`thresh`), the grouping, and the type of plot (jittered points over boxplots).
+The `thresh` argument in particular is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
+The `thresholdMWR` data object included with the package includes thresholds for ten common parameters that are either regulatory standards or recommended safe limits for different designated uses in freshwater or marine environments.
+Each threshold includes a source that is displayed in the legend above the plot.
+In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
+Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with `geom_hline()`).
+
+The y-axis scaling of the plot is also determined automatically from the data inputs.
+The DQO file for accuracy includes information on the distribution of each parameter, i.e., parameters with "log" in any of the columns are plotted on log10-scale, otherwise arithmetic.
+This behavior is controlled by the `yscl` argument, where the default is `"auto"` that indicates information on scaling is obtained automatically from the DQO file.
+Setting `yscl = "linear"` or `yscl = "log"` will set the axis as linear or log10-scale, respectively, regardless of the information in the DQO file.
+
+The `anlzMWRdate()` function plots results continuous in time on the date the samples or measurements were collected.
+This information can be use evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
+In the former case, individual points and lines are used for each site with appropriate labels.
+For the latter case, sites are aggregated and appropriate summary statistics are shown as the mean with 95% confidence intervals.
+Sites can be aggregated by sample dates or by "location groups" in the site metadata file.
+For example, all sites along the same river or tributary can be aggregated.
+The following demonstrates an aggregation of sites by the mainstem of the Assabet river and its tributaries using the `group = "locgroup"` argument.
+A user can specify any desired grouping in the `Location Group` column of the site metadata file.
+
+```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
+  thresh = 'fresh')
+```
+
+The `anlzMWRsite()` function can be used to view distributions of a parameter across sites.
+This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Results at each site can also be grouped by the `Result Attribute` column in the results file, where a user can enter arbitrary grouping criteria for samples.
+For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
+Individual sites can also be specified with the `site` argument.
+
+```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
+  site = c("ABT-026", "ABT-062", "ABT-077", "ABT-144", "ABT-237", "ABT-301"),
+  resultatt = c('DRY', 'WET'), byresultatt = TRUE)
+```
+
+Finally, maps of results at each site can be created with the `anlzMWRmap()` function.
+Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information as reference.
+For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the \CRANpkg{ggmap} package [@Kahle13].
+NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail in basemaps.
+These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
+Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) for including custom shapefiles.
+The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (`addwater = "medium"`).
+
+```{r fig.height = 6, fig.width = 6, echo = T, out.width = '100%'}
+anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
+```
+
+Samples and measurements across dates can be aggregated differently using the `sumfun` argument.
+If `sumfun = "auto"` (default), the mean is used where the distribution is determined automatically from the DQO file for accuracy, i.e., parameters with `"log"` in any of the columns are summarized with the geometric mean, otherwise arithmetic.
+Any other valid R summary function will be applied if passed to `sumfun` (`"mean"`, `"geomean"`, `"median"`, `"min"`, `"max"`).
+This argument also applies to other analysis functions where the data can be aggregated across dates or locations.
 
 ## Data submission
+
+The last
 

### 2023-07-10 paper.tex
added analysis section

--- 2023-07-05 paper.tex
@@
 
-The required data files for using \CRANpkg{MassWateR} are shown in Table \ref{tab:filreqpdf}, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
+The required data files for using \CRANpkg{MassWateR} are shown in Table \ref{tab:filreq}, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
 The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
@@
 
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
 \setlength{\tabcolsep}{0pt}
@@
 
-\providecommand{\ascline}[3]{\noalign{\global\Oldarrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
 
-\begin{longtable}[c]{|p{0.70in}|p{3.00in}|p{0.70in}|p{0.70in}|p{0.70in}|p{0.70in}}
+\begin{longtable}[c]{|p{0.60in}|p{2.50in}|p{0.60in}|p{0.60in}|p{0.60in}|p{0.60in}}
 
-\caption{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
+\caption{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
 
-\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
+\ascline{1.5pt}{666666}{1-6}
 
-\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
 
-\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
 
-\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
+\ascline{1.5pt}{666666}{1-6}
 
-\multicolumn{1}{>{\raggedright}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
 
-\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}\endhead
+\ascline{1.5pt}{666666}{1-6}\endhead
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-1.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-2.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-3.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-4.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Results}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Water\ quality\ results\ organized\ by\ sample\ location\ and\ date}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-1.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-2.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-3.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-4.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-5.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-6.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-7.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-8.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ accuracy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ accuracy\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-5.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-6.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-7.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-8.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-9.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-10.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{DQO\ frequency\ and\ completeness}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Summary\ of\ data\ quality\ objectives\ that\ describe\ quality\ control\ frequency\ and\ completeness\ measures\ for\ data\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-9.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-10.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-11.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-12.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-13.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{Sites}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ site\ metadata\ file,\ including\ location\ names,\ latitude,\ longitude,\ and\ additional\ grouping\ factors\ for\ sites\ in\ the\ results\ file}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-11.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-12.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-13.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreqpdf-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.7in+0\Oldtabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
-\noalign{\global\Oldarrayrulewidth 1.5pt}\arrayrulecolor[HTML]{666666}\cline{1-6}
+\ascline{1.5pt}{666666}{1-6}
 
@@
 
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
 \renewcommand*{\arraystretch}{1}
+
+The following sections describe the basic approach to using functions in \CRANpkg{MassWateR} for any of the processes in the workflow.
+The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
+Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
+Each prefix also includes \texttt{MWR} to avoid namespace conflicts with other packages (e.g., \texttt{readMWR}).
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{read}: Read input files
+\item
+  \texttt{check}: Check input files for formatting issues, used internally to the read functions
+\item
+  \texttt{form}: Format input files for downstream functions, used internally to the read functions once the checks have passed
+\item
+  \texttt{anlz}: Analyze imported data
+\item
+  \texttt{tab}: Create formatted tables for QC analysis
+\item
+  \texttt{qc}: QC functions for summarizing QC results, used internally to the table functions
+\item
+  \texttt{util}: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
+\end{itemize}
+
+Additionally, functions may often include a suffix that describes the relevant file used as input or otherwise evaluated in a downstream function.
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{results}: The results input file
+\item
+  \texttt{acc}: The data quality objectives file for accuracy
+\item
+  \texttt{frecom}: The data quality objectives file for frequency and completeness
+\item
+  \texttt{sites}: The site metadata file
+\item
+  \texttt{wqx}: The WQX metadata file
+\end{itemize}
+
+\hypertarget{functions}{%
+\section{\texorpdfstring{\CRANpkg{MassWateR} functions}{ functions}}\label{functions}}
+
+\hypertarget{read-and-check-files}{%
+\subsection{Read and check files}\label{read-and-check-files}}
+
+The primary task of the \texttt{read} functions is to ensure all imported files follow the required format for the package.
+Excel files are the expected format for all inputs and the \texttt{read} functions use the \texttt{read\_excel} function from the \CRANpkg{readxl} package (Wickham and Bryan 2023).
+The \texttt{read} functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant \texttt{check} functions inside the \texttt{read} function.
+There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
+Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
+The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
+As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \ref{fig:importflow}).
+Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
+This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+A user only needs to format their data once to use the package.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.
+All read functions import an Excel file and the imported file is then passed to a check function.
+The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.}\label{fig:importflow}
+\end{figure}
+
+A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that are performed and that all checks were successful.
+Below demonstrates what would be shown for the results file using an example dataset included with the package.
+A total of fifteen checks are applied to the results file.
+
+\begin{verbatim}
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+\end{verbatim}
+
+\begin{verbatim}
+#> Running checks on results data...
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking column names... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking all required columns are present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking valid Activity Types... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Start Date formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking depth data present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking for non-numeric values in Activity Depth/Height Measure... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Depth/Height Unit... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Activity Relative Depth Name formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking values in Activity Depth/Height Measure > 1 m / 3.3 ft... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Characteristic Name formats... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking Result Values... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking QC Reference Values... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking for missing entries for Result Unit... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking if more than one unit per Characteristic Name... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking acceptable units for each entry in Characteristic Name... OK
+\end{verbatim}
+
+\begin{verbatim}
+#> 
+#> All checks passed!
+\end{verbatim}
+
+The following shows a typical error that might be returned if a check fails importing the results file.
+The \texttt{resdat} object is an imported results file that has passed all checks, but incorrect entries are added to the \texttt{chk} object to demonstrate the error that is returned if a user would have attempted to import this file.
+The \texttt{checkMWRresults()} function is run inside the \texttt{readMWRresults()} function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the \texttt{Activity\ Type} column are found.
+In this example, a user would need to change the entries in rows 4 and 135 of the \texttt{Activity\ Type} column in their Excel file to fix the issue and import the file again as in Figure \ref{fig:importflow}.
+The online \href{https://massbays-tech.github.io/MassWateR/articles/inputs.html\#data-import-and-checks}{vignette} specifies the valid entries.
+
+\begin{verbatim}
+chk <- resdat
+chk[4, 2] <- "Sample"
+chk[135, 2] <- "Field"
+checkMWRresults(chk)
+\end{verbatim}
+
+\begin{verbatim}
+#> Running checks on results data...
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking column names... OK
+\end{verbatim}
+
+\begin{verbatim}
+#>  Checking all required columns are present... OK
+\end{verbatim}
+
+\begin{verbatim}
+#> Error:   Checking valid Activity Types...
+#>  Incorrect Activity Type found: Sample, Field in row(s) 4, 135
+\end{verbatim}
+
+The \texttt{readMWRresultsview()} function is also available to assist with troubleshooting formatting issues for the results file.
+This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
+The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
+
+After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
+In the latter case, a path or data object can be used as input for each file.
+For the former approach, the beginning of a script for using the package could appear as follows.
+Example files included with the package are imported, whereas a user will specify paths to their own files.
+
+\begin{verbatim}
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+# import accuracy data
+accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
+accdat <- readMWRacc(accpth)
+
+# import frequency and completeness data
+frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
+frecomdat <- readMWRfrecom(frecompth)
+
+# import site data
+sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
+sitdat <- readMWRsites(sitpth)
+
+# import WQX meta data
+wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
+wqxdat <- readMWRwqx(wqxpth)
+
+# a list of input data frames
+fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
+\end{verbatim}
+
+The object \texttt{fsetls} can then be used as input to downstream functions.
+
+A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
+The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
+On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
+The list includes 43 different parameters, each with multiple valid units of measurement.
+Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
+It is not an unreasonable expectation for users to provide only one unit of measurement per parameter.
+Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
+
+An additional set of functions can be used to check for outliers in the results file.
+Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
+Identifying and potentially removing or correcting outliers is a critical part of quality control.
+The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct outliers.
+
+The \texttt{anlzMWRoutlier()} function uses the results file and data quality objectives for accuracy to plot potential outliers by month.
+The accuracy file is used to automatically identify the y-axis scaling (as arithmetic or log) and to replace concentrations with appropriate values for those labelled as beyond detection.
+Outliers are defined using the standard definition of 1.5 times the interquartile range (the 25th to 75th percentile) of a parameter and can be visually identified as points above or below the whiskers in the boxplots.
+The station name for a point is also shown.
+The \texttt{param} specifies the water quality parameter to evaluate and the \texttt{group} argument specifies how the boxplots are grouped (by year, month, week, or station).
+In the following example, three stations are identified as potential outliers for the respective month.
+
+\begin{verbatim}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1}
+
+The outliers in the above plot can also be viewed as tabular output using \texttt{outliers\ =\ TRUE} to aid in their identification.
+
+\begin{verbatim}
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", 
+  outliers = TRUE)
+\end{verbatim}
+
+\begin{verbatim}
+#> # A tibble: 3 x 6
+#>   `Monitoring Location ID` `Activity Start Date` `Activity Start Time`
+#>   <chr>                    <dttm>                <chr>                
+#> 1 ELZ-004                  2022-05-15 00:00:00   06:50                
+#> 2 HOP-011                  2022-05-15 00:00:00   06:55                
+#> 3 ELZ-004                  2022-09-11 00:00:00   07:20                
+#> # i 3 more variables: `Characteristic Name` <chr>, `Result Value` <dbl>,
+#> #   `Result Unit` <chr>
+\end{verbatim}
+
+A user can also evaluate outliers for every water quality parameter in the results file.
+The \texttt{anlzMWRoutlierall()} function creates a Word document with images of boxplots for every parameter created with \texttt{anlzMWRoutlier()}.
+Images for each parameter can also be created as standalone files.
+The \texttt{param} argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
+The following shows how to use the function by creating a single Word file or individual image files in the working directory.
+
+\begin{verbatim}
+# create word output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', 
+  output_dir = getwd())
+
+# create png output
+anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'png', 
+  output_dir = getwd())
+\end{verbatim}
+
+As in Figure \ref{fig:importflow}, a user can identify outliers from the results, modify the file in Excel, and import the file again for further QC reporting or analysis.
+
+\hypertarget{quality-control-reporting}{%
+\subsection{Quality Control reporting}\label{quality-control-reporting}}
+
+The quality control functions in \CRANpkg{MassWateR} are designed to create a single report that compares the water quality data in the results file (\texttt{resdat}) to data quality objectives in the accuracy (\texttt{accdat}) and frequency and completeness (\texttt{frecomdat}) files.
+In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
+The QC checks for frequency and completeness evaluate if a sufficient number of records in the results file satisfy the accuracy checks and that sufficient QC data have been collected.
+The values in the \texttt{accdat} and \texttt{frecomdat} inputs are collectively described as data quality objectives (DQOs), such that the QC samples in \texttt{resdat} must satisfy these objectives to be considered accurate and precise data for use in regulatory or other assessments by water quality professionals.
+
+The \texttt{qcMWRreview()} function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the \texttt{accdat} and \texttt{frecomdat} input files.
+This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describe relevant evaluations for the QC assessment.
+The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
+A user can then further edit the Word document as needed.
+The first two pages of the QC report are shown in Figure \ref{fig:qcex}.
+
+\begin{verbatim}
+qcMWRreview(fset = fsetls, output_dir = getwd())
+\end{verbatim}
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{figs/qcreview1} \includegraphics[width=0.5\linewidth]{figs/qcreview2} \caption{The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+The first page shows the data quality objectives for accuracy, frequency, and completeness.
+The second page shows QC results for frequency and completeness.
+Parameters shown in red or marked as 'MISS' failed the data quality objectives.
+Users can edit the Word file as needed, e.g., entering the organization name or adding notes.}\label{fig:qcex}
+\end{figure}
+
+The QC report is built using several functions that can be used individually as needed.
+In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) table objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
+For example, the \texttt{tabMWRacc()} function evaluates accuracy checks for field duplicates, lab duplicates, field blanks, lab blanks, and lab spikes/instrument checks for QC records in the results file based on DQOs in the accuracy file.
+The function can return a summary of all checks as follows:
+
+\begin{verbatim}
+tabMWRacc(fset = fsetls, type = "summary")
+\end{verbatim}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{1.47in}|p{0.82in}|p{1.08in}|p{0.88in}|p{0.72in}}
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
+
+\ascline{1.5pt}{666666}{1-5}\endfirsthead
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
+
+\ascline{1.5pt}{666666}{1-5}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{75\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{DO}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{80\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{94\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{16}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{91\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{86\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Spikes\ /\ Instrument\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{9}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{90\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{20}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{19}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
+
+\ascline{1.5pt}{666666}{1-5}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The table shows the types and amounts of QC checks applied to each parameter and which of those checks did not satisfy the DQOs in the accuracy file.
+For example, there were four field duplicate records for ammonia in the results file and only one of those records included a duplicate value outside of the acceptable range, i.e., there was a 75\% acceptance rate for the four field duplicate records.
+This same table can be viewed relative to the applicable frequency rate for the amount of passing checks considered to be appropriate for the QC records as identified in the frequency and completeness DQO file.
+
+\begin{verbatim}
+tabMWRacc(fset = fsetls, type = "percent")
+\end{verbatim}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.82in}|p{0.74in}|p{0.69in}|p{0.58in}|p{0.53in}|p{1.07in}}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{75\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{86\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{DO}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{90\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{94\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{DB4325}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{80\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{91\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\%}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{57C4AD}\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\%}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The cells in red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
+All other parameters and checks in green had enough QC records to satisfy the DQOs.
+Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicate for dissolved oxygen.
+The empty cells are typically for QC checks that do not readily apply to a parameter.
+For example, dissolved oxygen is measured in the field with monitoring equipment with no lab processing, such that lab QC checks are not relevant.
+
+Detailed information about the QC checks for an individual parameter can be obtained by changing the arguments to any of the \texttt{tab} functions.
+For example, the results for every field blank check and every parameter can be obtained as follows by changing the \texttt{type} and \texttt{accchk} arguments.
+This is the same information that is summarized using \texttt{type\ =\ "summary"} or \texttt{type\ =\ "percent"}.
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.55in}|p{0.60in}|p{0.27in}|p{0.50in}|p{0.69in}|p{0.45in}}
+
+\caption{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endhead
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-13}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-18}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-01}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-29}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{MISS}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
+Only one sample sample for total phosphorus (TP) was at or above the threshold on July 17th.
+
+Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if a sufficient number of QC samples are available and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
+As with all the QC functions, these can be used individually within an R session to quickly view QC results or the \texttt{qcMWRreview()} function can be used to create a complete report that combines results from the individual functions.
+The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
+
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
+Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom visualization routines.
+As such, the analysis functions were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
+Several default settings described below allow further customization of the output as desired by the user.
+The four primary analysis functions can be used to analyze seasonal trends, trends by date, date by site, and spatially using maps.
+
+Seasonal trends can be evaluated using the \texttt{anlzMWRseason()} function that summarizes results for a single parameter using boxplots or barplots with seasonal groups assigned to months or weeks of the year.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Below demonstrates a jittered boxplot of dissolved oxygen observations by month.
+
+\begin{verbatim}
+anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
+  group = "month", type = "jitterbox")
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1}
+
+The arguments specify different options available for the plot, including which parameter to plot in the results file (\texttt{param}), the type of threshold lines to show (\texttt{thresh}), the grouping, and the type of plot (jittered points over boxplots).
+The \texttt{thresh} argument in particular is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
+The \texttt{thresholdMWR} data object included with the package includes thresholds for ten common parameters that are either regulatory standards or recommended safe limits for different designated uses in freshwater or marine environments.
+Each threshold includes a source that is displayed in the legend above the plot.
+In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
+Threshold lines can be suppressed (\texttt{thresh\ =\ "none"}) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with \texttt{geom\_hline()}).
+
+The y-axis scaling of the plot is also determined automatically from the data inputs.
+The DQO file for accuracy includes information on the distribution of each parameter, i.e., parameters with ``log'' in any of the columns are plotted on log10-scale, otherwise arithmetic.
+This behavior is controlled by the \texttt{yscl} argument, where the default is \texttt{"auto"} that indicates information on scaling is obtained automatically from the DQO file.
+Setting \texttt{yscl\ =\ "linear"} or \texttt{yscl\ =\ "log"} will set the axis as linear or log10-scale, respectively, regardless of the information in the DQO file.
+
+The \texttt{anlzMWRdate()} function plots results continuous in time on the date the samples or measurements were collected.
+This information can be use evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
+In the former case, individual points and lines are used for each site with appropriate labels.
+For the latter case, sites are aggregated and appropriate summary statistics are shown as the mean with 95\% confidence intervals.
+Sites can be aggregated by sample dates or by ``location groups'' in the site metadata file.
+For example, all sites along the same river or tributary can be aggregated.
+The following demonstrates an aggregation of sites by the mainstem of the Assabet river and its tributaries using the \texttt{group\ =\ "locgroup"} argument.
+A user can specify any desired grouping in the \texttt{Location\ Group} column of the site metadata file.
+
+\begin{verbatim}
+anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
+  thresh = 'fresh')
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1}
+
+The \texttt{anlzMWRsite()} function can be used to view distributions of a parameter across sites.
+This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Results at each site can also be grouped by the \texttt{Result\ Attribute} column in the results file, where a user can enter arbitrary grouping criteria for samples.
+For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
+Individual sites can also be specified with the \texttt{site} argument.
+
+\begin{verbatim}
+anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
+  site = c("ABT-026", "ABT-062", "ABT-077", "ABT-144", "ABT-237", "ABT-301"),
+  resultatt = c('DRY', 'WET'), byresultatt = TRUE)
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1}
+
+Finally, maps of results at each site can be created with the \texttt{anlzMWRmap()} function.
+Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information as reference.
+For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the \CRANpkg{ggmap} package (Kahle and Wickham 2013).
+NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail in basemaps.
+These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
+Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html\#modifying-masswater-plots}{vignette} for including custom shapefiles.
+The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (\texttt{addwater\ =\ "medium"}).
+
+\begin{verbatim}
+anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
+\end{verbatim}
+
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1}
+
+Samples and measurements across dates can be aggregated differently using the \texttt{sumfun} argument.
+If \texttt{sumfun\ =\ "auto"} (default), the mean is used where the distribution is determined automatically from the DQO file for accuracy, i.e., parameters with \texttt{"log"} in any of the columns are summarized with the geometric mean, otherwise arithmetic.
+Any other valid R summary function will be applied if passed to \texttt{sumfun} (\texttt{"mean"}, \texttt{"geomean"}, \texttt{"median"}, \texttt{"min"}, \texttt{"max"}).
+This argument also applies to other analysis functions where the data can be aggregated across dates or locations.
+
+\hypertarget{data-submission}{%
+\subsection{Data submission}\label{data-submission}}
+
+\hypertarget{building-a-community-and-future-work}{%
+\section{Building a community and future work}\label{building-a-community-and-future-work}}
+
+All developers hope that their package is used by the intended audience. To ensure this for \CRANpkg{MassWateR}, a community of practice was\ldots{}
+
+Building the community of practice\ldots{}
+
+MassWater in other locations, expansion elsewhere
+
+Inclusion of historical data
+
+Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.
+
+\hypertarget{summary}{%
+\section{Summary}\label{summary}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Gohel23}{}}%
+Gohel, David, and Panagiotis Skintzos. 2023. \emph{Flextable: Functions for Tabular Reporting}. \url{https://CRAN.R-project.org/package=flextable}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kahle13}{}}%
+Kahle, David, and Hadley Wickham. 2013. {``Ggmap: Spatial Visualization with Ggplot2.''} \emph{The R Journal} 5 (1): 144--61. \url{https://journal.r-project.org/archive/2013-1/kahle-wickham.pdf}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kelly22}{}}%
@@
 Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham23}{}}%
+Wickham, Hadley, and Jennifer Bryan. 2023. \emph{Readxl: Read Excel Files}. \url{https://CRAN.R-project.org/package=readxl}.
 

### 2023-07-10 R/tabs.R

@@ -23,8 +23,8 @@ tab <- flextable(totab) %>%
   colformat_image(j = 4, i = colind[[2]], width = imgsz, height = imgsz) %>% 
   colformat_image(j = 5, i = colind[[3]], width = imgsz, height = imgsz) %>% 
   colformat_image(j = 6, i = colind[[4]], width = imgsz, height = imgsz) %>% 
-  width(j = 2, width = 3) %>%
-  width(j = c(1, 3:6), width = 3.5 / 5) %>% 
+  width(j = 2, width = 2.5) %>%
+  width(j = c(1, 3:6), width = 3 / 5) %>%
   bold(part = 'header') %>%
   colformat_double(digits = 2) %>%
   valign(valign = 'top', part = 'header') %>%

### 2023-07-10 paper.R

@@ -5,9 +5,11 @@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 library(MassWateR)
 library(flextable)
+library(dplyr)
 library(here)
 
-add_latex_dep()
+flextable::set_flextable_defaults(font.size = 7, padding = 0)
+
 load(file = here('tabs/filerequirements.RData'))
 
 
@@ -15,11 +17,8 @@ load(file = here('tabs/filerequirements.RData'))
 knitr::include_graphics('figs/workflow.png')
 
 
-## ----filreqhtml, eval = knitr::is_html_output()-------------------------------
-#> filerequirements
-
-## ----filreqpdf, eval = knitr::is_latex_output(), results = 'asis'-------------
-flextable_to_rmd(filerequirements)
+## ----filreq-------------------------------------------------------------------
+filerequirements %>% fontsize(part = 'all', size = 9)
 
 
 ## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'----
@@ -73,15 +72,18 @@ anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
 
 
 ## ---- echo = T----------------------------------------------------------------
-anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", outliers = TRUE)
+anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", 
+  outliers = TRUE)
 
 
 ## ---- echo = T, eval = F------------------------------------------------------
 #> # create word output
-#> anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word', output_dir = getwd())
+#> anlzMWRoutlierall(fset = fsetls, group = 'month', format = 'word',
+#>   output_dir = getwd())
 #> 
 #> # create png output
[…]

### 2023-07-10 paper.Rmd
added wqx section

@@
 
-The last
+The last part of the \CRANpkg{MassWateR} workflow is preparation of data for submission to WQX.
+A single function, `tabMWRwqx()`, is provided to format data inputs using a template designed for data submission.
+This function will export a single Excel workbook with three sheets, named "Project", "Locations", and "Results", all of which are required for data submission.
+The output is populated with as much content as possible based on information in the input files.
+The remainder of the information not included in the output will need to be manually entered before uploading the data to WQX.
+All required columns are present, but individual rows will need to be verified for completeness.
+It is the responsibility of the user to verify this information is complete and correct before uploading the data.
+
+The workbook can be created as follows by including the required files and specifying an output directory where the Excel file is saved.
+Once the function is done running, a message indicating success and where the file is located is returned.
+
+```{r, echo = T, eval = F}
+tabMWRwqx(fset = fsetls, output_dir = getwd())
+#> Excel workbook created successfully! File located at /tmp/RtmpBrk9nw/wqxtab.xlsx
+```
+
+Additional templates and instructions for data submission are available on the [package website](https://massbays-tech.github.io/MassWateR/index.html).
+It is assumed that users are familiar with the WQX data submission portal if they are already using the package.
+\CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX) as the user base for the package increases.
 

### 2023-07-10 paper.tex
added wqx section

@@
 
+The last part of the \CRANpkg{MassWateR} workflow is preparation of data for submission to WQX.
+A single function, \texttt{tabMWRwqx()}, is provided to format data inputs using a template designed for data submission.
+This function will export a single Excel workbook with three sheets, named ``Project'', ``Locations'', and ``Results'', all of which are required for data submission.
+The output is populated with as much content as possible based on information in the input files.
+The remainder of the information not included in the output will need to be manually entered before uploading the data to WQX.
+All required columns are present, but individual rows will need to be verified for completeness.
+It is the responsibility of the user to verify this information is complete and correct before uploading the data.
+
+The workbook can be created as follows by including the required files and specifying an output directory where the Excel file is saved.
+Once the function is done running, a message indicating success and where the file is located is returned.
+
+\begin{verbatim}
+tabMWRwqx(fset = fsetls, output_dir = getwd())
+#> Excel workbook created successfully! File located at /tmp/RtmpBrk9nw/wqxtab.xlsx
+\end{verbatim}
+
+Additional templates and instructions for data submission are available on the \href{https://massbays-tech.github.io/MassWateR/index.html}{package website}.
+It is assumed that users are familiar with the WQX data submission portal if they are already using the package.
+\CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX) as the user base for the package increases.
+
 \hypertarget{building-a-community-and-future-work}{%

### 2023-07-10 paper.R

@@ -127,3 +127,8 @@ anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box",
 ## ----fig.height = 6, fig.width = 6, echo = T, out.width = '100%'--------------
 anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
 
+
+## ---- echo = T, eval = F------------------------------------------------------
+#> tabMWRwqx(fset = fsetls, output_dir = getwd())
+#> #> Excel workbook created successfully! File located at /tmp/RtmpBrk9nw/wqxtab.xlsx
+

### 2023-07-10 paper.Rmd
added community and future work section

@@
 The last part of the \CRANpkg{MassWateR} workflow is preparation of data for submission to WQX.
-A single function, `tabMWRwqx()`, is provided to format data inputs using a template designed for data submission.
+A single function, `tabMWRwqx()`, is provided to format data inputs using a [template](https://massbays-tech.github.io/MassWateR/RESOURCES.html) designed for data submission.
 This function will export a single Excel workbook with three sheets, named "Project", "Locations", and "Results", all of which are required for data submission.
@@
 The remainder of the information not included in the output will need to be manually entered before uploading the data to WQX.
-All required columns are present, but individual rows will need to be verified for completeness.
-It is the responsibility of the user to verify this information is complete and correct before uploading the data.
+All required columns are present, but individual rows must be verified for completeness and accuracy by the user before uploading the data.
 
@@
 It is assumed that users are familiar with the WQX data submission portal if they are already using the package.
-\CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX) as the user base for the package increases.
+\CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
 
@@
 
-All developers hope that their package is used by the intended audience.  To ensure this for \CRANpkg{MassWateR}, a community of practice was...
+To ensure that \CRANpkg{MassWateR} is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN.
+This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
+Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to the software, as well as use of \CRANpkg{MassWateR}.
+Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with \CRANpkg{MassWateR}.
+However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as \CRANpkg{ggplot2} to create additional visualizations for modifying the existing analysis plots in \CRANpkg{MassWateR}.
+For example, a [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html) was included on the package website to demonstrate how these plots can be modified for custom output using \CRANpkg{ggplot2}.
+Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about using the package and for others to view the discussion if similar issues were encountered.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplicative issues through sharing solutions in a public forum.
 
-Building the community of practice...
+As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
+First, some of the parameter thresholds applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+Users can simply omit the thresholds if they do not apply using `thresh = "none"` or add custom thresholds using standard \CRANpkg{ggplot2} functions.
+Second, the NHD waterbodies used by `anlzMWRmap()` are specific to watersheds in Massachusetts.
+Users can omit these layers from the plot using `addwater = NULL`, add a base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from \CRANpkg{ggplot2}.
+Third, the QC report created by `qcMWRreview()` uses a format vetted by MADEP.
+This format may not meet the requirements of other state organization, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
+Finally, minor components of the Excel file for WQX submission created by `tabMWRwqx()` are specific to Massachusetts.
+This includes the timezone for the `WQX Activity Start Time Zone` field and some default entries for sample collection methods that include `"MassWateR"` in the text.
+Each of these can also be modified by hand in the output file.
+Future enhancements and additions to \CRANpkg{MassWateR} will likely include automated tools to address these minor issues using the package outside of Massachusetts.
 
-MassWater in other locations, expansion elsewhere
-
-Inclusion of historical data
-
-Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.
+Additional future work to improve the functionality of \CRANpkg{MassWateR} is also expected as the user base increases and the functions mature with additional bug fixes or minor enhancements.
+Specifically, the inclusion of historical data for some of the analysis functions could provide additional context on status and trends for monitoring data at specific locations.
+This enhancement would require the extraction of existing data already included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
+Existing R packages already leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be usedby \CRANpkg{MassWateR}.
+A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed *in situ*.
+These data present additional challenges not encountered with routine samples collected at longer time intervals, including increased data volume and additional QC needs [@Wagner06; @Horsburgh15].
+For the latter, automated tools are needed for detecting and handling QC issues common with monitoring equipment deployed in the field for long duration, such as instrument drift, biofouling, or missing data.
+More complex methods for detecting outliers in continuous monitoring data beyond the existing tools in \CRANpkg{MassWateR} will also be needed [@Leigh19].
 

### 2023-07-10 paper.tex
added community and future work section

@@
 The last part of the \CRANpkg{MassWateR} workflow is preparation of data for submission to WQX.
-A single function, \texttt{tabMWRwqx()}, is provided to format data inputs using a template designed for data submission.
+A single function, \texttt{tabMWRwqx()}, is provided to format data inputs using a \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{template} designed for data submission.
 This function will export a single Excel workbook with three sheets, named ``Project'', ``Locations'', and ``Results'', all of which are required for data submission.
@@
 
-All developers hope that their package is used by the intended audience. To ensure this for \CRANpkg{MassWateR}, a community of practice was\ldots{}
-
-Building the community of practice\ldots{}
-
-MassWater in other locations, expansion elsewhere
-
-Inclusion of historical data
-
-Inclusion for continuous monitoring data, consider outlier anlaysis, drift, biofouling, etc.
+To ensure that \CRANpkg{MassWateR} is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN.
+This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
+Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an \href{https://massbays-tech.github.io/intro-to-r/}{introduction} to the software, as well as use of \CRANpkg{MassWateR}.
+Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with \CRANpkg{MassWateR}.
+However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as \CRANpkg{ggplot2} to create additional visualizations for modifying the existing analysis plots in \CRANpkg{MassWateR}.
+For example, a \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html}{vignette} was included on the package website to demonstrate how these plots can be modified for custom output using \CRANpkg{ggplot2}.
+Further, a \href{https://massbays.discourse.group/c/masswater-r-tools/5}{community forum} was created as a resource for users to post questions about using the package and for others to view the discussion if similar issues were encountered.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplicative issues through sharing solutions in a public forum.
+
+As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
+First, some of the parameter thresholds applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+Users can simply omit the thresholds if they do not apply using \texttt{thresh\ =\ "none"} or add custom thresholds using standard \CRANpkg{ggplot2} functions.
+Second, the NHD waterbodies used by \texttt{anlzMWRmap()} are specific to watersheds in Massachusetts.
+Users can omit these layers from the plot using \texttt{addwater\ =\ NULL}, add a base map using the \texttt{maptype} argument, or add custom waterbody layers as simple features objects (Pebesma and Bivand 2023) using the \texttt{geom\_sf()} function from \CRANpkg{ggplot2}.
+Third, the QC report created by \texttt{qcMWRreview()} uses a format vetted by MADEP.
+This format may not meet the requirements of other state organization, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
+Finally, minor components of the Excel file for WQX submission created by \texttt{tabMWRwqx()} are specific to Massachusetts.
+This includes the timezone for the \texttt{WQX\ Activity\ Start\ Time\ Zone} field and some default entries for sample collection methods that include \texttt{"MassWateR"} in the text.
+Each of these can also be modified by hand in the output file.
+Future enhancements and additions to \CRANpkg{MassWateR} will likely include automated tools to address these minor issues using the package outside of Massachusetts.
+
+Additional future work to improve the functionality of \CRANpkg{MassWateR} is also expected as the user base increases and the functions mature with additional bug fixes or minor enhancements.
+Specifically, the inclusion of historical data for some of the analysis functions could provide additional context on status and trends for monitoring data at specific locations.
+This enhancement would require the extraction of existing data already included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
+Existing R packages already leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be usedby \CRANpkg{MassWateR}.
+A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed \emph{in situ}.
+These data present additional challenges not encountered with routine samples collected at longer time intervals, including increased data volume and additional QC needs (Wagner et al.
+2006; Horsburgh et al.
+2015).
+For the latter, automated tools are needed for detecting and handling QC issues common with monitoring equipment deployed in the field for long duration, such as instrument drift, biofouling, or missing data.
+More complex methods for detecting outliers in continuous monitoring data beyond the existing tools in \CRANpkg{MassWateR} will also be needed (Leigh et al.
+2019).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Horsburgh15}{}}%
+Horsburgh, Jeffery S, Stephanie L Reeder, Amber Spackman Jones, and Jacob Meline.
+2015.
+{``Open Source Software for Visualization and Quality Control of Continuous Hydrologic and Water Quality Sensor Data.''} \emph{Environmental Modelling \& Software} 70: 32--44.
+\url{https://doi.org/10.1016/j.envsoft.2015.04.002}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kahle13}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Leigh19}{}}%
+Leigh, Catherine, Omar Alsibai, Rob J Hyndman, Sevvandi Kandanaarachchi, Olivia C King, James M McGree, Catherine Neelamraju, et al.
+2019.
+{``A Framework for Automated Anomaly Detection in High Frequency Water-Quality Data from in Situ Sensors.''} \emph{Science of the Total Environment} 664: 885--98.
+\url{https://doi.org/10.1016/j.scitotenv.2019.02.085}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pebesma23}{}}%
+Pebesma, Edzer, and Roger Bivand. 2023. \emph{{Spatial Data Science: With applications in R}}. {Chapman and Hall/CRC}. \url{https://r-spatial.org/book/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Schiff16}{}}%
@@
 \url{https://doi.org/10.1111/jawr.12108}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wagner06}{}}%
+Wagner, Richard J, Robert W Boulger Jr, Carolyn J Oblinger, and Brett A Smith.
+2006.
+{``Guidelines and Standard Procedures for Continuous Water-Quality Monitors: Station Operation, Record Computation, and Data Reporting.''} Techniques and Methods 1-D3.
+Version 1.0.
+Reston, VA: U.S.
+Geological Survey.
+\url{https://doi.org/10.3133/tm1D3}.
 

### 2023-07-12 paper.Rmd
added summary and acknowledgements

@@
 Specifically, the inclusion of historical data for some of the analysis functions could provide additional context on status and trends for monitoring data at specific locations.
-This enhancement would require the extraction of existing data already included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
-Existing R packages already leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be usedby \CRANpkg{MassWateR}.
+This enhancement would require the extraction of existing data included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
+Existing R packages leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be used by \CRANpkg{MassWateR}.
 A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed *in situ*.
@@
 
+The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how resource managers develop QC assessments and apply exploratory analyses to water quality monitoring data.
+The package can also expedite the preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
+These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessment of status and trends of environmental resources.
+As mentioned throughout this paper, \CRANpkg{MassWateR} was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in Figure \@ref(fig:workflow) can easily be applied to data collected elsewhere.
+Future development of the package will not only make the package functions more generalizable to other locations, but also provide additional features for working with continuous and historical monitoring data.
+The community of practice developed for \CRANpkg{MassWateR} is expected to grow and the package will be supported by the authors as the user base increases.
+
 # Acknowledgments
+
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bay Estuary Partnership.
+We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.

### 2023-07-12 paper.tex
added summary and acknowledgements

@@
 \caption{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
-
-\ascline{1.5pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
-
-\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
 
@@
 #>   `Monitoring Location ID` `Activity Start Date` `Activity Start Time`
-#>   <chr>                    <dttm>                <chr>                
-#> 1 ELZ-004                  2022-05-15 00:00:00   06:50                
-#> 2 HOP-011                  2022-05-15 00:00:00   06:55                
-#> 3 ELZ-004                  2022-09-11 00:00:00   07:20                
+#>   <chr>                    <date>                <chr>                
+#> 1 ELZ-004                  2022-05-15            06:50                
+#> 2 HOP-011                  2022-05-15            06:55                
+#> 3 ELZ-004                  2022-09-11            07:20                
 #> # i 3 more variables: `Characteristic Name` <chr>, `Result Value` <dbl>,
@@
 
-\ascline{1.5pt}{666666}{1-5}\endfirsthead
-
-\ascline{1.5pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
-
 \ascline{1.5pt}{666666}{1-5}\endhead
@@
 \begin{longtable}[c]{|p{0.82in}|p{0.74in}|p{0.69in}|p{0.58in}|p{0.53in}|p{1.07in}}
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Spike/Check\ Accuracy}}} \\
-
-\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
 
@@
 \caption{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
-
-\ascline{1.5pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
-
-\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
 
@@
 Specifically, the inclusion of historical data for some of the analysis functions could provide additional context on status and trends for monitoring data at specific locations.
-This enhancement would require the extraction of existing data already included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
-Existing R packages already leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be usedby \CRANpkg{MassWateR}.
+This enhancement would require the extraction of existing data included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
+Existing R packages leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be used by \CRANpkg{MassWateR}.
 A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed \emph{in situ}.
@@
 
+The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how resource managers develop QC assessments and apply exploratory analyses to water quality monitoring data.
+The package can also expedite the preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
+These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessment of status and trends of environmental resources.
+As mentioned throughout this paper, \CRANpkg{MassWateR} was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in Figure \ref{fig:workflow} can easily be applied to data collected elsewhere.
+Future development of the package will not only make the package functions more generalizable to other locations, but also provide additional features for working with continuous and historical monitoring data.
+The community of practice developed for \CRANpkg{MassWateR} is expected to grow and the package will be supported by the authors as the user base increases.
+
 \hypertarget{acknowledgments}{%
 \section{Acknowledgments}\label{acknowledgments}}
+
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bay Estuary Partnership.
+We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
 

### 2023-07-13 paper.Rmd
fix figure dimensions

@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-library(MassWateR)
+
 library(flextable)
@@
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'}
 knitr::include_graphics('figs/importflow.png')
@@
 ```{r, results = 'hide', echo = T}
-library(MassWateR)
-
 # import results data
@@
 
-```{r, fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+```{r, fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
 anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
@@
 
-```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
 anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
@@
 
-```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
 anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
@@
 
-```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
+```{r fig.height = 4, fig.width = 8, echo = T,  out.width = '95%', fig.align = 'center'}
 anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
@@
 
-```{r fig.height = 6, fig.width = 6, echo = T, out.width = '100%'}
+```{r fig.height = 5, fig.width = 5, echo = T, out.width = '95%', fig.align = 'center'}
 anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")

### 2023-07-13 paper.tex
fix figure dimensions

@@
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.}\label{fig:importflow}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).}\label{fig:importflow}
 \end{figure}
@@
 \begin{verbatim}
-library(MassWateR)
-
 # import results data
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1} \end{center}
 
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1} \end{center}
 
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1} \end{center}
 
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1} \end{center}
 
@@
 
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1} \end{center}
 

### 2023-07-13 paper.R

@@ -3,7 +3,7 @@
 
 ## ----setup, include=FALSE-----------------------------------------------------
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-library(MassWateR)
+
 library(flextable)
 library(dplyr)
 library(here)
@@ -21,7 +21,7 @@ knitr::include_graphics('figs/workflow.png')
 filerequirements %>% fontsize(part = 'all', size = 9)
 
 
-## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'----
+## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'----
 knitr::include_graphics('figs/importflow.png')
 
 
@@ -41,8 +41,6 @@ checkMWRresults(chk)
 
 
 ## ---- results = 'hide', echo = T----------------------------------------------
-library(MassWateR)
-
 # import results data
 respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
 resdat <- readMWRresults(respth)
@@ -67,7 +65,7 @@ wqxdat <- readMWRwqx(wqxpth)
 fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
 
 
[…]

### 2023-07-13 paper.Rmd
full draft done, not proofed

@@
 abstract: >
-  An abstract of less than 150 words.
+  The long-term protection and restoration of aquatic resources depends on accurate and precise monitoring data.
+These data require systematic quality control and analysis tools for regulatory applications or routine assessments.
+The \CRANpkg{MassWateR} package provides several functions that can facilitate quality control, analysis, and data submission for water quality data collected from different monitoring programs.
+The tools were developed to address specific regional needs for Massachusetts, USA, but the principles can be generalized to monitoring data collected at any location.
+Users can create quality control reports, perform outlier analyses, and assess various trends by season, date, and site.
+Functions are also included to prepare data for submission to the Water Quality Exchange data portal, the largest water quality database in the United States.
+These automated and reproducible assessments are expected to increase the amount of usable data for the evaluation of aquatic resources.
 draft: true

### 2023-07-13 paper.tex
full draft done, not proofed

@@
 \abstract{%
-An abstract of less than 150 words.
+The long-term protection and restoration of aquatic resources depends on accurate and precise monitoring data.
+These data require systematic quality control and analysis tools for regulatory applications or routine assessments.
+The \CRANpkg{MassWateR} package provides several functions that can facilitate quality control, analysis, and data submission for water quality data collected from different monitoring programs.
+The tools were developed to address specific regional needs for Massachusetts, USA, but the principles can be generalized to monitoring data collected at any location.
+Users can create quality control reports, perform outlier analyses, and assess various trends by season, date, and site.
+Functions are also included to prepare data for submission to the Water Quality Exchange data portal, the largest water quality database in the United States.
+These automated and reproducible assessments are expected to increase the amount of usable data for the evaluation of aquatic resources.
 }

### 2023-07-13 paper.Rmd
edited acknowledgments

@@
 
-This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bay Estuary Partnership.
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership.
 We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
+We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments.

### 2023-07-13 paper.tex
edited acknowledgments

@@
 
-This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bay Estuary Partnership.
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership.
 We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
+We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments.
 

### 2023-07-16 paper.Rmd
first draft proofed

@@
 Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
-In the United States, water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
 Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets [@Schiff16; @Tango13], or data collected *ad hoc* from multiple assessment endpoints [@Stein09; @Behmel16; @Kumpel20], where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest [@Buytaert14; @Kelly22].
-Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage of all areas of interest [@Buytaert14; @Kelly22].
+Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control (QC) requirements.
 
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for regulatory applications or inclusion in a consolidated database [@Arndt22].
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable QC checks for regulatory applications or inclusion in a consolidated database [@Arndt22].
 Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks) [@Wilde02].
@@
 These checks are often compiled in a single report for review by appropriate regulatory agencies.
-For example, precision of duplicate samples for a given parameter must not vary 5% and at least 10% of the data should be dedicated to these checks as a measure of completeness.
+For example, precision of duplicate samples for a given parameter must not vary more than 5% and at least 10% of the data should be dedicated to these checks as a measure of completeness.
 For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
-This process is time-consuming and prone to errors, often limiting the amount of useful information that is used for regulatory assessments or submitted to formal databases.
+This process is time-consuming and prone to errors, often limiting the amount of useful information for regulatory assessments or submitted to formal databases.
 
-The R statistical programming language offers a valuable software platform for developing tools to improve the QC of water quality data.
-The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
+The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
-Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] offer useful approaches to visualize numerous water quality records in a single graph.
+Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] and others in the \CRANpkg{tidyverse} [@Wickham19] offer useful tools to synthesize and visualize results.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
@@
 The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection (MADEP) and data submitted to the national WQX database.
-Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine methods for data collected elsewhere.
+Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine and commonly used methods for data collected elsewhere.
 As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water quality monitoring data in the US.
@@
 This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
-As such, data retrieval using existing web services is much simpler than data submission to a similar resource, as data formatting requirements do not apply when retrieving data.
+As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.
 Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like \CRANpkg{dataRetrieval} by increasing the amount of data that can be accessed through the WQP.
@@
 Users can engage with \CRANpkg{MassWateR} to achieve different goals.
-This design was purposeful based on likely differences in needs among the user community.
+This design was intentional based on likely differences in needs among the user community.
 Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
@@
 The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
-All steps require a formatted input file.
+All steps require formatted input files.
 WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'}
@@
 As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
-Several [resources](https://massbays-tech.github.io/MassWateR/RESOURCES.html) are provided on the package web page to assist potential users in this effort.
+Several [resources](https://massbays-tech.github.io/MassWateR/RESOURCES.html) are provided on the package web page to assist users in formatting their data.
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
@@
 This file includes all water quality monitoring data to be used with the package.
-As such, the formatting requirements are the most burdensome for potential users and additional functions are available to assist with formatting.
+As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.
 
@@
 * `qc`: QC functions for summarizing QC results, used internally to the table functions
-* `util`: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
+* `util`: Various utility functions that accomplish routine tasks, possibly useful as standalone functions
 
@@
 Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
-The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
+The error will typically indicate which parts of the input file need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
 As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \@ref(fig:importflow)).
-Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
-This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+Again, this design was intentional as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate all potential users.
+This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
 A user only needs to format their data once to use the package.
@@
 
-A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that are performed and that all checks were successful.
+A correctly formatted input file would be imported as follows, with the messages in the console indicating the checks that were performed and that all checks were successful.
 Below demonstrates what would be shown for the results file using an example dataset included with the package.
@@
 
-The following shows a typical error that might be returned if a check fails importing the results file.
+The following shows a typical error that might be returned if a check fails when importing the results file.
 The `resdat` object is an imported results file that has passed all checks, but incorrect entries are added to the `chk` object to demonstrate the error that is returned if a user would have attempted to import this file.
-The `checkMWRresults()` function is run inside the `readMWRresults()` function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the `Activity Type` column are found.
+The `checkMWRresults()` function is run inside the `readMWRresults()` function and runs the checks (e.g., the column names are correct, all required columns are present, activity types are valid, etc.), but then stops when invalid activity types in the `Activity Type` column are found.
 In this example, a user would need to change the entries in rows 4 and 135 of the `Activity Type` column in their Excel file to fix the issue and import the file again as in Figure \@ref(fig:importflow).
@@
 This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
-The output is similar to running `apply(resdat, 2, unique)` in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
+The output is similar to running `apply(resdat, 2, unique)` in the console, but an external file is created that users may be more comfortable evaluating to troubleshoot formatting problems.
 
 After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
-This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided in all functions.
 In the latter case, a path or data object can be used as input for each file.
@@
 
-# import WQX meta data
+# import WQX metadata
 wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
-On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
-The list includes `r nrow(paramsMWR)` different parameters, each with multiple valid units of measurement.
+The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a complete table of the parameters that can be used with the package.
+On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
+The dataset includes `r nrow(paramsMWR)` different parameters, each with multiple valid units of measurement.
 Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
@@
 The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
-The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct outliers.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct or remove outliers.
 
-The `anlzMWRoutlier()` function uses the results file and data quality objectives for accuracy to plot potential outliers by month.
+The `anlzMWRoutlier()` function uses the results file and data quality objectives for accuracy to plot potential outliers for a parameter by month.
 The accuracy file is used to automatically identify the y-axis scaling (as arithmetic or log) and to replace concentrations with appropriate values for those labelled as beyond detection.
@@
 The station name for a point is also shown.
-The `param` specifies the water quality parameter to evaluate and the `group` argument specifies how the boxplots are grouped (by year, month, week, or station).
+The `param` argument specifies the water quality parameter to evaluate and the `group` argument specifies how the boxplots are grouped (by year, month, week, or station).
 In the following example, three stations are identified as potential outliers for the respective month.
@@
 A user can also evaluate outliers for every water quality parameter in the results file.
-The `anlzMWRoutlierall()` function creates a Word document with images of boxplots for every parameter created with `anlzMWRoutlier()`.
+The `anlzMWRoutlierall()` function creates a Word document with images of boxplots for every parameter.
 Images for each parameter can also be created as standalone files.
@@
 The `qcMWRreview()` function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the `accdat` and `frecomdat` input files.
-This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describe relevant evaluations for the QC assessment.
+This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describes relevant evaluations for the QC assessment.
 The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
@@
 qcMWRreview(fset = fsetls, output_dir = getwd())
+#> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
 ```
@@
 The QC report is built using several functions that can be used individually as needed.
-In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] table objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] objects that can be viewed in RStudio and are compatible with Microsoft Word output.
 These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
@@
 The cells in red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
-All other parameters and checks in green had enough QC records to satisfy the DQOs.
-Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicate for dissolved oxygen.
+All other parameters and checks in green had enough QC checks to satisfy the DQOs.
+Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicates for dissolved oxygen.
 The empty cells are typically for QC checks that do not readily apply to a parameter.
-For example, dissolved oxygen is measured in the field with monitoring equipment with no lab processing, such that lab QC checks are not relevant.
+For example, dissolved oxygen is measured in the field with monitoring equipment, such that lab QC checks are not relevant.
 
@@
 tabMWRacc(res = resdat, acc = accdat, frecom = frecomdat, type = "individual", 
-  accchk = "Field Blanks", warn = FALSE)
+  accchk = "Field Blanks")
 ```
@@
 The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
-Only one sample sample for total phosphorus (TP) was at or above the threshold on July 17th.
+Only one sample taken on July 17th for total phosphorus (TP) was at or above the threshold.
 
@@
 The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
-Although several base R functions and supporting packages can be used to develop individual assessments, it was recognized that many users will not be comfortable developing their own custom visualization routines.
+Although several base R functions and supporting packages can be used to develop custom assessments, it was recognized that many users will not be comfortable developing their own visualization routines.
 As such, the analysis functions were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
 Several default settings described below allow further customization of the output as desired by the user.
-The four primary analysis functions can be used to analyze seasonal trends, trends by date, date by site, and spatially using maps.
+The four primary analysis functions can be used to analyze seasonal trends, trends by date, data by site, and spatially using maps.
 
@@
 
-The arguments specify different options available for the plot, including which parameter to plot in the results file (`param`), the type of threshold lines to show (`thresh`), the grouping, and the type of plot (jittered points over boxplots).
-The `thresh` argument in particular is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
+The arguments specify different options available for the plot, including which parameter to plot in the results file (`param`), the type of threshold lines to show (`thresh`), the grouping (`group`), and the type of plot (`type` as jittered points over boxplots).
+The `thresh` argument, in particular, is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
 The `thresholdMWR` data object included with the package includes thresholds for ten common parameters that are either regulatory standards or recommended safe limits for different designated uses in freshwater or marine environments.
@@
 In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
-Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with `geom_hline()`).
+Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with `geom_hline()` added to the plot output).
 
@@
 The `anlzMWRdate()` function plots results continuous in time on the date the samples or measurements were collected.
-This information can be use evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
+This information can be used to evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
 In the former case, individual points and lines are used for each site with appropriate labels.
-For the latter case, sites are aggregated and appropriate summary statistics are shown as the mean with 95% confidence intervals.
-Sites can be aggregated by sample dates or by "location groups" in the site metadata file.
+For the latter case, sites are aggregated and summary statistics are shown as the mean with 95% confidence intervals for each date.
+All sites can be aggregated by sample dates or by "location groups" in the site metadata file.
 For example, all sites along the same river or tributary can be aggregated.
@@
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
-Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown, as for the `anlzMWRseason()` function.
 Results at each site can also be grouped by the `Result Attribute` column in the results file, where a user can enter arbitrary grouping criteria for samples.
 For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
-Individual sites can also be specified with the `site` argument.
+Individual sites to plot can also be specified with the `site` argument, where the default is to plot all sites.
 
@@
 Finally, maps of results at each site can be created with the `anlzMWRmap()` function.
-Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information as reference.
+Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information for context.
 For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the \CRANpkg{ggmap} package [@Kahle13].
-NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail in basemaps.
+NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail provided by standard basemaps.
 These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
-Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) for including custom shapefiles.
+Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) that demonstrate how to include custom shapefiles in the map.
 The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (`addwater = "medium"`).
@@
 
-Samples and measurements across dates can be aggregated differently using the `sumfun` argument.
+Samples and measurements across dates in the map can be aggregated differently using the `sumfun` argument.
 If `sumfun = "auto"` (default), the mean is used where the distribution is determined automatically from the DQO file for accuracy, i.e., parameters with `"log"` in any of the columns are summarized with the geometric mean, otherwise arithmetic.
-Any other valid R summary function will be applied if passed to `sumfun` (`"mean"`, `"geomean"`, `"median"`, `"min"`, `"max"`).
+Additional valid R summary function will be applied if passed to `sumfun` (`"mean"`, `"geomean"`, `"median"`, `"min"`, `"max"`).
 This argument also applies to other analysis functions where the data can be aggregated across dates or locations.
@@
 Once the function is done running, a message indicating success and where the file is located is returned.
+Submitting the data to WQX simply requires copying/pasting the content in the output file into the data portal.
 
@@
 This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
-Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to the software, as well as use of \CRANpkg{MassWateR}.
+Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to R, as well as \CRANpkg{MassWateR}.
 Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with \CRANpkg{MassWateR}.
@@
 For example, a [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html) was included on the package website to demonstrate how these plots can be modified for custom output using \CRANpkg{ggplot2}.
-Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about using the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplicative issues through sharing solutions in a public forum.
+Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of issues through sharing solutions in a public forum.
 
 As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
-First, some of the parameter thresholds applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+First, some of the parameter thresholds that are visually applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
 Users can simply omit the thresholds if they do not apply using `thresh = "none"` or add custom thresholds using standard \CRANpkg{ggplot2} functions.
@@
 The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how resource managers develop QC assessments and apply exploratory analyses to water quality monitoring data.
-The package can also expedite the preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
-These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessment of status and trends of environmental resources.
+The package can also expedite preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
+These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessments of status and trends of environmental resources.
 As mentioned throughout this paper, \CRANpkg{MassWateR} was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in Figure \@ref(fig:workflow) can easily be applied to data collected elsewhere.

### 2023-07-16 paper.tex
first draft proofed

@@
 Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
-In the United States, water quality monitoring programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
 Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigation and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets (Schiff et al.
@@
 2020), where the former is atypical for most surface water bodies.
-Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage for areas of interest (Buytaert et al.
+Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage of all areas of interest (Buytaert et al.
 2014; Kelly-Quinn et al.
 2022).
-Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control requirements.
+Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control (QC) requirements.
 
 Monitoring data of sufficient quantity and quality are critical to ensure precise and accurate representation of environmental conditions.
-A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable quality control (QC) criteria for regulatory applications or inclusion in a consolidated database (Arndt et al.
+A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable QC checks for regulatory applications or inclusion in a consolidated database (Arndt et al.
 2022).
@@
 These checks are often compiled in a single report for review by appropriate regulatory agencies.
-For example, precision of duplicate samples for a given parameter must not vary 5\% and at least 10\% of the data should be dedicated to these checks as a measure of completeness.
+For example, precision of duplicate samples for a given parameter must not vary more than 5\% and at least 10\% of the data should be dedicated to these checks as a measure of completeness.
 For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
-This process is time-consuming and prone to errors, often limiting the amount of useful information that is used for regulatory assessments or submitted to formal databases.
-
-The R statistical programming language offers a valuable software platform for developing tools to improve the QC of water quality data.
+This process is time-consuming and prone to errors, often limiting the amount of useful information for regulatory assessments or submitted to formal databases.
+
 The use of R with document generation systems offered through packages like \CRANpkg{knitr} (Xie 2015) and \CRANpkg{rmarkdown} (Allaire et al.
-2023) can be leveraged to generate QC reports that follow a standard format for review by regulatory agencies.
+2023) can generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
-Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} (Wickham 2016) offer useful approaches to visualize numerous water quality records in a single graph.
+Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} (Wickham 2016) and others in the \CRANpkg{tidyverse} (Wickham et al.
+2019) offer useful tools to synthesize and visualize results.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
@@
 The fourth step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
-All steps require a formatted input file.
+All steps require formatted input files.
 WQX: Water Quality Exchange; QC: Quality Control.}\label{fig:workflow}
@@
 As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
-Several \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{resources} are provided on the package web page to assist potential users in this effort.
+Several \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{resources} are provided on the package web page to assist users in formatting their data.
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
@@
 \caption{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
 
@@
 \item
-  \texttt{util}: Various utility functions that accomplish routine tasks, but may be useful as standalone functions
+  \texttt{util}: Various utility functions that accomplish routine tasks, possibly useful as standalone functions
 \end{itemize}
@@
 Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
-The error will typically indicate which parts of the input data need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
+The error will typically indicate which parts of the input file need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
 As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \ref{fig:importflow}).
-Again, this design was purposeful as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate potential users.
-This may also encourage future standardization among groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+Again, this design was intentional as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate all potential users.
+This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
 A user only needs to format their data once to use the package.
@@
 
-The following shows a typical error that might be returned if a check fails importing the results file.
+The following shows a typical error that might be returned if a check fails when importing the results file.
 The \texttt{resdat} object is an imported results file that has passed all checks, but incorrect entries are added to the \texttt{chk} object to demonstrate the error that is returned if a user would have attempted to import this file.
-The \texttt{checkMWRresults()} function is run inside the \texttt{readMWRresults()} function and runs the checks (e.g., the column names are correct, all required columns are present), but then stops when invalid activity types in the \texttt{Activity\ Type} column are found.
+The \texttt{checkMWRresults()} function is run inside the \texttt{readMWRresults()} function and runs the checks (e.g., the column names are correct, all required columns are present, activity types are valid, etc.), but then stops when invalid activity types in the \texttt{Activity\ Type} column are found.
 In this example, a user would need to change the entries in rows 4 and 135 of the \texttt{Activity\ Type} column in their Excel file to fix the issue and import the file again as in Figure \ref{fig:importflow}.
@@
 This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
-The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but includes an external file that users may be more comfortable evaluating to troubleshoot formatting problems.
+The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but an external file is created that users may be more comfortable evaluating to troubleshoot formatting problems.
 
 After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
-This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided for all functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided in all functions.
 In the latter case, a path or data object can be used as input for each file.
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete list of the parameters that can be used with the package.
-On data import, this list is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
-The list includes 43 different parameters, each with multiple valid units of measurement.
+The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete table of the parameters that can be used with the package.
+On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
+The dataset includes 43 different parameters, each with multiple valid units of measurement.
 Additionally, only one unit of measurement is allowed per parameter, which was an intentional design so that tedious functions for converting between dozens of units of measurement did not need to be created during package development.
@@
 The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
-The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct outliers.
-
-The \texttt{anlzMWRoutlier()} function uses the results file and data quality objectives for accuracy to plot potential outliers by month.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct or remove outliers.
+
+The \texttt{anlzMWRoutlier()} function uses the results file and data quality objectives for accuracy to plot potential outliers for a parameter by month.
 The accuracy file is used to automatically identify the y-axis scaling (as arithmetic or log) and to replace concentrations with appropriate values for those labelled as beyond detection.
@@
 The station name for a point is also shown.
-The \texttt{param} specifies the water quality parameter to evaluate and the \texttt{group} argument specifies how the boxplots are grouped (by year, month, week, or station).
+The \texttt{param} argument specifies the water quality parameter to evaluate and the \texttt{group} argument specifies how the boxplots are grouped (by year, month, week, or station).
 In the following example, three stations are identified as potential outliers for the respective month.
@@
 #>   `Monitoring Location ID` `Activity Start Date` `Activity Start Time`
-#>   <chr>                    <date>                <chr>                
-#> 1 ELZ-004                  2022-05-15            06:50                
-#> 2 HOP-011                  2022-05-15            06:55                
-#> 3 ELZ-004                  2022-09-11            07:20                
+#>   <chr>                    <dttm>                <chr>                
+#> 1 ELZ-004                  2022-05-15 00:00:00   06:50                
+#> 2 HOP-011                  2022-05-15 00:00:00   06:55                
+#> 3 ELZ-004                  2022-09-11 00:00:00   07:20                
 #> # i 3 more variables: `Characteristic Name` <chr>, `Result Value` <dbl>,
@@
 A user can also evaluate outliers for every water quality parameter in the results file.
-The \texttt{anlzMWRoutlierall()} function creates a Word document with images of boxplots for every parameter created with \texttt{anlzMWRoutlier()}.
+The \texttt{anlzMWRoutlierall()} function creates a Word document with images of boxplots for every parameter.
 Images for each parameter can also be created as standalone files.
@@
 The \texttt{qcMWRreview()} function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the \texttt{accdat} and \texttt{frecomdat} input files.
-This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describe relevant evaluations for the QC assessment.
+This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describes relevant evaluations for the QC assessment.
 The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
@@
 qcMWRreview(fset = fsetls, output_dir = getwd())
+#> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
 \end{verbatim}
@@
 The QC report is built using several functions that can be used individually as needed.
-In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) table objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) objects that can be viewed in RStudio and are compatible with Microsoft Word output.
 These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
@@
 
+\ascline{1.5pt}{666666}{1-5}\endfirsthead
+
+\ascline{1.5pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
+
 \ascline{1.5pt}{666666}{1-5}\endhead
@@
 
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blank}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.07in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Spike/Check\ Accuracy}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
 \hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endhead
@@
 
+\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+
+\ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
+
 \ascline{1.5pt}{666666}{1-6}\endhead
@@
 
-The arguments specify different options available for the plot, including which parameter to plot in the results file (\texttt{param}), the type of threshold lines to show (\texttt{thresh}), the grouping, and the type of plot (jittered points over boxplots).
-The \texttt{thresh} argument in particular is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
+The arguments specify different options available for the plot, including which parameter to plot in the results file (\texttt{param}), the type of threshold lines to show (\texttt{thresh}), the grouping (\texttt{group}), and the type of plot (\texttt{type} as jittered points over boxplots).
+The \texttt{thresh} argument, in particular, is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
 The \texttt{thresholdMWR} data object included with the package includes thresholds for ten common parameters that are either regulatory standards or recommended safe limits for different designated uses in freshwater or marine environments.
@@
 In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
-Threshold lines can be suppressed (\texttt{thresh\ =\ "none"}) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with \texttt{geom\_hline()}).
+Threshold lines can be suppressed (\texttt{thresh\ =\ "none"}) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with \texttt{geom\_hline()} added to the plot output).
 
@@
 The \texttt{anlzMWRdate()} function plots results continuous in time on the date the samples or measurements were collected.
-This information can be use evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
+This information can be used to evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
 In the former case, individual points and lines are used for each site with appropriate labels.
-For the latter case, sites are aggregated and appropriate summary statistics are shown as the mean with 95\% confidence intervals.
-Sites can be aggregated by sample dates or by ``location groups'' in the site metadata file.
+For the latter case, sites are aggregated and summary statistics are shown as the mean with 95\% confidence intervals for each date.
+All sites can be aggregated by sample dates or by ``location groups'' in the site metadata file.
 For example, all sites along the same river or tributary can be aggregated.
@@
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
-Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
+Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown, as for the \texttt{anlzMWRseason()} function.
 Results at each site can also be grouped by the \texttt{Result\ Attribute} column in the results file, where a user can enter arbitrary grouping criteria for samples.
 For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
-Individual sites can also be specified with the \texttt{site} argument.
+Individual sites to plot can also be specified with the \texttt{site} argument, where the default is to plot all sites.
 
@@
 Finally, maps of results at each site can be created with the \texttt{anlzMWRmap()} function.
-Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information as reference.
+Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information for context.
 For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the \CRANpkg{ggmap} package (Kahle and Wickham 2013).
-NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail in basemaps.
+NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail provided by standard basemaps.
 These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
-Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html\#modifying-masswater-plots}{vignette} for including custom shapefiles.
+Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html\#modifying-masswater-plots}{vignette} that demonstrate how to include custom shapefiles in the map.
 The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (\texttt{addwater\ =\ "medium"}).
@@
 
-Samples and measurements across dates can be aggregated differently using the \texttt{sumfun} argument.
+Samples and measurements across dates in the map can be aggregated differently using the \texttt{sumfun} argument.
 If \texttt{sumfun\ =\ "auto"} (default), the mean is used where the distribution is determined automatically from the DQO file for accuracy, i.e., parameters with \texttt{"log"} in any of the columns are summarized with the geometric mean, otherwise arithmetic.
-Any other valid R summary function will be applied if passed to \texttt{sumfun} (\texttt{"mean"}, \texttt{"geomean"}, \texttt{"median"}, \texttt{"min"}, \texttt{"max"}).
+Additional valid R summary function will be applied if passed to \texttt{sumfun} (\texttt{"mean"}, \texttt{"geomean"}, \texttt{"median"}, \texttt{"min"}, \texttt{"max"}).
 This argument also applies to other analysis functions where the data can be aggregated across dates or locations.
@@
 This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
-Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an \href{https://massbays-tech.github.io/intro-to-r/}{introduction} to the software, as well as use of \CRANpkg{MassWateR}.
+Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an \href{https://massbays-tech.github.io/intro-to-r/}{introduction} to R, as well as \CRANpkg{MassWateR}.
 Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with \CRANpkg{MassWateR}.
@@
 For example, a \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html}{vignette} was included on the package website to demonstrate how these plots can be modified for custom output using \CRANpkg{ggplot2}.
-Further, a \href{https://massbays.discourse.group/c/masswater-r-tools/5}{community forum} was created as a resource for users to post questions about using the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplicative issues through sharing solutions in a public forum.
+Further, a \href{https://massbays.discourse.group/c/masswater-r-tools/5}{community forum} was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of issues through sharing solutions in a public forum.
 
 As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
-First, some of the parameter thresholds applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+First, some of the parameter thresholds that are visually applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
 Users can simply omit the thresholds if they do not apply using \texttt{thresh\ =\ "none"} or add custom thresholds using standard \CRANpkg{ggplot2} functions.
@@
 The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how resource managers develop QC assessments and apply exploratory analyses to water quality monitoring data.
-The package can also expedite the preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
-These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessment of status and trends of environmental resources.
+The package can also expedite preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
+These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessments of status and trends of environmental resources.
 As mentioned throughout this paper, \CRANpkg{MassWateR} was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in Figure \ref{fig:workflow} can easily be applied to data collected elsewhere.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham19}{}}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy D'Agostino McGowan, Romain François, Garrett Grolemund, et al.
+2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software} 4 (43): 1686.
+\url{https://doi.org/10.21105/joss.01686}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham23}{}}%

### 2023-07-16 paper.R

@@ -13,7 +13,7 @@ flextable::set_flextable_defaults(font.size = 7, padding = 0)
 load(file = here('tabs/filerequirements.RData'))
 
 
-## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.  A user can apply one to any of the four steps depending on their need.  The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.  The second step can be used to create a QC report for submission to a regulatory agency.  The third step can create a formatted table for WQX submission.  The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.  All steps require a formatted input file.  WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
+## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.  A user can apply one to any of the four steps depending on their need.  The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.  The second step can be used to create a QC report for submission to a regulatory agency.  The third step can create a formatted table for WQX submission.  The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.  All steps require formatted input files.  WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
 knitr::include_graphics('figs/workflow.png')
 
 
@@ -57,7 +57,7 @@ frecomdat <- readMWRfrecom(frecompth)
 sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
 sitdat <- readMWRsites(sitpth)
 
-# import WQX meta data
+# import WQX metadata
 wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
 wqxdat <- readMWRwqx(wqxpth)
 
@@ -86,6 +86,7 @@ anlzMWRoutlier(fset = fsetls, param = "DO", group = "month",
 
 ## ---- echo = T, eval = F------------------------------------------------------
 #> qcMWRreview(fset = fsetls, output_dir = getwd())
+#> #> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
 
 
[…]

### 2023-07-28 paper.Rmd
edits for BW comments done

@@
     url: https://www.acasak.com/
-    email: bwetherill@acasak.co
+    email: bwetherill@acasak.com
     affiliation: ACASAK Consulting
@@
     - Boston, Massachusetts, USA
-    orcid: 0000-0002-0912-0225
   - name: Jillian Carr
@@
     email: Jillian.Carr@umb.edu
-    affiliation: Massachusetts Bays National Estuary Partnership
-    address:
-    - University of Massachusetts Boston, 100 Morrissey Blvd
-    - Boston, Massachusetts, USA 02125
-  - name: Pamela DiBona
-    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
-    email: pamela.dibona@state.ma.us
     affiliation: Massachusetts Bays National Estuary Partnership
@@
 A significant bottleneck in the use of monitoring data for environmental assessment of surface waters is the ability to clearly and efficiently indicate that the data fulfill applicable QC checks for regulatory applications or inclusion in a consolidated database [@Arndt22].
-Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks) [@Wilde02].
+Common QC checks for *in situ* field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) accuracy of a sample relative to a known concentration (spikes or instrument checks), and 3) evaluation of the measurement from an empty or blank sample (blanks) [@Wilde02].
 An adequate number of QC samples must also be included in the dataset as a measure of "completeness".
@@
 To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
-However, there are several that can be used to retrieve and analysis data from existing sources (see the CRAN \ctv{Hydrology} Task View).
+However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN \ctv{Hydrology} Task View).
 In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
@@
 Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
-That is, QC reporting is not a requirement to submit to WQX, whereas state institutions require this reporting for regulatory assessment.
+That is, state institutions require QC reporting for regulatory assessment, whereas data submission to WQX may be a separate process.
 Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
@@
 The largest input file required for all parts of the workflow in Figure \@ref(fig:workflow) is the results file.
-This file includes all water quality monitoring data to be used with the package.
+This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle.
 As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.
@@
 
-```{r, echo = T, message = T}
+```{r, echo = T, eval = T, message = F}
 library(MassWateR)
@@
 resdat <- readMWRresults(respth)
+```
+```
+#> Running checks on results data...
+#>    Checking column names... OK
+#>    Checking all required columns are present... OK
+#>    Checking valid Activity Types... OK
+#>    Checking Activity Start Date formats... OK
+#>    Checking depth data present... OK
+#>    Checking for non-numeric values in Activity Depth/Height Measure... OK
+#>    Checking Activity Depth/Height Unit... OK
+#>    Checking Activity Relative Depth Name formats... OK
+#>    Checking values in Activity Depth/Height Measure > 1 m / 3.3 ft... OK
+#>    Checking Characteristic Name formats... OK
+#>    Checking Result Values... OK
+#>    Checking QC Reference Values... OK
+#>    Checking for missing entries for Result Unit... OK
+#>    Checking if more than one unit per Characteristic Name... OK
+#>    Checking acceptable units for each entry in Characteristic Name... OK
+#> All checks passed!
 ```
@@
 
-```{r, error = T, echo = T, message = T}
+```{r, eval = F, echo = T}
 chk <- resdat
@@
 ```
+```
+#> Running checks on results data...
+#>    Checking column names... OK
+#>    Checking all required columns are present... OK
+#> Error:  Checking valid Activity Types...
+#>    Incorrect Activity Type found: Sample, Field in row(s) 4, 135
+```
 
@@
 This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
-The output is similar to running `apply(resdat, 2, unique)` in the console, but an external file is created that users may be more comfortable evaluating to troubleshoot formatting problems.
+The output is similar to running the following:
+
+```{r, echo = T, eval = F}
+apply(readxl::read_excel('path/to/results.xlsx'), 2, unique)
+```
+
+However, this approach returns unique column entries in the R console as a list object.
+Users may be more comfortable evaluating the external file created by `readMWRresultsview()` to troubleshoot formatting problems.
 
@@
 Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
+Both the number of parameters and acceptable units can easily be extended and those herein were chosen simply to limit the development of \CRANpkg{MassWateR} to a manageable scope.
 
-An additional set of functions can be used to check for outliers in the results file.
+## Outliers
+
+Checking the results file for outliers is an additional and essential step of QC screening.
 Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
@@
 
+The following describes the types of QC measurements that are evaluated by \CRANpkg{MassWateR}:
+
+* *Field Blanks*: Measurements in the field to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present 
+* *Lab Blanks*: Laboratory samples to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
+* *Field Duplicates*: Duplicate measurements in the field to assess similar values, i.e., precision between measurements is comparable
+* *Lab Duplicates*: Duplicate laboratory samples to assess similar values, i.e., precision between samples is comparable
+* *Calibration Checks*: Measurements in the field to verify an instrument returns a known quantity of a parameter, i.e., to verify accuracy of field sampling equipment
+* *Lab Spikes*: Laboratory samples to verify if the processing equipment returns a known quantity of a parameter, i.e., to verify accuracy of laboratory equipment
+
+Additionally, \CRANpkg{MassWateR} allows a user to include "qualified samples" in the results file.
+These samples are similar as those from the above criteria and are identified by the user as having special circumstances.
+For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the `"QC Reference Value"` column.
+This eliminates row repetition and facilitates preparation of the results file for the user.
+
 The `qcMWRreview()` function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the `accdat` and `frecomdat` input files.
@@
 For example, the `tabMWRacc()` function evaluates accuracy checks for field duplicates, lab duplicates, field blanks, lab blanks, and lab spikes/instrument checks for QC records in the results file based on DQOs in the accuracy file.
-The function can return a summary of all checks as follows:
+The function can return a summary of all checks as follows (only ammonia and total phosphorus are shown for brevity):
 
-```{r, echo = T}
+```{r, echo = T, eval = F}
 tabMWRacc(fset = fsetls, type = "summary")
+```
+```{r, echo = F, eval = T}
+resin <- resdat[resdat$`Characteristic Name` %in% c('Ammonia', 'TP'), ]
+tabMWRacc(res = resin, acc = accdat, frecom = frecomdat, type = "summary")
 ```
@@
 For example, there were four field duplicate records for ammonia in the results file and only one of those records included a duplicate value outside of the acceptable range, i.e., there was a 75% acceptance rate for the four field duplicate records.
-This same table can be viewed relative to the applicable frequency rate for the amount of passing checks considered to be appropriate for the QC records as identified in the frequency and completeness DQO file.
+This function can also return a matrix of only acceptance rates for a more compact view of the QC accuracy.
 
@@
 
-Detailed information about the QC checks for an individual parameter can be obtained by changing the arguments to any of the `tab` functions.
-For example, the results for every field blank check and every parameter can be obtained as follows by changing the `type` and `accchk` arguments.
+Detailed information about the QC checks for an individual parameter can be obtained by changing the inputs to the `type` and `accchk` arguments.
+For example, the results for every field blank check and every parameter can be obtained using `type = "individual"` and `accchk = "Field Blanks"`.
 This is the same information that is summarized using `type = "summary"` or `type = "percent"`.
+Only ammonia and total phosphorus are shown for brevity.
 
-```{r}
-tabMWRacc(res = resdat, acc = accdat, frecom = frecomdat, type = "individual", 
-  accchk = "Field Blanks")
+```{r, echo = T, eval = F}
+tabMWRacc(fset = fsetls, type = "individual", accchk = "Field Blanks")
+```
+```{r, echo = F, eval = T}
+resin <- resdat[resdat$`Characteristic Name` %in% c('TP', 'Ammonia') ,]
+tabMWRacc(res = resin, acc = accdat, frecom = frecomdat, type = "individual", accchk = "Field Blanks", warn = F, caption = F)
 ```
@@
 
-Additional functions for creating QC tables include `tabMWRfre()` for assessing if a sufficient number of QC samples are available and `tabMWRcom()` for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
+Additional functions for creating QC tables include `tabMWRfre()` for assessing if a sufficient number of QC samples were performed and `tabMWRcom()` for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
 As with all the QC functions, these can be used individually within an R session to quickly view QC results or the `qcMWRreview()` function can be used to create a complete report that combines results from the individual functions.
@@
 
-The `anlzMWRdate()` function plots results continuous in time on the date the samples or measurements were collected.
+The `anlzMWRdate()` function plots results as time series on the date the samples or measurements were collected.
 This information can be used to evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
@@
 
-The `anlzMWRsite()` function can be used to view distributions of a parameter across sites.
+The `anlzMWRsite()` function can be used to view data organized by site.
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
@@
 This function will export a single Excel workbook with three sheets, named "Project", "Locations", and "Results", all of which are required for data submission.
-The output is populated with as much content as possible based on information in the input files.
-The remainder of the information not included in the output will need to be manually entered before uploading the data to WQX.
+The output is populated with as much content as possible based on information in the input files and the user can manually adjust the workbook prior to submission.
 All required columns are present, but individual rows must be verified for completeness and accuracy by the user before uploading the data.
@@
 Each of these can also be modified by hand in the output file.
-Future enhancements and additions to \CRANpkg{MassWateR} will likely include automated tools to address these minor issues using the package outside of Massachusetts.
+Future enhancements and additions to \CRANpkg{MassWateR} will likely include automated tools to make the package more applicable outside of Massachusetts.
 

### 2023-07-28 paper.tex
edits for BW comments done

@@
 \title{MassWateR: Improving quality control, analysis, and sharing of water quality data}
-\author{by Marcus W. Beck, Benjamen Wetherill, Jillian Carr, and Pamela DiBona}
+\author{by Marcus W. Beck, Benjamen Wetherill, and Jillian Carr}
 
@@
 2022).
-Common QC checks for \emph{in situ} field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) comparison of a sample to a known concentration (spikes or instrument checks), and 3) precision of the measurement from an empty or blank sample (blanks) (Wilde and U.S.
+Common QC checks for \emph{in situ} field measurements or concentrations measured in the laboratory may include 1) comparison of the precision between replicate samples (duplicates), 2) accuracy of a sample relative to a known concentration (spikes or instrument checks), and 3) evaluation of the measurement from an empty or blank sample (blanks) (Wilde and U.S.
 Geological Survey 2002).
@@
 To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
-However, there are several that can be used to retrieve and analysis data from existing sources (see the CRAN \ctv{Hydrology} Task View).
+However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN \ctv{Hydrology} Task View).
 In particular, the \CRANpkg{dataRetrieval} package (De Cicco et al.
@@
 The largest input file required for all parts of the workflow in Figure \ref{fig:workflow} is the results file.
-This file includes all water quality monitoring data to be used with the package.
+This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle.
 As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.
@@
 #> Running checks on results data...
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking column names... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking all required columns are present... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking valid Activity Types... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking Activity Start Date formats... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking depth data present... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking for non-numeric values in Activity Depth/Height Measure... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking Activity Depth/Height Unit... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking Activity Relative Depth Name formats... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking values in Activity Depth/Height Measure > 1 m / 3.3 ft... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking Characteristic Name formats... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking Result Values... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking QC Reference Values... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking for missing entries for Result Unit... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking if more than one unit per Characteristic Name... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking acceptable units for each entry in Characteristic Name... OK
-\end{verbatim}
-
-\begin{verbatim}
-#> 
 #> All checks passed!
@@
 #> Running checks on results data...
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking column names... OK
-\end{verbatim}
-
-\begin{verbatim}
 #>    Checking all required columns are present... OK
-\end{verbatim}
-
-\begin{verbatim}
 #> Error:  Checking valid Activity Types...
@@
 This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
-The output is similar to running \texttt{apply(resdat,\ 2,\ unique)} in the console, but an external file is created that users may be more comfortable evaluating to troubleshoot formatting problems.
+The output is similar to running the following:
+
+\begin{verbatim}
+apply(readxl::read_excel('path/to/results.xlsx'), 2, unique)
+\end{verbatim}
+
+However, this approach returns unique column entries in the R console as a list object.
+Users may be more comfortable evaluating the external file created by \texttt{readMWRresultsview()} to troubleshoot formatting problems.
 
@@
 Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
-
-An additional set of functions can be used to check for outliers in the results file.
+Both the number of parameters and acceptable units can easily be extended and those herein were chosen simply to limit the development of \CRANpkg{MassWateR} to a manageable scope.
+
+\hypertarget{outliers}{%
+\subsection{Outliers}\label{outliers}}
+
+Checking the results file for outliers is an additional and essential step of QC screening.
 Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
@@
 
-\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1} \end{center}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1} \end{center}
 
@@
 
+The following describes the types of QC measurements that are evaluated by \CRANpkg{MassWateR}:
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{Field Blanks}: Measurements in the field to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
+\item
+  \emph{Lab Blanks}: Laboratory samples to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
+\item
+  \emph{Field Duplicates}: Duplicate measurements in the field to assess similar values, i.e., precision between measurements is comparable
+\item
+  \emph{Lab Duplicates}: Duplicate laboratory samples to assess similar values, i.e., precision between samples is comparable
+\item
+  \emph{Calibration Checks}: Measurements in the field to verify an instrument returns a known quantity of a parameter, i.e., to verify accuracy of field sampling equipment
+\item
+  \emph{Lab Spikes}: Laboratory samples to verify if the processing equipment returns a known quantity of a parameter, i.e., to verify accuracy of laboratory equipment
+\end{itemize}
+
+Additionally, \CRANpkg{MassWateR} allows a user to include ``qualified samples'' in the results file.
+These samples are similar as those from the above criteria and are identified by the user as having special circumstances.
+For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the \texttt{"QC\ Reference\ Value"} column.
+This eliminates row repetition and facilitates preparation of the results file for the user.
+
 The \texttt{qcMWRreview()} function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the \texttt{accdat} and \texttt{frecomdat} input files.
@@
 For example, the \texttt{tabMWRacc()} function evaluates accuracy checks for field duplicates, lab duplicates, field blanks, lab blanks, and lab spikes/instrument checks for QC records in the results file based on DQOs in the accuracy file.
-The function can return a summary of all checks as follows:
+The function can return a summary of all checks as follows (only ammonia and total phosphorus are shown for brevity):
 
@@
 
-\begin{longtable}[c]{|p{1.47in}|p{0.82in}|p{1.08in}|p{0.88in}|p{0.72in}}
+\begin{longtable}[c]{|p{1.47in}|p{0.55in}|p{1.08in}|p{0.88in}|p{0.72in}}
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
-
-\ascline{1.5pt}{666666}{1-5}\endfirsthead
-
-\ascline{1.5pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Type}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ QC\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Number\ of\ Misses}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\%\ Acceptance}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{75\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{DO}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{80\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{94\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{16}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{91\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{86\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{-}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Spikes\ /\ Instrument\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{9}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{90\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{pH}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{20}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Sp\ Conductance}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{21}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
-
-\ascline{1pt}{666666}{1-5}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.82in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Water\ Temp}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{19}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{95\ \%}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{4}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{75\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{80\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Duplicates}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{10}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{16}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Field\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{91\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Blanks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{7}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{86\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{5}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Lab\ Spikes\ /\ Instrument\ Checks}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{9}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
+
+\ascline{1pt}{666666}{1-5}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.47in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.72in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{100\ \%}}} \\
 
@@
 For example, there were four field duplicate records for ammonia in the results file and only one of those records included a duplicate value outside of the acceptable range, i.e., there was a 75\% acceptance rate for the four field duplicate records.
-This same table can be viewed relative to the applicable frequency rate for the amount of passing checks considered to be appropriate for the QC records as identified in the frequency and completeness DQO file.
+This function can also return a matrix of only acceptance rates for a more compact view of the QC accuracy.
 
@@
 
-Detailed information about the QC checks for an individual parameter can be obtained by changing the arguments to any of the \texttt{tab} functions.
-For example, the results for every field blank check and every parameter can be obtained as follows by changing the \texttt{type} and \texttt{accchk} arguments.
+Detailed information about the QC checks for an individual parameter can be obtained by changing the inputs to the \texttt{type} and \texttt{accchk} arguments.
+For example, the results for every field blank check and every parameter can be obtained using \texttt{type\ =\ "individual"} and \texttt{accchk\ =\ "Field\ Blanks"}.
 This is the same information that is summarized using \texttt{type\ =\ "summary"} or \texttt{type\ =\ "percent"}.
+Only ammonia and total phosphorus are shown for brevity.
+
+\begin{verbatim}
+tabMWRacc(fset = fsetls, type = "individual", accchk = "Field Blanks")
+\end{verbatim}
 
@@
 
-\begin{longtable}[c]{|p{0.55in}|p{0.60in}|p{0.27in}|p{0.50in}|p{0.69in}|p{0.45in}}
-
-\caption{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
+\begin{longtable}[c]{|p{0.55in}|p{0.60in}|p{0.27in}|p{0.50in}|p{0.53in}|p{0.45in}}
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
-
-\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
-
-\ascline{1.5pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Parameter}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Result}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Threshold}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Hit/Miss}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{E.coli}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-13}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-18}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-01}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-29}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{1\ MPN/100ml}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Nitrate}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.05\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{MISS}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
-
-\ascline{1pt}{666666}{1-6}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.69in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{Ammonia}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.1\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{TP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-05-15}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-06-12}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-07-17}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{MISS}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-08-14}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
+
+\ascline{1pt}{666666}{1-6}
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.55in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{2022-09-11}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.27in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{BDL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.53in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{0.01\ mg/l}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 0.45in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{}}} \\
 
@@
 
-Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if a sufficient number of QC samples are available and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
+Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if a sufficient number of QC samples were performed and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
 As with all the QC functions, these can be used individually within an R session to quickly view QC results or the \texttt{qcMWRreview()} function can be used to create a complete report that combines results from the individual functions.
@@
 
-\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1} \end{center}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1} \end{center}
 
@@
 
-The \texttt{anlzMWRdate()} function plots results continuous in time on the date the samples or measurements were collected.
+The \texttt{anlzMWRdate()} function plots results as time series on the date the samples or measurements were collected.
 This information can be used to evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
@@
 
-\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1} \end{center}
-
-The \texttt{anlzMWRsite()} function can be used to view distributions of a parameter across sites.
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-15-1} \end{center}
+
+The \texttt{anlzMWRsite()} function can be used to view data organized by site.
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
@@
 
-\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1} \end{center}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-16-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1} \end{center}
+\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-17-1} \end{center}
 
@@
 This function will export a single Excel workbook with three sheets, named ``Project'', ``Locations'', and ``Results'', all of which are required for data submission.
-The output is populated with as much content as possible based on information in the input files.
-The remainder of the information not included in the output will need to be manually entered before uploading the data to WQX.
+The output is populated with as much content as possible based on information in the input files and the user can manually adjust the workbook prior to submission.
 All required columns are present, but individual rows must be verified for completeness and accuracy by the user before uploading the data.
@@
 \url{https://www.acasak.com/}\\%
-\textit{ORCiD: \href{https://orcid.org/0000-0002-0912-0225}{0000-0002-0912-0225}}\\%
-\href{mailto:bwetherill@acasak.co}{\nolinkurl{bwetherill@acasak.co}}%
+%
+\href{mailto:bwetherill@acasak.com}{\nolinkurl{bwetherill@acasak.com}}%
 }
@@
 }
-
-\address{%
-Pamela DiBona\\
-Massachusetts Bays National Estuary Partnership\\%
-University of Massachusetts Boston, 100 Morrissey Blvd\\ Boston, Massachusetts, USA 02125\\
-%
-\url{https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership}\\%
-%
-\href{mailto:pamela.dibona@state.ma.us}{\nolinkurl{pamela.dibona@state.ma.us}}%
-}

### 2023-07-28 paper.R

@@ -25,7 +25,7 @@ filerequirements %>% fontsize(part = 'all', size = 9)
 knitr::include_graphics('figs/importflow.png')
 
 
-## ---- echo = T, message = T---------------------------------------------------
+## ---- echo = T, eval = T, message = F-----------------------------------------
 library(MassWateR)
 
 # import results data
@@ -33,11 +33,15 @@ respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
 resdat <- readMWRresults(respth)
 
 
-## ---- error = T, echo = T, message = T----------------------------------------
-chk <- resdat
-chk[4, 2] <- "Sample"
-chk[135, 2] <- "Field"
-checkMWRresults(chk)
+## ---- eval = F, echo = T------------------------------------------------------
+#> chk <- resdat
+#> chk[4, 2] <- "Sample"
+#> chk[135, 2] <- "Field"
+#> checkMWRresults(chk)
+
+
+## ---- echo = T, eval = F------------------------------------------------------
+#> apply(readxl::read_excel('path/to/results.xlsx'), 2, unique)
 
 
 ## ---- results = 'hide', echo = T----------------------------------------------
@@ -94,17 +98,24 @@ knitr::include_graphics('figs/qcreview1.png')
 knitr::include_graphics('figs/qcreview2.png')
 
 
-## ---- echo = T----------------------------------------------------------------
-tabMWRacc(fset = fsetls, type = "summary")
+## ---- echo = T, eval = F------------------------------------------------------
+#> tabMWRacc(fset = fsetls, type = "summary")
+
+## ---- echo = F, eval = T------------------------------------------------------
+resin <- resdat[resdat$`Characteristic Name` %in% c('Ammonia', 'TP'), ]
+tabMWRacc(res = resin, acc = accdat, frecom = frecomdat, type = "summary")
 
 
 ## ---- echo = T----------------------------------------------------------------
 tabMWRacc(fset = fsetls, type = "percent")
 
 
-## -----------------------------------------------------------------------------
-tabMWRacc(res = resdat, acc = accdat, frecom = frecomdat, type = "individual", 
-  accchk = "Field Blanks")
+## ---- echo = T, eval = F------------------------------------------------------
+#> tabMWRacc(fset = fsetls, type = "individual", accchk = "Field Blanks")
+
+## ---- echo = F, eval = T------------------------------------------------------
[…]

### 2023-07-28 paper.Rmd
revisions form JC comments done

@@
 abstract: >
-  The long-term protection and restoration of aquatic resources depends on accurate and precise monitoring data.
-These data require systematic quality control and analysis tools for regulatory applications or routine assessments.
-The \CRANpkg{MassWateR} package provides several functions that can facilitate quality control, analysis, and data submission for water quality data collected from different monitoring programs.
-The tools were developed to address specific regional needs for Massachusetts, USA, but the principles can be generalized to monitoring data collected at any location.
-Users can create quality control reports, perform outlier analyses, and assess various trends by season, date, and site.
-Functions are also included to prepare data for submission to the Water Quality Exchange data portal, the largest water quality database in the United States.
-These automated and reproducible assessments are expected to increase the amount of usable data for the evaluation of aquatic resources.
+  The long-term protection and restoration of aquatic resources depends on robust monitoring data; data that require systematic quality control and analysis tools.
+The \CRANpkg{MassWateR} package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
+The tools were developed to address regional needs for programs in Massachusetts, USA, but the principles and outputs can be applicable to monitoring data collected anywhere.
+Users can create quality control reports, perform outlier analyses, and assess trends by season, date, and site for more than 40 parameters.
+Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
+The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data for the evaluation of aquatic resources.
 draft: true
@@
 In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
+Similarly, the Water Framework Directive provides a similar legislative foundation for the protection of aquatic resources in member states of the European Union.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances idenfitied from water quality measurements require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets [@Schiff16; @Tango13], or data collected *ad hoc* from multiple assessment endpoints [@Stein09; @Behmel16; @Kumpel20], where the former is atypical for most surface water bodies.
@@
 For example, precision of duplicate samples for a given parameter must not vary more than 5% and at least 10% of the data should be dedicated to these checks as a measure of completeness.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for potential use by agencies.
 This process is time-consuming and prone to errors, often limiting the amount of useful information for regulatory assessments or submitted to formal databases.
+As an example, dozens of community-driven environmental organizations in Massachusetts, USA, collect water quality data, yet government agencies are only able to access and utilize a fraction of those datasets.
+The Massachusetts Bays National Estuary Partnership funded the development of \CRANpkg{MassWateR} described herein to build capacity among water monitoring programs to generate and share high quality data.
+This capacity need is not specific to Massachusetts, thus, the tools were developed with transferability in mind.
 
 The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
-These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
+These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Portal (WQP) database maintained by the US Environmental Protection Agency (USEPA) and contributed to via the Water Quality eXchange (WQX).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
@@
 This paper describes the \CRANpkg{MassWateR} package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
-The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection (MADEP) and data submitted to the national WQX database.
+The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection (MADEP) and data submitted to the national WQP database.
 Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine and commonly used methods for data collected elsewhere.
@@
 However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN \ctv{Hydrology} Task View).
-In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
 This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
@@
 Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
-That is, state institutions require QC reporting for regulatory assessment, whereas data submission to WQX may be a separate process.
-Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
+That is, state institutions require QC reporting for regulatory assessments, whereas data submission to WQX may be a separate process.
+Users may also simply have a need to explore trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
 Figure \@ref(fig:workflow) demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
 The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
-
-```{r workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.
 A user can apply one to any of the four steps depending on their need.
@@
 The third step can create a formatted table for WQX submission.
-The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+The fourth step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
 All steps require formatted input files.
+
+```{r workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.
 WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'}
@@
 Developing a workflow to accommodate data inputs from the dozens of potential users from different organizations that use different data formats would have been impractical.
-As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
+As such, the primary limitation to using the package is to adhere to the formatting requirements for all input files.
 Several [resources](https://massbays-tech.github.io/MassWateR/RESOURCES.html) are provided on the package web page to assist users in formatting their data.
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
+The trainings, \CRANpkg{pkdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were implemented so that learning R was not a significant limitation for using the package.
 
@@
 This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle.
+The results file design also considered WQX requirements to facilitate data submission.
 As such, the formatting requirements for the results file are the most burdensome for potential users and additional functions are available to assist in this effort.
@@
 As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \@ref(fig:importflow)).
-Again, this design was intentional as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate all potential users.
+Again, this design was intentional as many monitoring agencies and groups organize data differently and a standard input format for the package was the best option to accommodate all potential users.
 This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
@@
 The `readMWRresultsview()` function is also available to assist with troubleshooting formatting issues for the results file.
-This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
+This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries or typos.
 The output is similar to running the following:
@@
 
-After all file format checks are fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
-This prevents the need to identify which input datasets are needed for each function, although the latter approach could used because arguments for individual input files are also provided in all functions.
+After all file format checks are completed and errors fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
+This prevents the need to identify which input datasets are needed for each function, although the latter approach could be used because arguments for individual input files are also provided in all functions.
 In the latter case, a path or data object can be used as input for each file.
@@
 Checking the results file for outliers is an additional and essential step of QC screening.
-Outliers can be caused by several reasons, including data entry errors, laboratory processing errors, or anomalous environmental events.
+Outliers can have many causes, including data entry errors, laboratory processing errors, or anomalous environmental events.
 Identifying and potentially removing or correcting outliers is a critical part of quality control.
@@
 Images for each parameter can also be created as standalone files.
-The `param` argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
-The following shows how to use the function by creating a single Word file or individual image files in the working directory.
+Here, the `param` argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
+The following shows how to use the function to create a single Word file or individual image files in the working directory.
 
@@
 qcMWRreview(fset = fsetls, output_dir = getwd())
+```
+```
 #> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
@@
 
-The cells in red showed that four of the checks for three of the parameters did not include a sufficient amount of QC records that passed the relevant accuracy checks.
-All other parameters and checks in green had enough QC checks to satisfy the DQOs.
+The cells in red showed that four of the QC checks for three of the parameters did not meet the accuracy DQOs.
+All other parameters and checks in green had enough QC checks to satisfy the DQOs (note that the table colors are color-blind friendly).
 Empty cells include checks where no QC records were available in the results file, e.g., no lab duplicates for dissolved oxygen.
@@
 The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
-Only one sample taken on July 17th for total phosphorus (TP) was at or above the threshold.
+Only one sample taken on July 17th for total phosphorus (TP) was at or above the threshold (i.e., was a "MISS" for the DQO target).
 
-Additional functions for creating QC tables include `tabMWRfre()` for assessing if a sufficient number of QC samples were performed and `tabMWRcom()` for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
-As with all the QC functions, these can be used individually within an R session to quickly view QC results or the `qcMWRreview()` function can be used to create a complete report that combines results from the individual functions.
+Additional functions for creating QC tables include `tabMWRfre()` for assessing if QC samples were conducted at the targeted frequency and `tabMWRcom()` for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples, i.e., a measure of the proportion of the data that is usable.
+As with all the QC functions, these can be used individually within an R session to quickly view QC results or the `qcMWRreview()` function can be used to create a complete report that combines outputs from the individual functions.
 The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
+The report provides space for the user to add narrative context and notes prior to submission.
 
@@
 
-The analysis functions in \CRANpkg{MassWateR} provide a simple approach to quickly evaluate data in the results file.
+The analysis functions in \CRANpkg{MassWateR} provide a streamlined approach to quickly evaluate data in the results file.
 Although several base R functions and supporting packages can be used to develop custom assessments, it was recognized that many users will not be comfortable developing their own visualization routines.
@@
 The DQO file for accuracy includes information on the distribution of each parameter, i.e., parameters with "log" in any of the columns are plotted on log10-scale, otherwise arithmetic.
-This behavior is controlled by the `yscl` argument, where the default is `"auto"` that indicates information on scaling is obtained automatically from the DQO file.
+This behavior is controlled by the `yscl` argument, where the default is `"auto"` which indicates information on scaling is obtained automatically from the DQO file.
 Setting `yscl = "linear"` or `yscl = "log"` will set the axis as linear or log10-scale, respectively, regardless of the information in the DQO file.
@@
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
-Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown, as for the `anlzMWRseason()` function.
+Boxplots or barplots can also include overlaid jittered points of the observations or only the jittered points can be shown, as for the `anlzMWRseason()` function.
 Results at each site can also be grouped by the `Result Attribute` column in the results file, where a user can enter arbitrary grouping criteria for samples.
-For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
+For example, sites can be grouped by wet or dry conditions if this information is included in the results file to evaluate the effects of precipitation on water chemistry or pollutants.
 Individual sites to plot can also be specified with the `site` argument, where the default is to plot all sites.
@@
 These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
-Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) that demonstrate how to include custom shapefiles in the map.
+Currently, only flowlines and waterbodies that intersect Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) that demonstrate how to include custom shapefiles in the map.
 The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (`addwater = "medium"`).
@@
 A single function, `tabMWRwqx()`, is provided to format data inputs using a [template](https://massbays-tech.github.io/MassWateR/RESOURCES.html) designed for data submission.
-This function will export a single Excel workbook with three sheets, named "Project", "Locations", and "Results", all of which are required for data submission.
+This function will export a single Excel workbook with three sheets, named "Project", "Locations", and "Results", all of which are required by USEPA for data submission.
 The output is populated with as much content as possible based on information in the input files and the user can manually adjust the workbook prior to submission.
@@
 Once the function is done running, a message indicating success and where the file is located is returned.
-Submitting the data to WQX simply requires copying/pasting the content in the output file into the data portal.
+Submitting the data to WQX simply requires uploading the output file into the data portal.
+After passing checks within WQX, the data are archived in the portal within 3-5 business days and made accessible to downstream users for public consumption.
 
@@
 Additional templates and instructions for data submission are available on the [package website](https://massbays-tech.github.io/MassWateR/index.html).
-It is assumed that users are familiar with the WQX data submission portal if they are already using the package.
+It is assumed that users are familiar with the WQX data submission portal if they are already using the package, though [training materials](https://www.epa.gov/waterdata/learn-more-about-water-quality-data) from USEPA are available.
 \CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
+Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., to pair lab duplicates, we created activity types "Quality Control Lab Duplicate 1" and "Quality Control Lab Duplicate 2").
+Custom WQX import configurations were also developed to streamline data submission, which were made available publicly to all WQX users.
 
@@
 
-To ensure that \CRANpkg{MassWateR} is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN.
+To ensure that \CRANpkg{MassWateR} is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN (January, 2023).
 This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
@@
 As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
-First, some of the parameter thresholds that are visually applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+First, some of the parameter thresholds that are visually overlaid on the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
 Users can simply omit the thresholds if they do not apply using `thresh = "none"` or add custom thresholds using standard \CRANpkg{ggplot2} functions.
-Second, the NHD waterbodies used by `anlzMWRmap()` are specific to watersheds in Massachusetts.
+Second, the NHD waterbodies used by `anlzMWRmap()` are specific to watersheds that intersect Massachusetts.
 Users can omit these layers from the plot using `addwater = NULL`, add a base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from \CRANpkg{ggplot2}.
@@
 
-The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how resource managers develop QC assessments and apply exploratory analyses to water quality monitoring data.
-The package can also expedite preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the amount of data made available through the WQP.
+The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how monitoring programs and resource managers implement QC assessments and apply exploratory analyses to water quality monitoring data.
+The package can also expedite preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the new data made available through the WQP.
 These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessments of status and trends of environmental resources.
@@
 
-This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership.
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership, Grant No\.
+OS-84029801-0.
 We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
-We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments.
+We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments and WQX staff at USEPA for consult on submitting data formatted with \CRANpkg{MassWateR}.

### 2023-07-28 paper.tex
revisions form JC comments done

@@
 \abstract{%
-The long-term protection and restoration of aquatic resources depends on accurate and precise monitoring data.
-These data require systematic quality control and analysis tools for regulatory applications or routine assessments.
-The \CRANpkg{MassWateR} package provides several functions that can facilitate quality control, analysis, and data submission for water quality data collected from different monitoring programs.
-The tools were developed to address specific regional needs for Massachusetts, USA, but the principles can be generalized to monitoring data collected at any location.
-Users can create quality control reports, perform outlier analyses, and assess various trends by season, date, and site.
-Functions are also included to prepare data for submission to the Water Quality Exchange data portal, the largest water quality database in the United States.
-These automated and reproducible assessments are expected to increase the amount of usable data for the evaluation of aquatic resources.
+The long-term protection and restoration of aquatic resources depends on robust monitoring data; data that require systematic quality control and analysis tools.
+The \CRANpkg{MassWateR} package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
+The tools were developed to address regional needs for programs in Massachusetts, USA, but the principles and outputs can be applicable to monitoring data collected anywhere.
+Users can create quality control reports, perform outlier analyses, and assess trends by season, date, and site for more than 40 parameters.
+Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
+The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data for the evaluation of aquatic resources.
 }
@@
 In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive provides a framework for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established, that, if exceeded based on water quality measurements, require additional regulatory action to ensure compliance.
+Similarly, the Water Framework Directive provides a similar legislative foundation for the protection of aquatic resources in member states of the European Union.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances idenfitied from water quality measurements require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets (Schiff et al.
@@
 For example, precision of duplicate samples for a given parameter must not vary more than 5\% and at least 10\% of the data should be dedicated to these checks as a measure of completeness.
-For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for review.
+For local monitoring groups that lack the resources to develop robust and repeatable workflows, QC reports are often prepared manually before submitting the data for potential use by agencies.
 This process is time-consuming and prone to errors, often limiting the amount of useful information for regulatory assessments or submitted to formal databases.
+As an example, dozens of community-driven environmental organizations in Massachusetts, USA, collect water quality data, yet government agencies are only able to access and utilize a fraction of those datasets.
+The Massachusetts Bays National Estuary Partnership funded the development of \CRANpkg{MassWateR} described herein to build capacity among water monitoring programs to generate and share high quality data.
+This capacity need is not specific to Massachusetts, thus, the tools were developed with transferability in mind.
 
@@
 2023) can generate QC reports that follow a standard format for review by regulatory agencies.
-These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Exchange (WQX) database maintained by the US Environmental Protection Agency (USEPA).
+These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Portal (WQP) database maintained by the US Environmental Protection Agency (USEPA) and contributed to via the Water Quality eXchange (WQX).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
@@
 In particular, the \CRANpkg{dataRetrieval} package (De Cicco et al.
-2022) has been used widely to retrieve data from the USEPA Water Quality Portal (WQP), which is the counterpart of the WQX system for accessing data submitted using the latter.
+2022) has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
 This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
@@
 Although increasing data submission and facilitating QC reporting was the primary goal, we also assumed that users may not want to do both.
-That is, state institutions require QC reporting for regulatory assessment, whereas data submission to WQX may be a separate process.
-Users may also simply have a need to understand trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
+That is, state institutions require QC reporting for regulatory assessments, whereas data submission to WQX may be a separate process.
+Users may also simply have a need to explore trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
 Figure \ref{fig:workflow} demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
 The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{figs/workflow} \caption{Workflow demonstrating how a user could engage with the \CRANpkg{MassWateR} package.
 A user can apply one to any of the four steps depending on their need.
@@
 All steps require formatted input files.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figs/workflow} \caption{Workflow demonstrating how a user could engage with the \CRANpkg{MassWateR} package.
 WQX: Water Quality Exchange; QC: Quality Control.}\label{fig:workflow}
@@
 Developing a workflow to accommodate data inputs from the dozens of potential users from different organizations that use different data formats would have been impractical.
-As such, the only limitation to using the package is to adhere to the formatting requirements for all input files.
+As such, the primary limitation to using the package is to adhere to the formatting requirements for all input files.
 Several \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{resources} are provided on the package web page to assist users in formatting their data.
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
+The trainings, \CRANpkg{pkdown} \href{https://massbays-tech.github.io/MassWateR/}{website} (Wickham, Hesselberth, and Salmon 2022), and \href{https://massbays.discourse.group/login}{Community of Practice forum} were implemented so that learning R was not a significant limitation for using the package.
 
@@
 As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \ref{fig:importflow}).
-Again, this design was intentional as many monitoring agencies and groups collect data differently and a standard input format for the package was the best option to accommodate all potential users.
+Again, this design was intentional as many monitoring agencies and groups organize data differently and a standard input format for the package was the best option to accommodate all potential users.
 This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
@@
 The \texttt{readMWRresultsview()} function is also available to assist with troubleshooting formatting issues for the results file.
-This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries.
+This function exports an Excel file that shows the unique values that are found in each column to allow a user to quickly see potential incorrect entries or typos.
 The output is similar to running the following:
@@
 Images for each parameter can also be created as standalone files.
-The \texttt{param} argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
-The following shows how to use the function by creating a single Word file or individual image files in the working directory.
+Here, the \texttt{param} argument does not need to be specified because all parameters are identified in the results file and processed accordingly.
+The following shows how to use the function to create a single Word file or individual image files in the working directory.
 
@@
 qcMWRreview(fset = fsetls, output_dir = getwd())
+\end{verbatim}
+
+\begin{verbatim}
 #> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
@@
 The example shows that all but one field blank passed the checks, where most were below the detection limit (BDL) of the laboratory equipment.
-Only one sample taken on July 17th for total phosphorus (TP) was at or above the threshold.
-
-Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if a sufficient number of QC samples were performed and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples.
-As with all the QC functions, these can be used individually within an R session to quickly view QC results or the \texttt{qcMWRreview()} function can be used to create a complete report that combines results from the individual functions.
+Only one sample taken on July 17th for total phosphorus (TP) was at or above the threshold (i.e., was a ``MISS'' for the DQO target).
+
+Additional functions for creating QC tables include \texttt{tabMWRfre()} for assessing if QC samples were conducted at the targeted frequency and \texttt{tabMWRcom()} for assessing completeness checks that compare the number of regular samples (field measurements or lab samples) to the number of qualified samples, i.e., a measure of the proportion of the data that is usable.
+As with all the QC functions, these can be used individually within an R session to quickly view QC results or the \texttt{qcMWRreview()} function can be used to create a complete report that combines outputs from the individual functions.
 The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
+The report provides space for the user to add narrative context and notes prior to submission.
 
@@
 The DQO file for accuracy includes information on the distribution of each parameter, i.e., parameters with ``log'' in any of the columns are plotted on log10-scale, otherwise arithmetic.
-This behavior is controlled by the \texttt{yscl} argument, where the default is \texttt{"auto"} that indicates information on scaling is obtained automatically from the DQO file.
+This behavior is controlled by the \texttt{yscl} argument, where the default is \texttt{"auto"} which indicates information on scaling is obtained automatically from the DQO file.
 Setting \texttt{yscl\ =\ "linear"} or \texttt{yscl\ =\ "log"} will set the axis as linear or log10-scale, respectively, regardless of the information in the DQO file.
@@
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
-Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown, as for the \texttt{anlzMWRseason()} function.
+Boxplots or barplots can also include overlaid jittered points of the observations or only the jittered points can be shown, as for the \texttt{anlzMWRseason()} function.
 Results at each site can also be grouped by the \texttt{Result\ Attribute} column in the results file, where a user can enter arbitrary grouping criteria for samples.
-For example, sites can be grouped by wet or dry conditions if this information is included in the results file.
+For example, sites can be grouped by wet or dry conditions if this information is included in the results file to evaluate the effects of precipitation on water chemistry or pollutants.
 Individual sites to plot can also be specified with the \texttt{site} argument, where the default is to plot all sites.
@@
 These datasets are available from an external source and clipped to an approximate bounding box for the selected stations.
-Currently, only flowlines and waterbodies for Massachusetts are included, although examples are provided in a package \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html\#modifying-masswater-plots}{vignette} that demonstrate how to include custom shapefiles in the map.
+Currently, only flowlines and waterbodies that intersect Massachusetts are included, although examples are provided in a package \href{https://massbays-tech.github.io/MassWateR/articles/modifying.html\#modifying-masswater-plots}{vignette} that demonstrate how to include custom shapefiles in the map.
 The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (\texttt{addwater\ =\ "medium"}).
@@
 A single function, \texttt{tabMWRwqx()}, is provided to format data inputs using a \href{https://massbays-tech.github.io/MassWateR/RESOURCES.html}{template} designed for data submission.
-This function will export a single Excel workbook with three sheets, named ``Project'', ``Locations'', and ``Results'', all of which are required for data submission.
+This function will export a single Excel workbook with three sheets, named ``Project'', ``Locations'', and ``Results'', all of which are required by USEPA for data submission.
 The output is populated with as much content as possible based on information in the input files and the user can manually adjust the workbook prior to submission.
@@
 Additional templates and instructions for data submission are available on the \href{https://massbays-tech.github.io/MassWateR/index.html}{package website}.
-It is assumed that users are familiar with the WQX data submission portal if they are already using the package.
+It is assumed that users are familiar with the WQX data submission portal if they are already using the package, though \href{https://www.epa.gov/waterdata/learn-more-about-water-quality-data}{training materials} from USEPA are available.
 \CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
+Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., to pair lab duplicates, we created activity types ``Quality Control Lab Duplicate 1'' and ``Quality Control Lab Duplicate 2'').
+Custom WQX import configurations were also developed to streamline data submission, which were made available publicly to all WQX users.
 
@@
 As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
-First, some of the parameter thresholds that are visually applied to the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
+First, some of the parameter thresholds that are visually overlaid on the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
 Users can simply omit the thresholds if they do not apply using \texttt{thresh\ =\ "none"} or add custom thresholds using standard \CRANpkg{ggplot2} functions.
-Second, the NHD waterbodies used by \texttt{anlzMWRmap()} are specific to watersheds in Massachusetts.
+Second, the NHD waterbodies used by \texttt{anlzMWRmap()} are specific to watersheds that intersect Massachusetts.
 Users can omit these layers from the plot using \texttt{addwater\ =\ NULL}, add a base map using the \texttt{maptype} argument, or add custom waterbody layers as simple features objects (Pebesma and Bivand 2023) using the \texttt{geom\_sf()} function from \CRANpkg{ggplot2}.
@@
 
-This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership.
+This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership, Grant No.
+OS-84029801-0.
 We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
-We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments.
+We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments and WQX staff at USEPA for consult on submitting data formatted with \CRANpkg{MassWateR}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham22}{}}%
+Wickham, Hadley, Jay Hesselberth, and Maëlle Salmon. 2022. \emph{Pkgdown: Make Static HTML Documentation for a Package}. \url{https://CRAN.R-project.org/package=pkgdown}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wilde02}{}}%

### 2023-07-28 paper.R

@@ -13,7 +13,7 @@ flextable::set_flextable_defaults(font.size = 7, padding = 0)
 load(file = here('tabs/filerequirements.RData'))
 
 
-## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.  A user can apply one to any of the four steps depending on their need.  The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.  The second step can be used to create a QC report for submission to a regulatory agency.  The third step can create a formatted table for WQX submission.  The fourth step is data analysis and visualization, using \\CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.  All steps require formatted input files.  WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
+## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package. WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
 knitr::include_graphics('figs/workflow.png')
 
 
@@ -90,7 +90,6 @@ anlzMWRoutlier(fset = fsetls, param = "DO", group = "month",
 
 ## ---- echo = T, eval = F------------------------------------------------------
 #> qcMWRreview(fset = fsetls, output_dir = getwd())
-#> #> Report created successfully! File located at /tmp/RtmpUzzrbC/qcreview.docx
 
 
 ## ----qcex, fig.cap = "The first two pages of the quality control report that evaluates the results data relative to data quality objectives.  The first page shows the data quality objectives for accuracy, frequency, and completeness.  The second page shows QC results for frequency and completeness.  Parameters shown in red or marked as 'MISS' failed the data quality objectives.  Users can edit the Word file as needed, e.g., entering the organization name or adding notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '50%', fig.show='hold'----

### 2023-08-05 paper.Rmd
proofreading and minor edits

@@
 Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
-The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data for the evaluation of aquatic resources.
+The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data to support the management of aquatic resources.
 draft: true
@@
 In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive provides a similar legislative foundation for the protection of aquatic resources in member states of the European Union.
+Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union.
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances idenfitied from water quality measurements require additional regulatory action to ensure compliance.
@@
 Figure \@ref(fig:workflow) demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
-The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
-A user can apply one to any of the four steps depending on their need.
+The functions allow a user to engage with their data several ways.
 The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.
 The second step can be used to create a QC report for submission to a regulatory agency.
-The third step can create a formatted table for WQX submission.
-The fourth step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
-All steps require formatted input files.
+The third step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+The fourth and final step can create a formatted table for WQX submission.
 
@@
 No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.
-Developing a workflow to accommodate data inputs from the dozens of potential users from different organizations that use different data formats would have been impractical.
+Developing a workflow to accommodate data inputs from the dozens of potential users from several organizations that use different data formats would have been impractical.
 As such, the primary limitation to using the package is to adhere to the formatting requirements for all input files.
@@
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
-The trainings, \CRANpkg{pkdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were implemented so that learning R was not a significant limitation for using the package.
+The trainings, \CRANpkg{pkdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were also implemented so that learning R was not a significant limitation for using the package.
 
-The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filreq), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).
-The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.
+The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filreq), including how each file applies to the workflow steps in Figure \@ref(fig:workflow).
+The files are imported into R using specific `read` functions with relevant checks, explained in the next section.
 These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.
@@
 There are several checks for each type of input file, with the number of checks increasing based on the complexity of the input file.
-Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function is exited.
+Each check is printed to the R console on completion, whereas an error is returned at the first instance of a failed check, at which point the function exits.
 The error will typically indicate which parts of the input file need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
@@
 ```{r importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.
-All read functions import an Excel file and the imported file is then passed to a check function.
+All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
@@
 Below demonstrates what would be shown for the results file using an example dataset included with the package.
-A total of fifteen checks are applied to the results file.
+A total of fifteen checks are applied to the results file (described in detail in the [help documentation](https://massbays-tech.github.io/MassWateR/reference/checkMWRresults.html) and [vignettes](https://massbays-tech.github.io/MassWateR/articles/inputs.html#surface-water-quality-results)).
 
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a complete table of the parameters that can be used with the package.
+The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a lookup table of the parameters that can be used with the package.
 On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
@@
 It is not an unreasonable expectation for users to provide only one unit of measurement per parameter.
-Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure concentrations of water quality parameters.
+Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure water quality parameters.
 Both the number of parameters and acceptable units can easily be extended and those herein were chosen simply to limit the development of \CRANpkg{MassWateR} to a manageable scope.
@@
 The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
-The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct or remove outliers.
+The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct or remove these values.
 
@@
 Outliers are defined using the standard definition of 1.5 times the interquartile range (the 25th to 75th percentile) of a parameter and can be visually identified as points above or below the whiskers in the boxplots.
-The station name for a point is also shown.
+The station name for a point is also shown for identification.
 The `param` argument specifies the water quality parameter to evaluate and the `group` argument specifies how the boxplots are grouped (by year, month, week, or station).
 In the following example, three stations are identified as potential outliers for the respective month.
+Note that the outliers may differ slightly by the grouping choice as they are specific to each value on the x-axis.
 
@@
 
-A user can also evaluate outliers for every water quality parameter in the results file.
+A user can also jointly evaluate outliers for every water quality parameter in the results file.
 The `anlzMWRoutlierall()` function creates a Word document with images of boxplots for every parameter.
@@
 
-* *Field Blanks*: Measurements in the field to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present 
-* *Lab Blanks*: Laboratory samples to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
+* *Field Blanks*: Measurements in the field to verify absence of a parameter, i.e., the parameter is not detected by the field method when it is not present
+* *Lab Blanks*: Laboratory samples to verify absence a parameter, i.e., the parameter is not detected by the lab method when it is not present
 * *Field Duplicates*: Duplicate measurements in the field to assess similar values, i.e., precision between measurements is comparable
@@
 These samples are similar as those from the above criteria and are identified by the user as having special circumstances.
-For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the `"QC Reference Value"` column.
+For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the `"QC Reference Value"` column of the results file.
 This eliminates row repetition and facilitates preparation of the results file for the user.
@@
 
-```{r qcex, fig.cap = "The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+```{r qcex, fig.cap = "The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
 The first page shows the data quality objectives for accuracy, frequency, and completeness.
@@
 The QC report is built using several functions that can be used individually as needed.
-In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] objects that can be viewed in RStudio and are compatible with Word output.
 These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
@@
 
-The cells in red showed that four of the QC checks for three of the parameters did not meet the accuracy DQOs.
+The cells in red show that four of the QC checks for three of the parameters did not meet the accuracy DQOs.
 All other parameters and checks in green had enough QC checks to satisfy the DQOs (note that the table colors are color-blind friendly).
@@
 The summarized report can then be submitted to an appropriate regulatory agency for review to ensure that any submitted datasets fulfill appropriate data quality objectives.
-The report provides space for the user to add narrative context and notes prior to submission.
 
@@
 Although several base R functions and supporting packages can be used to develop custom assessments, it was recognized that many users will not be comfortable developing their own visualization routines.
-As such, the analysis functions were designed for a rapid overview of the results that required minimal decisions by the user to create the output.
+As such, the analysis functions were designed for a rapid overview of the results that require minimal decisions by the user to create the output.
 Several default settings described below allow further customization of the output as desired by the user.
@@
 
-The arguments specify different options available for the plot, including which parameter to plot in the results file (`param`), the type of threshold lines to show (`thresh`), the grouping (`group`), and the type of plot (`type` as jittered points over boxplots).
+The arguments specify different options available for the plot, including which parameter to plot in the results file (`param`), the type of threshold line(s) to show (`thresh`), the grouping (`group`), and the type of plot (`type` as jittered points over boxplots).
 The `thresh` argument, in particular, is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
@@
 In the former case, individual points and lines are used for each site with appropriate labels.
-For the latter case, sites are aggregated and summary statistics are shown as the mean with 95% confidence intervals for each date.
+For the latter case, sites are aggregated and summary statistics are shown as the mean with optional 95% confidence intervals for each date.
 All sites can be aggregated by sample dates or by "location groups" in the site metadata file.
@@
 \CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
-Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., to pair lab duplicates, we created activity types "Quality Control Lab Duplicate 1" and "Quality Control Lab Duplicate 2").
+Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., activity types "Quality Control Lab Duplicate 1" and "Quality Control Lab Duplicate 2" were created to pair lab duplicates).
 Custom WQX import configurations were also developed to streamline data submission, which were made available publicly to all WQX users.
@@
 Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of issues through sharing solutions in a public forum.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
 
@@
 Second, the NHD waterbodies used by `anlzMWRmap()` are specific to watersheds that intersect Massachusetts.
-Users can omit these layers from the plot using `addwater = NULL`, add a base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from \CRANpkg{ggplot2}.
+Users can omit these layers from the plot using `addwater = NULL`, add a universal base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from \CRANpkg{ggplot2}.
 Third, the QC report created by `qcMWRreview()` uses a format vetted by MADEP.
-This format may not meet the requirements of other state organization, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
+This format may not meet the requirements of other state organizations, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
 Finally, minor components of the Excel file for WQX submission created by `tabMWRwqx()` are specific to Massachusetts.
@@
 This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership, Grant No\.
-OS-84029801-0.
+OS\-84029801\-0.
 We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.

### 2023-08-05 paper.tex
proofreading and minor edits

@@
 Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
-The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data for the evaluation of aquatic resources.
+The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data to support the management of aquatic resources.
 }
@@
 Figure \ref{fig:workflow} demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
-The functions allow a user to engage with their data several ways, including 1) screening data for quality control, 2) summarizing quality control results into a single report or separate tables, 3) creating graphics for analysis and reports to stakeholders, and 4) formatting data for upload to WQX.
-A user can apply one to any of the four steps depending on their need.
+The functions allow a user to engage with their data several ways.
 The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.
 The second step can be used to create a QC report for submission to a regulatory agency.
-The third step can create a formatted table for WQX submission.
-The fourth step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
-All steps require formatted input files.
+The third step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+The fourth and final step can create a formatted table for WQX submission.
 
@@
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
-The trainings, \CRANpkg{pkdown} \href{https://massbays-tech.github.io/MassWateR/}{website} (Wickham, Hesselberth, and Salmon 2022), and \href{https://massbays.discourse.group/login}{Community of Practice forum} were implemented so that learning R was not a significant limitation for using the package.
-
-The required data files for using \CRANpkg{MassWateR} are shown in Table \ref{tab:filreq}, including the files that apply to the workflow steps in Figure \ref{fig:workflow}.
-The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
+The trainings, \CRANpkg{pkdown} \href{https://massbays-tech.github.io/MassWateR/}{website} (Wickham, Hesselberth, and Salmon 2022), and \href{https://massbays.discourse.group/login}{Community of Practice forum} were also implemented so that learning R was not a significant limitation for using the package.
+
+The required data files for using \CRANpkg{MassWateR} are shown in Table \ref{tab:filreq}, including how each file applies to the workflow steps in Figure \ref{fig:workflow}.
+The files are imported into R using specific \texttt{read} functions with relevant checks, explained in the next section.
 These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.
@@
 
-\caption{\textcolor[HTML]{000000}{\fontsize{7}{8}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreq}\\
+\caption{\textcolor[HTML]{000000}{\fontsize{11}{13}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.\ DQO:\ Data\ Quality\ Objective;\ QC:\ Quality\ Control.}}}\label{tab:filreq}\\
 
@@
 
-\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{WQX\ formatting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Data\ analysis}}}} \\
+\multicolumn{1}{>{\raggedright}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Formatted\ file}}}} & \multicolumn{1}{>{\raggedright}p{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{Description}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{1.\ QC\ screening}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{2.\ QC\ reporting}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{3.\ Data\ analysis}}}} & \multicolumn{1}{>{\centering}p{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{\textbf{4.\ WQX\ formatting}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{WQX\ metadata}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 2.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{A\ wqx\ metadata\ file\ required\ for\ generating\ output\ to\ facilitate\ data\ upload\ to\ WQX}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}\includegraphics[width=0.15in, height=0.15in]{paper_files/figure-latex/filreq-14.png}\textcolor[HTML]{000000}{\fontsize{9}{9}\selectfont{}}} \\
 
@@
 \includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.
-All read functions import an Excel file and the imported file is then passed to a check function.
+All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
@@
 Below demonstrates what would be shown for the results file using an example dataset included with the package.
-A total of fifteen checks are applied to the results file.
+A total of fifteen checks are applied to the results file (described in detail in the \href{https://massbays-tech.github.io/MassWateR/reference/checkMWRresults.html}{help documentation} and \href{https://massbays-tech.github.io/MassWateR/articles/inputs.html\#surface-water-quality-results}{vignettes}).
 
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a complete table of the parameters that can be used with the package.
+The \texttt{paramsMWR} dataset included with \CRANpkg{MassWateR} provides a lookup table of the parameters that can be used with the package.
 On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
@@
 Outliers are defined using the standard definition of 1.5 times the interquartile range (the 25th to 75th percentile) of a parameter and can be visually identified as points above or below the whiskers in the boxplots.
-The station name for a point is also shown.
+The station name for a point is also shown for identification.
 The \texttt{param} argument specifies the water quality parameter to evaluate and the \texttt{group} argument specifies how the boxplots are grouped (by year, month, week, or station).
 In the following example, three stations are identified as potential outliers for the respective month.
+Note that the outliers may differ slightly by the grouping choice as they are specific to each value on the x-axis.
 
@@
 
-A user can also evaluate outliers for every water quality parameter in the results file.
+A user can also jointly evaluate outliers for every water quality parameter in the results file.
 The \texttt{anlzMWRoutlierall()} function creates a Word document with images of boxplots for every parameter.
@@
 \item
-  \emph{Field Blanks}: Measurements in the field to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
-\item
-  \emph{Lab Blanks}: Laboratory samples to assess lack of presence of a parameter, i.e., no measurement when the parameter is not present
+  \emph{Field Blanks}: Measurements in the field to verify absence of a parameter, i.e., the parameter is not detected by the field method when it is not present
+\item
+  \emph{Lab Blanks}: Laboratory samples to verify absence a parameter, i.e., the parameter is not detected by the lab method when it is not present
 \item
@@
 These samples are similar as those from the above criteria and are identified by the user as having special circumstances.
-For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the \texttt{"QC\ Reference\ Value"} column.
+For example, field duplicates are typically in pairs and the second measurement can be entered as a qualified sample in the same row of the first sample under the \texttt{"QC\ Reference\ Value"} column of the results file.
 This eliminates row repetition and facilitates preparation of the results file for the user.
@@
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{figs/qcreview1} \includegraphics[width=0.5\linewidth]{figs/qcreview2} \caption{The first two pages of the quality control report that evaluates the results data relative to data quality objectives.
+\includegraphics[width=0.5\linewidth]{figs/qcreview1} \includegraphics[width=0.5\linewidth]{figs/qcreview2} \caption{The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
 The first page shows the data quality objectives for accuracy, frequency, and completeness.
@@
 The QC report is built using several functions that can be used individually as needed.
-In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) objects that can be viewed in RStudio and are compatible with Microsoft Word output.
+In particular, the \texttt{tabMWRacc()}, \texttt{tabMWRfre()}, and \texttt{tabMWRcom()} create \CRANpkg{flextable} (Gohel and Skintzos 2023) objects that can be viewed in RStudio and are compatible with Word output.
 These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
@@
 
-The arguments specify different options available for the plot, including which parameter to plot in the results file (\texttt{param}), the type of threshold lines to show (\texttt{thresh}), the grouping (\texttt{group}), and the type of plot (\texttt{type} as jittered points over boxplots).
+The arguments specify different options available for the plot, including which parameter to plot in the results file (\texttt{param}), the type of threshold line(s) to show (\texttt{thresh}), the grouping (\texttt{group}), and the type of plot (\texttt{type} as jittered points over boxplots).
 The \texttt{thresh} argument, in particular, is used to plot relevant thresholds of interest based on the parameter and if the samples are from freshwater or marine sites.
@@
 In the former case, individual points and lines are used for each site with appropriate labels.
-For the latter case, sites are aggregated and summary statistics are shown as the mean with 95\% confidence intervals for each date.
+For the latter case, sites are aggregated and summary statistics are shown as the mean with optional 95\% confidence intervals for each date.
 All sites can be aggregated by sample dates or by ``location groups'' in the site metadata file.
@@
 \CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
-Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., to pair lab duplicates, we created activity types ``Quality Control Lab Duplicate 1'' and ``Quality Control Lab Duplicate 2'').
+Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., activity types ``Quality Control Lab Duplicate 1'' and ``Quality Control Lab Duplicate 2'' were created to pair lab duplicates).
 Custom WQX import configurations were also developed to streamline data submission, which were made available publicly to all WQX users.
@@
 Further, a \href{https://massbays.discourse.group/c/masswater-r-tools/5}{community forum} was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of issues through sharing solutions in a public forum.
+This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
 
@@
 Second, the NHD waterbodies used by \texttt{anlzMWRmap()} are specific to watersheds that intersect Massachusetts.
-Users can omit these layers from the plot using \texttt{addwater\ =\ NULL}, add a base map using the \texttt{maptype} argument, or add custom waterbody layers as simple features objects (Pebesma and Bivand 2023) using the \texttt{geom\_sf()} function from \CRANpkg{ggplot2}.
+Users can omit these layers from the plot using \texttt{addwater\ =\ NULL}, add a universal base map using the \texttt{maptype} argument, or add custom waterbody layers as simple features objects (Pebesma and Bivand 2023) using the \texttt{geom\_sf()} function from \CRANpkg{ggplot2}.
 Third, the QC report created by \texttt{qcMWRreview()} uses a format vetted by MADEP.
-This format may not meet the requirements of other state organization, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
+This format may not meet the requirements of other state organizations, although the reporting principles are generally universal and the resulting Word document can easily be manually modified.
 Finally, minor components of the Excel file for WQX submission created by \texttt{tabMWRwqx()} are specific to Massachusetts.

### 2023-08-05 R/tabs.R

@@ -9,10 +9,10 @@ chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
 totab <- tibble(
   `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
   `Description` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
-  `QC screening` = c('r', 'r', 'r', 'r', ''), 
-  `QC reporting` = c('r', 'r', 'r', '', ''),
-  `WQX formatting` = c('r', 'r', '', 'r', 'r'),
-  `Data analysis` = c('r', 'r', '', 'r', '')
+  `1. QC screening` = c('r', 'r', 'r', 'r', ''), 
+  `2. QC reporting` = c('r', 'r', 'r', '', ''),
+  `3. Data analysis` = c('r', 'r', '', 'r', ''),
+  `4. WQX formatting` = c('r', 'r', '', 'r', 'r'),
 ) %>% 
   mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
 
@@ -31,7 +31,7 @@ tab <- flextable(totab) %>%
   align(j = 3:6, align = 'center', part = 'all') %>% 
   set_caption(
     as_paragraph(
-      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow.", props = fp_text_default(font.family = "Arial"))
+      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.", props = fp_text_default(font.family = "Arial"))
               ), 
     word_stylename = "Table Caption"
     )

### 2023-08-05 paper.R

@@ -21,7 +21,7 @@ knitr::include_graphics('figs/workflow.png')
 filerequirements %>% fontsize(part = 'all', size = 9)
 
 
-## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'----
+## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'----
 knitr::include_graphics('figs/importflow.png')
 
 
@@ -92,7 +92,7 @@ anlzMWRoutlier(fset = fsetls, param = "DO", group = "month",
 #> qcMWRreview(fset = fsetls, output_dir = getwd())
 
 
-## ----qcex, fig.cap = "The first two pages of the quality control report that evaluates the results data relative to data quality objectives.  The first page shows the data quality objectives for accuracy, frequency, and completeness.  The second page shows QC results for frequency and completeness.  Parameters shown in red or marked as 'MISS' failed the data quality objectives.  Users can edit the Word file as needed, e.g., entering the organization name or adding notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '50%', fig.show='hold'----
[…]

### 2023-08-05 paper.Rmd
minor edits for rjtools checks

@@
 ---
-title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
+title: "MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data"
 date: "`r Sys.Date()`"
@@
 Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances idenfitied from water quality measurements require additional regulatory action to ensure compliance.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances identified from water quality measurements require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets [@Schiff16; @Tango13], or data collected *ad hoc* from multiple assessment endpoints [@Stein09; @Behmel16; @Kumpel20], where the former is atypical for most surface water bodies.
@@
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
-The trainings, \CRANpkg{pkdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were also implemented so that learning R was not a significant limitation for using the package.
+The trainings, \CRANpkg{pkgdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were also implemented so that learning R was not a significant limitation for using the package.
 
@@
 
-# \CRANpkg{MassWateR} functions
+# MassWateR functions
 

### 2023-08-05 paper.tex
minor edits for rjtools checks

@@
 % !TeX root = RJwrapper.tex
-\title{MassWateR: Improving quality control, analysis, and sharing of water quality data}
+\title{MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data}
 \author{by Marcus W. Beck, Benjamen Wetherill, and Jillian Carr}
@@
 Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union.
-Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances idenfitied from water quality measurements require additional regulatory action to ensure compliance.
+Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances identified from water quality measurements require additional regulatory action to ensure compliance.
 These standards and other regulatory assessments as applied at the state-level use information from long-term monitoring datasets (Schiff et al.
@@
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
-The trainings, \CRANpkg{pkdown} \href{https://massbays-tech.github.io/MassWateR/}{website} (Wickham, Hesselberth, and Salmon 2022), and \href{https://massbays.discourse.group/login}{Community of Practice forum} were also implemented so that learning R was not a significant limitation for using the package.
+The trainings, \CRANpkg{pkgdown} \href{https://massbays-tech.github.io/MassWateR/}{website} (Wickham, Hesselberth, and Salmon 2022), and \href{https://massbays.discourse.group/login}{Community of Practice forum} were also implemented so that learning R was not a significant limitation for using the package.
 
@@
 
-\hypertarget{functions}{%
-\section{\texorpdfstring{\CRANpkg{MassWateR} functions}{ functions}}\label{functions}}
+\hypertarget{masswater-functions}{%
+\section{MassWateR functions}\label{masswater-functions}}
 

### 2023-08-05 submission/R/tabs.R
more submission check fixes, zip submission

@@ -1,0 +1,40 @@
+library(flextable)
+library(tidyverse)
+library(here)
+
+# file inputs ---------------------------------------------------------------------------------
+
+chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
+
+totab <- tibble(
+  `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
+  `Description` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
+  `1. QC screening` = c('r', 'r', 'r', 'r', ''), 
+  `2. QC reporting` = c('r', 'r', 'r', '', ''),
+  `3. Data analysis` = c('r', 'r', '', 'r', ''),
+  `4. WQX formatting` = c('r', 'r', '', 'r', 'r'),
+) %>% 
+  mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
+
+colind <- apply(totab[, 3:6], 2, function(x) which(x != ''))
+imgsz <- 0.15
+tab <- flextable(totab) %>%
+  colformat_image(j = 3, i = colind[[1]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 4, i = colind[[2]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 5, i = colind[[3]], width = imgsz, height = imgsz) %>% 
+  colformat_image(j = 6, i = colind[[4]], width = imgsz, height = imgsz) %>% 
+  width(j = 2, width = 2.5) %>%
+  width(j = c(1, 3:6), width = 3 / 5) %>%
+  bold(part = 'header') %>%
+  colformat_double(digits = 2) %>%
+  valign(valign = 'top', part = 'header') %>%
+  align(j = 3:6, align = 'center', part = 'all') %>% 
+  set_caption(
+    as_paragraph(
+      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.", props = fp_text_default(font.family = "Arial"))
+              ), 
[…]

### 2023-08-05 submission/paper.R

@@ -1,0 +1,143 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit paper.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+
+library(flextable)
+library(dplyr)
+library(here)
+
+flextable::set_flextable_defaults(font.size = 7, padding = 0)
+
+load(file = here('tabs/filerequirements.RData'))
+
+
+## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package. WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
+knitr::include_graphics('figs/workflow.png')
+
+
+## ----filreq-------------------------------------------------------------------
+filerequirements %>% fontsize(part = 'all', size = 9)
+
+
+## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'----
+knitr::include_graphics('figs/importflow.png')
+
+
+## ---- echo = T, eval = T, message = F-----------------------------------------
+library(MassWateR)
+
+# import results data
+respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
+resdat <- readMWRresults(respth)
+
+
+## ---- eval = F, echo = T------------------------------------------------------
+#> chk <- resdat
+#> chk[4, 2] <- "Sample"
+#> chk[135, 2] <- "Field"
+#> checkMWRresults(chk)
+
+
+## ---- echo = T, eval = F------------------------------------------------------
[…]

### 2023-08-05 submission/R/tabs.R
submitted to r journal

@@ -1,40 +1,0 @@
-library(flextable)
-library(tidyverse)
-library(here)
-
-# file inputs ---------------------------------------------------------------------------------
-
-chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
-
-totab <- tibble(
-  `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
-  `Description` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
-  `1. QC screening` = c('r', 'r', 'r', 'r', ''), 
-  `2. QC reporting` = c('r', 'r', 'r', '', ''),
-  `3. Data analysis` = c('r', 'r', '', 'r', ''),
-  `4. WQX formatting` = c('r', 'r', '', 'r', 'r'),
-) %>% 
-  mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
-
-colind <- apply(totab[, 3:6], 2, function(x) which(x != ''))
-imgsz <- 0.15
-tab <- flextable(totab) %>%
-  colformat_image(j = 3, i = colind[[1]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 4, i = colind[[2]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 5, i = colind[[3]], width = imgsz, height = imgsz) %>% 
-  colformat_image(j = 6, i = colind[[4]], width = imgsz, height = imgsz) %>% 
-  width(j = 2, width = 2.5) %>%
-  width(j = c(1, 3:6), width = 3 / 5) %>%
-  bold(part = 'header') %>%
-  colformat_double(digits = 2) %>%
-  valign(valign = 'top', part = 'header') %>%
-  align(j = 3:6, align = 'center', part = 'all') %>% 
-  set_caption(
-    as_paragraph(
-      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.", props = fp_text_default(font.family = "Arial"))
-              ), 
[…]

### 2023-08-05 submission/paper.R

@@ -1,143 +1,0 @@
-# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
-# Please edit paper.Rmd to modify this file
-
-## ----setup, include=FALSE-----------------------------------------------------
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-
-library(flextable)
-library(dplyr)
-library(here)
-
-flextable::set_flextable_defaults(font.size = 7, padding = 0)
-
-load(file = here('tabs/filerequirements.RData'))
-
-
-## ----workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package. WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'----
-knitr::include_graphics('figs/workflow.png')
-
-
-## ----filreq-------------------------------------------------------------------
-filerequirements %>% fontsize(part = 'all', size = 9)
-
-
-## ----importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'----
-knitr::include_graphics('figs/importflow.png')
-
-
-## ---- echo = T, eval = T, message = F-----------------------------------------
-library(MassWateR)
-
-# import results data
-respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
-resdat <- readMWRresults(respth)
-
-
-## ---- eval = F, echo = T------------------------------------------------------
-#> chk <- resdat
-#> chk[4, 2] <- "Sample"
-#> chk[135, 2] <- "Field"
-#> checkMWRresults(chk)
-
-
-## ---- echo = T, eval = F------------------------------------------------------
[…]

### 2023-08-18 manu-draft.qmd
working on reformatting for plos one

--- 2023-08-05 paper.Rmd
@@
 ---
+format: 
+  docx:
+    reference-doc: my_styles.docx
+    number-sections: true
 title: "MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data"
-date: "`r Sys.Date()`"
-abstract: >
-  The long-term protection and restoration of aquatic resources depends on robust monitoring data; data that require systematic quality control and analysis tools.
-The \CRANpkg{MassWateR} package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
-The tools were developed to address regional needs for programs in Massachusetts, USA, but the principles and outputs can be applicable to monitoring data collected anywhere.
-Users can create quality control reports, perform outlier analyses, and assess trends by season, date, and site for more than 40 parameters.
-Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
-The automated and reproducible workflow offered by \CRANpkg{MassWateR} is expected to increase the quantity and quality of publicly available data to support the management of aquatic resources.
-draft: true
+bibliography: refs.bib
+csl: plos-one.csl
 author: 
-  # see ?rjournal_article for more information
-  - name: Marcus W. Beck
-    affiliation: Tampa Bay Estuary Program
-    address:
-    - 263 13th Ave S
-    - St. Petersburg, Florida, USA 33701
-    url: https://tbep.org
-    orcid: 0000-0002-4996-0059
+  - Marcus W Beck:
       email: mbeck@tbep.org
-  - name: Benjamen Wetherill
-    url: https://www.acasak.com/
+      institute: [TBEP]
+      correspondence: true
+  - Benjamen Wetherill:
       email: bwetherill@acasak.com 
-    affiliation: ACASAK Consulting
-    address:
-    - Boston, Massachusetts, USA
-  - name: Jillian Carr
-    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
+      institute: [ACA]
+      correspondence: false
+  - Jillian Carr:
       email: Jillian.Carr@umb.edu
-    affiliation: Massachusetts Bays National Estuary Partnership
-    address:
-    - University of Massachusetts Boston, 100 Morrissey Blvd
-    - Boston, Massachusetts, USA 02125
-type: package
-output: 
-  rjtools::rjournal_web_article:
-    self_contained: yes
-    toc: no
-bibliography: RJreferences.bib
-preamble: |
-  \usepackage{multirow}
-  \usepackage{multicol}
-  \usepackage{colortbl}
-  \usepackage{hhline}
-  \newlength\Oldarrayrulewidth
-  \newlength\Oldtabcolsep
-  \usepackage{longtable}
-  \usepackage{array}
-  \usepackage{hyperref}
-  \usepackage{float}
-  \usepackage{wrapfig}\usepackage{longtable}
+      institute: [MASS]
+      correspondence: false
+
+institute:
+  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida 33701 USA
+  - ACA: ACASAK Consulting, Boston, Massachusetts USA
+  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts 02125 USA
+
+filters: 
+  - templates/scholarly-metadata.lua
+  - templates/author-info-blocks.lua
+
+execute: 
+  echo: false
+  warning: false
+  message: false
+  ft.keepnext: false
+  ft.align: left
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+```{r}
+#| include: false
 
 library(flextable)
+library(officer)
+library(officedown)
 library(dplyr)
@@
 ```
+
+## Abstract {.unnumbered}
+
+The long-term protection and restoration of aquatic resources depends on robust monitoring data; data that require systematic quality control and analysis tools.
+The *MassWateR* package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
+The tools were developed to address regional needs for programs in Massachusetts, USA, but the principles and outputs can be applicable to monitoring data collected anywhere.
+Users can create quality control reports, perform outlier analyses, and assess trends by season, date, and site for more than 40 parameters.
+Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
+The automated and reproducible workflow offered by *MassWateR* is expected to increase the quantity and quality of publicly available data to support the management of aquatic resources.
 
@@
 As an example, dozens of community-driven environmental organizations in Massachusetts, USA, collect water quality data, yet government agencies are only able to access and utilize a fraction of those datasets.
-The Massachusetts Bays National Estuary Partnership funded the development of \CRANpkg{MassWateR} described herein to build capacity among water monitoring programs to generate and share high quality data.
+The Massachusetts Bays National Estuary Partnership funded the development of *MassWateR* described herein to build capacity among water monitoring programs to generate and share high quality data.
 This capacity need is not specific to Massachusetts, thus, the tools were developed with transferability in mind.
 
-The use of R with document generation systems offered through packages like \CRANpkg{knitr} [@Xie15] and \CRANpkg{rmarkdown} [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
+The use of R with document generation systems offered through packages like *knitr* [@Xie15] and *rmarkdown* [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Portal (WQP) database maintained by the US Environmental Protection Agency (USEPA) and contributed to via the Water Quality eXchange (WQX).
 This database is the largest source of monitoring data in the United States that includes information on hydrologic conditions and chemical, physical, and biological measurements from surface waters.
-Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as \CRANpkg{ggplot2} [@Wickham16] and others in the \CRANpkg{tidyverse} [@Wickham19] offer useful tools to synthesize and visualize results.
+Further, many environmental resource managers have the need to analyze status and trends in monitoring data and R packages such as *ggplot2* [@Wickham16] and others in the *tidyverse* [@Wickham19] offer useful tools to synthesize and visualize results.
 Integrating this functionality into a single package is expected to have wide ranging utility for anyone collecting surface water data and is likely to improve the quality and insights obtained from these data.
 
-This paper describes the \CRANpkg{MassWateR} package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
+This paper describes the *MassWateR* package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
 The regional focus of the package is for monitoring data collected in Massachusetts, USA, with QC reports submitted to the Massachusetts Department of Environmental Protection (MADEP) and data submitted to the national WQP database.
-Although the initial conception of \CRANpkg{MassWateR} was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine and commonly used methods for data collected elsewhere.
+Although the initial conception of *MassWateR* was to address regional needs in Massachusetts, there is nothing specific in the package that prevents its use outside of the state as the QC checks and analyses follow routine and commonly used methods for data collected elsewhere.
 As such, this paper is written with emphasis on how the tools are broadly applicable to anyone interested in improving efficiency and reproducibility of QC checks, in addition to analysis of water quality data and submission to WQX as the largest source of water quality monitoring data in the US.
 
-# Requirements for using \CRANpkg{MassWateR}
+# Requirements for use
 
 To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
-However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN \ctv{Hydrology} Task View).
-In particular, the \CRANpkg{dataRetrieval} package [@DeCicco22] has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
+However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN [Hydrology](https://cran.r-project.org/web/views/Hydrology.html) Task View).
+In particular, the *dataRetrieval* package [@DeCicco22] has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
 This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
 As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.
-Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like \CRANpkg{dataRetrieval} by increasing the amount of data that can be accessed through the WQP.
-The \CRANpkg{MassWateR} package was developed to provide this benefit.
+Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like *dataRetrieval* by increasing the amount of data that can be accessed through the WQP.
+The *MassWateR* package was developed to provide this benefit.
 
-Users can engage with \CRANpkg{MassWateR} to achieve different goals.
+Users can engage with *MassWateR* to achieve different goals.
 This design was intentional based on likely differences in needs among the user community.
@@
 That is, state institutions require QC reporting for regulatory assessments, whereas data submission to WQX may be a separate process.
-Users may also simply have a need to explore trends or to summarize their data, while also wanting to extend these analyses beyond \CRANpkg{MassWateR} using additional R packages.
-Figure \@ref(fig:workflow) demonstrates how a user may apply the functions in \CRANpkg{MassWateR} once the required data are imported.
+Users may also simply have a need to explore trends or to summarize their data, while also wanting to extend these analyses beyond *MassWateR* using additional R packages.
+@fig-workflow demonstrates how a user may apply the functions in *MassWateR* once the required data are imported.
 The functions allow a user to engage with their data several ways.
@@
 The second step can be used to create a QC report for submission to a regulatory agency.
-The third step is data analysis and visualization, using \CRANpkg{MassWateR} functions and downstream analysis with additional R packages and functions.
+The third step is data analysis and visualization, using MassWateR functions and downstream analysis with additional R packages and functions.
 The fourth and final step can create a formatted table for WQX submission.
 
-```{r workflow, fig.cap = 'Workflow demonstrating how a user could engage with the \\CRANpkg{MassWateR} package.
-WQX: Water Quality Exchange; QC: Quality Control.', fig.alt='Workflow diagram showing four ways to engage with MassWateR', out.width='100%'}
+```{r}
+#| label: fig-workflow
+#| fig-cap: 'Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.'
+#| fig-alt: 'Workflow diagram showing four ways to engage with *MassWateR*'
+#| out-width: '100%'
 knitr::include_graphics('figs/workflow.png')
@@
 
-No matter the user need, all data inputs to \CRANpkg{MassWateR} must follow a strict format.
+No matter the user need, all data inputs to *MassWateR* must follow a strict format.
 Developing a workflow to accommodate data inputs from the dozens of potential users from several organizations that use different data formats would have been impractical.
@@
 These resources included several training activities that were conducted during package development and templates demonstrating the appropriate format and rationale.
-The trainings, \CRANpkg{pkgdown} [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were also implemented so that learning R was not a significant limitation for using the package.
+The trainings, *pkgdown* [website](https://massbays-tech.github.io/MassWateR/) [@Wickham22], and [Community of Practice forum](https://massbays.discourse.group/login) were also implemented so that learning R was not a significant limitation for using the package.
 
-The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filreq), including how each file applies to the workflow steps in Figure \@ref(fig:workflow).
+The required data files for using *MassWateR* are shown in `r run_reference(id = "tbl-filreq")`, including how each file applies to the workflow steps in @fig-workflow.
 The files are imported into R using specific `read` functions with relevant checks, explained in the next section.
 These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.
-The largest input file required for all parts of the workflow in Figure \@ref(fig:workflow) is the results file.
+The largest input file required for all parts of the workflow in @fig-workflow is the results file.
 This file includes all water quality monitoring data to be used with the package and the recommendation is that the results data include a year of sampling as reporting typically follows an annual cycle.
@@
 
-```{r filreq}
-filerequirements %>% fontsize(part = 'all', size = 9)
+```{r}
+#| label: tbl-filreq
+#| tbl-cap: 'File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.'
+filerequirements
 ```
 
-The following sections describe the basic approach to using functions in \CRANpkg{MassWateR} for any of the processes in the workflow.
-The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
+The following sections describe the basic approach to using functions in *MassWateR* for any of the processes in the workflow.
+The naming convention for the functions is meant to provide users with an intuitive format for understanding what each funcfiletion does and the step of the workflow for which the function applies.
 Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
@@
 
-# MassWateR functions
+# Package workflow
 
@@
 The primary task of the `read` functions is to ensure all imported files follow the required format for the package.
-Excel files are the expected format for all inputs and the `read` functions use the `read_excel` function from the \CRANpkg{readxl} package [@Wickham23].
+Excel files are the expected format for all inputs and the `read` functions use the `read_excel` function from the *readxl* package [@Wickham23].
 The `read` functions do very little other than import the file - once the file is imported it is immediately passed to one of the relevant `check` functions inside the `read` function.
@@
 The error will typically indicate which parts of the input file need to be changed to rectify the issue, often indicating a specific cell in the Excel file that requires attention.
-As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (Figure \@ref(fig:importflow)).
+As such, the workflow is intended to be iterative, where a user imports a file, receives an error, manually changes the input file in Excel, then imports the data again until all checks pass (@fig-importflow).
 Again, this design was intentional as many monitoring agencies and groups organize data differently and a standard input format for the package was the best option to accommodate all potential users.
-This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using \CRANpkg{MassWateR}.
+This may also encourage future standardization among monitoring groups for how data are maintained to ease formatting challenges to using *MassWateR*.
 A user only needs to format their data once to use the package.
 
-```{r importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.
+```{r}
+#| label: fig-importflow
+#| fig-cap: "Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.
 All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`)."
+#| fig-alt: 'Diagram showing pseudocode for importing and fixing a data file with *MassWateR*'
+#| out-width: "100%"
 knitr::include_graphics('figs/importflow.png')
@@
 
-```{r, echo = T, eval = T, message = F}
+```{r}
+#| echo: true
+#| eval: true
+#| message: false
 library(MassWateR)
@@
 The `checkMWRresults()` function is run inside the `readMWRresults()` function and runs the checks (e.g., the column names are correct, all required columns are present, activity types are valid, etc.), but then stops when invalid activity types in the `Activity Type` column are found.
-In this example, a user would need to change the entries in rows 4 and 135 of the `Activity Type` column in their Excel file to fix the issue and import the file again as in Figure \@ref(fig:importflow).
+In this example, a user would need to change the entries in rows 4 and 135 of the `Activity Type` column in their Excel file to fix the issue and import the file again as in @fig-importflow.
 The online [vignette](https://massbays-tech.github.io/MassWateR/articles/inputs.html#data-import-and-checks) specifies the valid entries.
 
-```{r, eval = F, echo = T}
+```{r}
+#| eval: false
+#| echo: true
 chk <- resdat
@@
 
-```{r, echo = T, eval = F}
+```{r}
+#| eval: false
+#| echo: true
 apply(readxl::read_excel('path/to/results.xlsx'), 2, unique)
@@
 
-After all file format checks are completed and errors fixed, a standard approach for using \CRANpkg{MassWateR} is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
+After all file format checks are completed and errors fixed, a standard approach for using *MassWateR* is to import all required files and save them as a list of named data frame objects that can be used by nearly all the package functions.
 This prevents the need to identify which input datasets are needed for each function, although the latter approach could be used because arguments for individual input files are also provided in all functions.
@@
 
-```{r, results = 'hide', echo = T}
+```{r}
+#| results: 'hide'
+#| echo: true
 # import results data
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The `paramsMWR` dataset included with \CRANpkg{MassWateR} provides a lookup table of the parameters that can be used with the package.
+The `paramsMWR` dataset included with *MassWateR* provides a lookup table of the parameters that can be used with the package.
 On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
@@
 Laboratories typically have a standard reporting format based on the same methodology or instrument used to measure water quality parameters.
-Both the number of parameters and acceptable units can easily be extended and those herein were chosen simply to limit the development of \CRANpkg{MassWateR} to a manageable scope.
+Both the number of parameters and acceptable units can easily be extended and those herein were chosen simply to limit the development of *MassWateR* to a manageable scope.
 
@@
 Identifying and potentially removing or correcting outliers is a critical part of quality control.
-The functions in \CRANpkg{MassWateR} simply identify potential outliers to provide an opportunity for users to address these values.
+The functions in *MassWateR* simply identify potential outliers to provide an opportunity for users to address these values.
 The decision on how to address outliers remains with the user and no automated tools are provided in the package to correct or remove these values.
@@
 
-```{r, fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
+```{r}
+#| fig-height: 4
+#| fig-width: 8
+#| echo: true
+#| out-width: '95%'
+#| fig-align: 'center'
 anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
@@
 
-```{r, echo = T}
+```{r}
+#| echo: true
 anlzMWRoutlier(fset = fsetls, param = "DO", group = "month", 
@@
 
-```{r, echo = T, eval = F}
+```{r}
+#| echo: true
+#| eval: false
 # create word output
@@
 
-As in Figure \@ref(fig:importflow), a user can identify outliers from the results, modify the file in Excel, and import the file again for further QC reporting or analysis.
+As in @fig-importflow, a user can identify outliers from the results, modify the file in Excel, and import the file again for further QC reporting or analysis.
 
@@
 
-The quality control functions in \CRANpkg{MassWateR} are designed to create a single report that compares the water quality data in the results file (`resdat`) to data quality objectives in the accuracy (`accdat`) and frequency and completeness (`frecomdat`) files.
+The quality control functions in *MassWateR* are designed to create a single report that compares the water quality data in the results file (`resdat`) to data quality objectives in the accuracy (`accdat`) and frequency and completeness (`frecomdat`) files.
 In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
@@
 
-The following describes the types of QC measurements that are evaluated by \CRANpkg{MassWateR}:
+The following describes the types of QC measurements that are evaluated by *MassWateR*:
 
@@
 
-Additionally, \CRANpkg{MassWateR} allows a user to include "qualified samples" in the results file.
+Additionally, *MassWateR* allows a user to include "qualified samples" in the results file.
 These samples are similar as those from the above criteria and are identified by the user as having special circumstances.
@@
 The `qcMWRreview()` function creates a single QC report as a Word document that evaluates all data in the results file using the DQOs in the `accdat` and `frecomdat` input files.
-This file includes several tables created by individual \CRANpkg{MassWateR} functions, where each describes relevant evaluations for the QC assessment.
+This file includes several tables created by individual *MassWateR* functions, where each describes relevant evaluations for the QC assessment.
 The file is created as follows, which typically requires less than a minute to complete and is followed by a message in the console indicating the report was successfully created and the path where the Word file is located.
 A user can then further edit the Word document as needed.
-The first two pages of the QC report are shown in Figure \@ref(fig:qcex).
+The first two pages of the QC report are shown in @fig-qcex.
 
-```{r, echo = T, eval = F}
+```{r}
+#| echo: true
+#| eval: false
 qcMWRreview(fset = fsetls, output_dir = getwd())
@@
 
-```{r qcex, fig.cap = "The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
+::: {#fig-qcex layout-ncol=2}
+
+![](figs/qcreview1.png)
+
+![](figs/qcreview2.png)
+
+The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
 The first page shows the data quality objectives for accuracy, frequency, and completeness.
@@
 Parameters shown in red or marked as 'MISS' failed the data quality objectives.
-Users can edit the Word file as needed, e.g., entering the organization name or adding notes.", fig.alt = "A Word document showing the first two pages of the quality control report.", out.width = '50%', fig.show='hold'}
-knitr::include_graphics('figs/qcreview1.png')
-knitr::include_graphics('figs/qcreview2.png')
-```
+Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
+:::
 
 The QC report is built using several functions that can be used individually as needed.
-In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create \CRANpkg{flextable} [@Gohel23] objects that can be viewed in RStudio and are compatible with Word output.
+In particular, the `tabMWRacc()`, `tabMWRfre()`, and `tabMWRcom()` create *flextable* [@Gohel23] objects that can be viewed in RStudio and are compatible with Word output.
 These functions are useful for understanding how the QC checks are created for the separate components of the QC report.
@@
 
-```{r, echo = T, eval = F}
+```{r}
+#| echo: true
+#| eval: false
 tabMWRacc(fset = fsetls, type = "summary")
 ```
-```{r, echo = F, eval = T}
+```{r}
+#| echo: false
+#| eval: true
 resin <- resdat[resdat$`Characteristic Name` %in% c('Ammonia', 'TP'), ]
@@
 
-```{r, echo = T}
+```{r}
+#| echo: true
 tabMWRacc(fset = fsetls, type = "percent")
@@
 
-```{r, echo = T, eval = F}
+```{r}
+#| echo: true
+#| eval: false
 tabMWRacc(fset = fsetls, type = "individual", accchk = "Field Blanks")
 ```
-```{r, echo = F, eval = T}
+```{r}
+#| echo: false
+#| eval: true
 resin <- resdat[resdat$`Characteristic Name` %in% c('TP', 'Ammonia') ,]
@@
 
-The analysis functions in \CRANpkg{MassWateR} provide a streamlined approach to quickly evaluate data in the results file.
+The analysis functions in *MassWateR* provide a streamlined approach to quickly evaluate data in the results file.
 Although several base R functions and supporting packages can be used to develop custom assessments, it was recognized that many users will not be comfortable developing their own visualization routines.
@@
 
-```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
+```{r}
+#| fig-height: 4
+#| fig-width: 8
+#| echo: true
+#| out-width: '95%'
+#| fig-align: 'center'
 anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
@@
 In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
-Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional \CRANpkg{ggplot2} functionality (i.e., with `geom_hline()` added to the plot output).
+Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional *ggplot2* functionality (i.e., with `geom_hline()` added to the plot output).
 
@@
 
-```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
+```{r}
+#| fig-height: 4
+#| fig-width: 8
+#| echo: true
+#| out-width: '95%'
+#| fig-align: 'center'
 anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
@@
 
-```{r fig.height = 4, fig.width = 8, echo = T,  out.width = '95%', fig.align = 'center'}
+```{r}
+#| fig-height: 4
+#| fig-width: 8
+#| echo: true
+#| out-width: '95%'
+#| fig-align: 'center'
 anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
@@
 Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information for context.
-For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the \CRANpkg{ggmap} package [@Kahle13].
+For example, hydrologic lines and waterbodies from the National Hydrograpy Dataset (NHD) can be shown with varying level of detail and base maps can be included from the *ggmap* package [@Kahle13].
 NHD data were included to provide more specific information on hydrologic features of interest because of insufficient detail provided by standard basemaps.
@@
 
-```{r fig.height = 5, fig.width = 5, echo = T, out.width = '95%', fig.align = 'center'}
+```{r}
+#| fig-height: 5
+#| fig-width: 5
+#| echo: true
+#| out-width: '95%'
+#| fig-align: 'center'
 anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
@@
 
-The last part of the \CRANpkg{MassWateR} workflow is preparation of data for submission to WQX.
+The last part of the *MassWateR* workflow is preparation of data for submission to WQX.
 A single function, `tabMWRwqx()`, is provided to format data inputs using a [template](https://massbays-tech.github.io/MassWateR/RESOURCES.html) designed for data submission.
@@
 
-```{r, echo = T, eval = F}
+```{r}
+#| echo: true
+#| eval: false
 tabMWRwqx(fset = fsetls, output_dir = getwd())
@@
 It is assumed that users are familiar with the WQX data submission portal if they are already using the package, though [training materials](https://www.epa.gov/waterdata/learn-more-about-water-quality-data) from USEPA are available.
-\CRANpkg{MassWateR} eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
+*MassWateR* eliminates the need to format the data by hand and it is expected to increase the amount of data made available on the WQP (via WQX upload) as the user base for the package increases.
 Further, the authors worked with USEPA WQX staff to improve WQX handling of Quality Control-coded data, by improving the list of potential field names and highlighting the need to better connect paired data (e.g., activity types "Quality Control Lab Duplicate 1" and "Quality Control Lab Duplicate 2" were created to pair lab duplicates).
@@
 
-To ensure that \CRANpkg{MassWateR} is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN (January, 2023).
+To ensure that *MassWateR* is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN (January, 2023).
 This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
-Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to R, as well as \CRANpkg{MassWateR}.
-Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with \CRANpkg{MassWateR}.
-However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as \CRANpkg{ggplot2} to create additional visualizations for modifying the existing analysis plots in \CRANpkg{MassWateR}.
-For example, a [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html) was included on the package website to demonstrate how these plots can be modified for custom output using \CRANpkg{ggplot2}.
+Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to R, as well as *MassWateR*.
+Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with *MassWateR*.
+However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as *ggplot2* to create additional visualizations for modifying the existing analysis plots in *MassWateR*.
+For example, a [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html) was included on the package website to demonstrate how these plots can be modified for custom output using *ggplot2*.
 Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
@@
 
-As noted above, \CRANpkg{MassWateR} was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
+As noted above, *MassWateR* was developed to meet specific needs of water quality professionals in Massachusetts, but the principles for QC reporting, analysis, and WQX data submission are largely universal and the package can be used outside of the state as long as the following minor limitations are addressed.
 First, some of the parameter thresholds that are visually overlaid on the analysis plots are unique to Massachusetts, whereas others apply more broadly, such as those defined using standards from the USEPA.
-Users can simply omit the thresholds if they do not apply using `thresh = "none"` or add custom thresholds using standard \CRANpkg{ggplot2} functions.
+Users can simply omit the thresholds if they do not apply using `thresh = "none"` or add custom thresholds using standard *ggplot2* functions.
 Second, the NHD waterbodies used by `anlzMWRmap()` are specific to watersheds that intersect Massachusetts.
-Users can omit these layers from the plot using `addwater = NULL`, add a universal base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from \CRANpkg{ggplot2}.
+Users can omit these layers from the plot using `addwater = NULL`, add a universal base map using the `maptype` argument, or add custom waterbody layers as simple features objects [@Pebesma23] using the `geom_sf()` function from *ggplot2*.
 Third, the QC report created by `qcMWRreview()` uses a format vetted by MADEP.
@@
 Each of these can also be modified by hand in the output file.
-Future enhancements and additions to \CRANpkg{MassWateR} will likely include automated tools to make the package more applicable outside of Massachusetts.
+Future enhancements and additions to *MassWateR* will likely include automated tools to make the package more applicable outside of Massachusetts.
 
-Additional future work to improve the functionality of \CRANpkg{MassWateR} is also expected as the user base increases and the functions mature with additional bug fixes or minor enhancements.
+Additional future work to improve the functionality of *MassWateR* is also expected as the user base increases and the functions mature with additional bug fixes or minor enhancements.
 Specifically, the inclusion of historical data for some of the analysis functions could provide additional context on status and trends for monitoring data at specific locations.
 This enhancement would require the extraction of existing data included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
-Existing R packages leverage these tools (e.g., \CRANpkg{dataRetrieval}) and a similar approach could be used by \CRANpkg{MassWateR}.
+Existing R packages leverage these tools (e.g., *dataRetrieval*) and a similar approach could be used by *MassWateR*.
 A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed *in situ*.
@@
 For the latter, automated tools are needed for detecting and handling QC issues common with monitoring equipment deployed in the field for long duration, such as instrument drift, biofouling, or missing data.
-More complex methods for detecting outliers in continuous monitoring data beyond the existing tools in \CRANpkg{MassWateR} will also be needed [@Leigh19].
+More complex methods for detecting outliers in continuous monitoring data beyond the existing tools in *MassWateR* will also be needed [@Leigh19].
 
@@
 
-The \CRANpkg{MassWateR} package represents an important set of functions that are expected to significantly improve how monitoring programs and resource managers implement QC assessments and apply exploratory analyses to water quality monitoring data.
+The *MassWateR* package represents an important set of functions that are expected to significantly improve how monitoring programs and resource managers implement QC assessments and apply exploratory analyses to water quality monitoring data.
 The package can also expedite preparation of data for submission to the largest water quality database in the United States, which will likely contribute to the new data made available through the WQP.
 These activities are critically needed to ensure that monitoring data are of sufficient quality and quantity for use in regulatory applications or routine assessments of status and trends of environmental resources.
-As mentioned throughout this paper, \CRANpkg{MassWateR} was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in Figure \@ref(fig:workflow) can easily be applied to data collected elsewhere.
+As mentioned throughout this paper, *MassWateR* was developed to address specific needs for resource management professionals in Massachusetts, although the workflow in @fig-workflow can easily be applied to data collected elsewhere.
 Future development of the package will not only make the package functions more generalizable to other locations, but also provide additional features for working with continuous and historical monitoring data.
-The community of practice developed for \CRANpkg{MassWateR} is expected to grow and the package will be supported by the authors as the user base increases.
+The community of practice developed for *MassWateR* is expected to grow and the package will be supported by the authors as the user base increases.
 
@@
 OS\-84029801\-0.
-We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.
-We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments and WQX staff at USEPA for consult on submitting data formatted with \CRANpkg{MassWateR}.
+We thank the early users of *MassWateR* that contributed ideas on improving the package during initial testing.
+We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments and WQX staff at USEPA for consult on submitting data formatted with *MassWateR*.
+
+# References

### 2023-08-18 R/tabs.R

@@ -29,12 +29,7 @@ tab <- flextable(totab) %>%
   colformat_double(digits = 2) %>%
   valign(valign = 'top', part = 'header') %>%
   align(j = 3:6, align = 'center', part = 'all') %>% 
-  set_caption(
-    as_paragraph(
-      as_chunk("File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.", props = fp_text_default(font.family = "Arial"))
-              ), 
-    word_stylename = "Table Caption"
-    )
+  fontsize(part = 'all', size = 9)
 
 filerequirements <- tab
 save(filerequirements, file = here('tabs/filerequirements.RData'))

### 2023-08-20 manu-draft.qmd
changing fig imports to markdown only, filerequirements table is now kable

@@
   message: false
-  ft.keepnext: false
-  ft.align: left
 ---
@@
 
-library(flextable)
-library(officer)
-library(officedown)
 library(dplyr)
 library(here)
-
-flextable::set_flextable_defaults(font.size = 7, padding = 0)
 
@@
 
-```{r}
-#| label: fig-workflow
-#| fig-cap: 'Workflow demonstrating how a user could engage with the *MassWateR* package. WQX: Water Quality Exchange; QC: Quality Control.'
-#| fig-alt: 'Workflow diagram showing four ways to engage with *MassWateR*'
-#| out-width: '100%'
-knitr::include_graphics('figs/workflow.png')
-```
+![Workflow demonstrating how a user could engage with the *MassWateR* package.
+WQX: Water Quality Exchange; QC: Quality Control.](figs/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
 
@@
 
-The required data files for using *MassWateR* are shown in `r run_reference(id = "tbl-filreq")`, including how each file applies to the workflow steps in @fig-workflow.
+The required data files for using *MassWateR* are shown in @tbl-filreq, including how each file applies to the workflow steps in @fig-workflow.
 The files are imported into R using specific `read` functions with relevant checks, explained in the next section.
@@
 #| tbl-cap: 'File requirements for using MassWateR.  Check marks indicate which file is required for each part of the MassWateR workflow. DQO: Data Quality Objective; QC: Quality Control.'
-filerequirements
+knitr::kable(filerequirements)
 ```
@@
 
-```{r}
-#| label: fig-importflow
-#| fig-cap: "Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.
+![Pseudocode demonstrating the iterative process of importing a required data file for *MassWateR*.
 All read functions import an Excel file from the user-specified path (e.g., `respth`) and the imported file is then passed to a check function.
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`)."
-#| fig-alt: 'Diagram showing pseudocode for importing and fixing a data file with *MassWateR*'
-#| out-width: "100%"
-knitr::include_graphics('figs/importflow.png')
-```
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](figs/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
 

### 2023-08-20 R/tabs.R

@@ -1,35 +1,17 @@
-library(flextable)
 library(tidyverse)
 library(here)
 
 # file inputs ---------------------------------------------------------------------------------
 
-chkloc <- here(list.files('tabs', pattern = 'check', full.names = T))
-
 totab <- tibble(
-  `Formatted file` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
-  `Description` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
-  `1. QC screening` = c('r', 'r', 'r', 'r', ''), 
-  `2. QC reporting` = c('r', 'r', 'r', '', ''),
-  `3. Data analysis` = c('r', 'r', '', 'r', ''),
-  `4. WQX formatting` = c('r', 'r', '', 'r', 'r'),
+  `**Formatted file**` = c('Results', 'DQO accuracy', 'DQO frequency and completeness', 'Sites', 'WQX metadata'), 
+  `**Description**` = c('Water quality results organized by sample location and date', 'Summary of data quality objectives that describe quality control accuracy for data in the results file', 'Summary of data quality objectives that describe quality control frequency and completeness measures for data in the results file', 'A site metadata file, including location names, latitude, longitude, and additional grouping factors for sites in the results file', 'A wqx metadata file required for generating output to facilitate data upload to WQX'),
+  `**1. QC screening**` = c('r', 'r', 'r', 'r', ''), 
+  `**2. QC reporting**` = c('r', 'r', 'r', '', ''),
+  `**3. Data analysis**` = c('r', 'r', '', 'r', ''),
+  `**4. WQX formatting**` = c('r', 'r', '', 'r', 'r'),
 ) %>% 
-  mutate_at(vars(-`Formatted file`, -`Description`), function(x) gsub('^r$', chkloc, x))
+  mutate_at(vars(-`**Formatted file**`, -`**Description**`), function(x) gsub('^r$', '\u2713', x))
 
[…]

### 2023-08-20 manu-draft.qmd
more formatting, figures from code examples now include captions and citations

@@
 
+knitr:
+  opts_chunk: 
+    fig.path: 'images/'
+
 execute: 
@@
   message: false
+  ft.keepnext: false
+  ft.align: left
+  fig-dpi: 300
 ---
@@
 #| include: false
+#|
 
+library(flextable)
 library(dplyr)
@@
 
+flextable::set_flextable_defaults(font.size = 7, padding = 0)
+
 load(file = here('tabs/filerequirements.RData'))
 ```
+
+Short title: *MassWateR* R package for water quality data
 
@@
 Users can create quality control reports, perform outlier analyses, and assess trends by season, date, and site for more than 40 parameters.
-Users can also prepare data for submission to the USEPA Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
+Users can also prepare data for submission to the United States Environmental Protection Agency Water Quality Exchange, thus sharing data to the largest water quality database in the United States.
 The automated and reproducible workflow offered by *MassWateR* is expected to increase the quantity and quality of publicly available data to support the management of aquatic resources.
@@
 ![Workflow demonstrating how a user could engage with the *MassWateR* package.
-WQX: Water Quality Exchange; QC: Quality Control.](figs/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
+WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
 
@@
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](figs/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
 
@@
 The `param` argument specifies the water quality parameter to evaluate and the `group` argument specifies how the boxplots are grouped (by year, month, week, or station).
-In the following example, three stations are identified as potential outliers for the respective month.
+In the following example (@fig-outlier), three stations are identified as potential outliers for the respective month.
 Note that the outliers may differ slightly by the grouping choice as they are specific to each value on the x-axis.
@@
 ```{r}
+#| label: fig-outlier
+#| fig-cap: "Example plot showing identification of outliers in a water quality dataset.  The plot was created using the `anlzMWRoutlier()` function."
 #| fig-height: 4
@@
 
-![](figs/qcreview1.png)
+![](images/qcreview1.png)
 
-![](figs/qcreview2.png)
+![](images/qcreview2.png)
 
@@
 
-Seasonal trends can be evaluated using the `anlzMWRseason()` function that summarizes results for a single parameter using boxplots or barplots with seasonal groups assigned to months or weeks of the year.
+Seasonal trends can be evaluated using the `anlzMWRseason()` function that summarizes results for a single parameter using boxplots or barplots with seasonal groups assigned to months or weeks of the year (@fig-season).
 Boxplots or barplots can also include jittered points of the observations on top or only the jittered points can be shown.
-Below demonstrates a jittered boxplot of dissolved oxygen observations by month.
+@fig-season demonstrates a jittered boxplot of dissolved oxygen observations by month.
 
 ```{r}
+#| label: fig-season
 #| fig-height: 4
@@
 #| fig-align: 'center'
+#| fig-cap: "Example plot showing water quality results grouped by month.  The plot was created using the `anlzMWRseason()` function."
 anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
@@
 
-The `anlzMWRdate()` function plots results as time series on the date the samples or measurements were collected.
+The `anlzMWRdate()` function plots results as time series on the date the samples or measurements were collected (@fig-date).
 This information can be used to evaluate how samples have changed at individual sites over time or as aggregate samples across sites.
@@
 For example, all sites along the same river or tributary can be aggregated.
-The following demonstrates an aggregation of sites by the mainstem of the Assabet river and its tributaries using the `group = "locgroup"` argument.
+@fig-date shows an aggregation of sites by the mainstem of the Assabet river and its tributaries using the `group = "locgroup"` argument.
 A user can specify any desired grouping in the `Location Group` column of the site metadata file.
@@
 ```{r}
+#| label: fig-date
 #| fig-height: 4
@@
 #| fig-align: 'center'
+#| fig-cap: "Example plot showing water quality results grouped by sample date.  The plot was created using the `anlzMWRdate()` function."
 anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
@@
 
-The `anlzMWRsite()` function can be used to view data organized by site.
+The `anlzMWRsite()` function can be used to view data organized by site (@fig-site).
 This function summarizes results for a single parameter using boxplots or barplots separately for each site on the x-axis.
@@
 ```{r}
+#| label: fig-site
 #| fig-height: 4
@@
 #| fig-align: 'center'
+#| fig-cap: "Example plot showing water quality results grouped by site.  The plot was created using the `anlzMWRsite()` function."
 anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
@@
 
-Finally, maps of results at each site can be created with the `anlzMWRmap()` function.
+Finally, maps of results at each site can be created with the `anlzMWRmap()` function (@fig-map).
 Parameter values at each site are summarized with colors indicating relative values and the maps can include various spatial information for context.
@@
 Currently, only flowlines and waterbodies that intersect Massachusetts are included, although examples are provided in a package [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html#modifying-masswater-plots) that demonstrate how to include custom shapefiles in the map.
-The below example shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (`addwater = "medium"`).
+@fig-map shows mean dissolved oxygen concentrations using the medium level of detail for the NHD maps (`addwater = "medium"`).
 
 ```{r}
+#| label: fig-map
 #| fig-height: 5
@@
 #| fig-align: 'center'
+#| fig-cap: "Example map showing water quality results averaged by sampling location. The map was created using the `anlzMWRmap()` function."
 anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
@@
 
-# Building a community and future work
+# Discussion
 
@@
 
-# Summary
+# Conclusions
 
@@
 
-# Acknowledgments
+# Acknowledgments {.unnumbered}
 
-This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership, Grant No\.
-OS\-84029801\-0.
 We thank the early users of *MassWateR* that contributed ideas on improving the package during initial testing.
@@
 
-# References
+# References {.unnumbered}

### 2023-08-20 manu-draft.qmd
qcreview figure combined in one file using imagemagick convert, added citation to R

@@
 The long-term protection and restoration of aquatic resources depends on robust monitoring data; data that require systematic quality control and analysis tools.
-The *MassWateR* package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
+The *MassWateR* R package facilitates quality control, analysis, and data sharing for discrete surface water quality data collected by monitoring programs of various size and technical capacity.
 The tools were developed to address regional needs for programs in Massachusetts, USA, but the principles and outputs can be applicable to monitoring data collected anywhere.
@@
 
-The use of R with document generation systems offered through packages like *knitr* [@Xie15] and *rmarkdown* [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
+The use of R [@RCT2023] with document generation systems offered through packages like *knitr* [@Xie15] and *rmarkdown* [@Allaire23] can generate QC reports that follow a standard format for review by regulatory agencies.
 These tools can also be used to format water quality data for submission to state or national water quality databases, such as the Water Quality Portal (WQP) database maintained by the US Environmental Protection Agency (USEPA) and contributed to via the Water Quality eXchange (WQX).
@@
 ```
-
-::: {#fig-qcex layout-ncol=2}
-
-![](images/qcreview1.png)
-
-![](images/qcreview2.png)
-
-The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
+![The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
 The first page shows the data quality objectives for accuracy, frequency, and completeness.
@@
 Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
-:::
+](images/qcex.png){#fig-qcex}
 

### 2023-08-28 manu-draft.qmd
all png figs to svg or tif, additional formatting for PO

@@
     number-sections: true
-title: "MassWateR: Improving Quality Control, Analysis, and Sharing of Water Quality Data"
+title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
 bibliography: refs.bib
 csl: plos-one.csl
+crossref:
+  fig-title: Fig
+  fig-prefix: Fig 
 author: 
@@
 institute:
-  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida 33701 USA
+  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida, USA
   - ACA: ACASAK Consulting, Boston, Massachusetts USA
-  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts 02125 USA
+  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts, USA
 
@@
   ft.align: left
+  fig-format: svg
   fig-dpi: 300
@@
 Short title: *MassWateR* R package for water quality data
+
+{{< pagebreak >}}
 
@@
 ![Workflow demonstrating how a user could engage with the *MassWateR* package.
-WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.png){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
+WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.tif){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
 
@@
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.png){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.tif){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
 
@@
 Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
-](images/qcex.png){#fig-qcex}
+](images/qcex.tif){#fig-qcex}
 

### 2023-09-12 revision/review-response.qmd
plos one revision started

---
format: 
  docx:
    reference-doc: response_styles.docx

execute: 
  echo: false
  warning: false
  message: false
---

```{r echo = F, cache = F, eval = F}
#| eval: false
spelling::spell_check_files(here::here('revision/review-response.qmd'))
```

We sincerely thank the academic editor and two reviewers for providing thoughtful comments on our manuscript.  We provide a point-by-point response to these comments below.

## Academic Editor

Though one of the reviewers recommended a complete rejection, I found that this study could be of benefit to the community especially in the industry 4.0 era. However, I request that you take into consideration the following while revising your manuscript.

1. You should describe explicitly how the package provides a better alternative to all the other existing packages. Where applicable, cite the weaknesses of the existing packages with supporting citations.

__Response__:

2. Make appropriate citations to literature sources. For example, in L26 and L29, you talk about an Act and an EU framework whose sources are not cited. The same applies to L39-40, where you argue out why this communication could be important but without any supporting citation(s).  Similar omissions are evident in the DISCUSSION where you should make appropriate citation of the ‘‘community of practice established’’ and any outcomes (L521-537, and so forth).

__Response__:

3. L87-99 appears to should have been part of the introduction, highlighting what the MassWateR brings onboard.

__Response__:

4. Figure 1 could best be presented as a flow/block diagram.

__Response__:

5. For Table 4, it would be important to provide all the parameters tested as a supplementary file to support the submission. Please ensure that the full details of the algorithms designed are provided, and where there are restrictions, it should otherwise be stated.

__Response__:

6. To improve the chances of manuscript suitability for PLOS ONE, ensure that the criteria listed for manuscript types (https://journals.plos.org/plosone/s/submission-guidelines#loc-methods-software-databases-and-tools) are met. i.e. Utility, Validation and Availability for articles describing new/improved METHODS, SOFTWARE, DATABASES, and TOOLS.

__Response__:

## Reviewer 1

The paper describes a new R package for the processing of water quality information, mainly following US standards, but could be adapted for other regions. It is well written and easy to follow. I have only a few minor comments. Several of the figures were missing from the submission, so I could not check them (Figure 3, and Figure 5 following).

__Response__:

L27 and 29 please cite respective regulatory frameworks

__Response__:

L108 should be „their data in several ways“

__Response__:

L109 should be „outlier checks“

__Response__:

L137 should be function - spelling error

__Response__:

L327 should be „to evaluate“

__Response__:

L334-335 I guess more correct would be to state „to verify that the parameter is below a certain threshold, e.g. below detection limit“. Even if the parameter has a value of zero - the parameter itself is not absent

__Response__:

336-337 same

__Response__:

338-339 More correct would be „to assess the similarity of values, i.e. precision is high. (Precision is a value that is calculated from bot measurements - do not understand how each measurement can have its own precision)

__Response__:

385 Add: „in red in Table 3 show…“

__Response__:

439 spelling „can be“

__Response__:

506 I guess public use is better than public consumption

__Response__:

## Reviewer 2

The availability of reliable monitoring data is the basis of scientific research. This study collected discrete surface water quality data generated by MassWateR software package and analyzed the trend of parameters. The study has some fundamental significance. However, this paper is more like a technical manual than a scientific research paper. Therefore, I would recommend the authors to submit the paper to a technical journal rather than a research-oriented journal.

__Response__:

In addition, the transferability of the developed tool needs to be demonstrated and analyzed, which is directly related to its application value. The authors should give concrete examples in this area;

__Response__:

Finally, the quality of the authors' images is so poor that improving the clarity is very necessary.

__Response__:

### 2023-09-12 revision/review-response.qmd
working on revisions

@@
     reference-doc: response_styles.docx
+bibliography: ../refs.bib
+csl: ../plos-one.csl
 
@@
 
-We sincerely thank the academic editor and two reviewers for providing thoughtful comments on our manuscript.  We provide a point-by-point response to these comments below.
+We sincerely thank the academic editor and two reviewers for providing thoughtful comments on our manuscript.
+We provide a point-by-point response to these comments below.
+We hope that these responses and changes to the manuscript are satisfactory.
 
@@
 
-__Response__:
+**Response**: Thank you for this comment.
+As noted in the original submission on line 88, there are no other R packages that we are aware of that provide similar functionality.
+As such, there is no basis of comparison of MassWateR to determine relative strengths/weakness with other packages.
+However, we have added text describing other R packages that are somewhat related and have included a description of software packages outside of the R environment to provide a more comprehensive discussion of alternatives.
+The following additions were made:
+
+"The *TADA* R package [@Mullin22] is also currently under development as a resource for for compiling and evaluating data from the WQP.
+*TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP."
+
+"Other software platforms outside of the R environment provide various services for quality control of water quality data.
+The [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
+Functionality is provided to pre-process and synthesize multiple data streams, manually correct erroneous values, and to visualize results for decision-making.
+A graphical user interface is provided to access the various features of the software as compared to a programmatic approach for building custom routines.
+Moreover, the software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
+Similar platforms are available from companies that manufacture data loggers (e.g., [YSI](https://www.ysi.com/), [HOBO](https://www.onsetcomp.com/products/software/hoboware)), all of which are specific to the monitoring equipment and not broadly transferable.
+Alternative publicly funded software and data services are provided by the Consortium of Universities for the Advancement of Hydrologic Science ([CUAHSI](https://www.cuahsi.org/data-services/solutions)).
+Services provided by CUAHSI include data discovery, archiving, cloud computing, and analysis, with many of the services available in open source environments (e.g., [Python](https://www.python.org/)).
+However, the services provided by CUAHSI are meant to address a variety of different resources and use cases, none of which are immediately related to quality control reporting and data submission to public institutions.
+As such, Specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed."
 
@@
 The same applies to L39-40, where you argue out why this communication could be important but without any supporting citation(s).
-Similar omissions are evident in the DISCUSSION where you should make appropriate citation of the ‘‘community of practice established’’ and any outcomes (L521-537, and so forth).
+Similar omissions are evident in the DISCUSSION where you should make appropriate citation of the "community of practice established" and any outcomes (L521-537, and so forth).
 
-__Response__:
+**Response**: We have added citations where needed.
+Specifically, line 26 includes a link to a description of the US Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim), note that there is no citation provided in the references because this is legislative code), line 29 includes a citation to the European Water Framework Directive [Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000, @pollard1998],
 
@@
 
-__Response__:
+**Response**: This paragraph and the additions shown above were moved to the introduction.
 
@@
 
-__Response__:
+**Response**:
 
@@
 
-__Response__:
+**Response**: Thank you for your review comments.
+We have provided responses below.
+Please note that some of the figures provided in the journal submission system can only be viewed by selecting the download link on the page for each figure.
+I have verified that all figures were present in the original submission and the revision.
 
@@
 
-__Response__:
+**Response**: References were added for both the Clean Water Act and Water Framework Directive.
 
-L108 should be „their data in several ways“
+L108 should be "their data in several ways"
 
-__Response__:
+**Response**: Accepted suggestion.
 
-L109 should be „outlier checks“
+L109 should be "outlier checks"
 
-__Response__:
+**Response**: Edited the sentence as follows: "The first step, QC screening, is often iterative as a user can modify parts of the raw data based on messages from the data import functions or checks for outliers."
 
@@
 
-__Response__:
+**Response**: Corrected.
 
-L327 should be „to evaluate“
+L327 should be "to evaluate"
 
-__Response__:
+**Response**: Edited the sentence as follows: "The QC checks for frequency and completeness can be used to evaluate if..."
 
-L334-335 I guess more correct would be to state „to verify that the parameter is below a certain threshold, e.g.
-below detection limit“.
+L334-335 I guess more correct would be to state "to verify that the parameter is below a certain threshold, e.g.
+below detection limit".
 Even if the parameter has a value of zero - the parameter itself is not absent
 
-__Response__:
+**Response**: Edited as follows: "Measurements in the field to verify that the parameter is below a certain threshold, e.g., below the detection limit of the field equipment"
 
@@
 
-__Response__:
+**Response**: Edited as follows: "Laboratory samples to verify that the parameter is below a certain threshold, e.g., below the detection limit of the laboratory analysis method"
 
-338-339 More correct would be „to assess the similarity of values, i.e.
+338-339 More correct would be "to assess the similarity of values, i.e.
 precision is high.
@@
 
-__Response__:
+**Response**: Accepted suggestion and made a similar edit for lab duplicates.
 
-385 Add: „in red in Table 3 show…“
+385 Add: "in red in Table 3 show..."
 
-__Response__:
+**Response**: Accepted suggestion.
 
-439 spelling „can be“
+439 spelling "can be"
 
-__Response__:
+**Response**: Corrected.
 
@@
 
-__Response__:
+**Response**: Edited the sentence as follows: "...and made accessible for public use."
 
@@
 
-__Response__:
+**Response**: Thank you for taking the time to review our paper.
+Based on the opinion of the academic editor, this paper is considered to be of sufficient interest to the readership of the journal.
+Additionally, the paper is not written as a research article and was submitted as a software manuscript under the acceptable formats considered by the journal (see [here](https://journals.plos.org/plosone/s/submission-guidelines#loc-methods-software-databases-and-tools)).
+The format of these submissions is notably different from those of conventional research articles.
+In particular, papers describing software must demonstrate utility, validation, and availability.
+Please see our comment to the academic editor above regarding these requirements.
 
@@
 
-__Response__:
+**Response**: Thank you for this suggestion.
+In our original submission, we provided substantial text describing how MassWateR can be used in more generic applications, i.e., its transferability.
+This information was provided in the discussion on lines 538-556, where specific considerations were noted for how users could apply the software to novel datasets.
+Truthfully, we are not yet aware of specific applications of MassWateR outside of our core user base, but our intention of publishing this work in the primary literature was to reach a broader audience and thereby promote transferibility of the software.
+We are confident that the software can be broadly applied given the relatively minor limitations for its use outside of Massachusetts.
+Additionally, the software has been downloaded over 4000 times from CRAN as of this wwriting, which suggests many others have found the software transferable.
 
@@
 
-__Response__:
+**Response**: Please note that the article submission system greatly reduces the quality of the submitted figures at the end of the manuscript.
+The original, high-resolution figures can be viewed by clicking the link on the top of the page for each figure.
+Several are also provided as .svg files, following the journal guidelines.
+Previews for these figures are not provided in the PDF and they can only be viewed by downloading each file.
+
+# References {.unnumbered}

### 2023-09-12 manu-draft.qmd
working on revisions

@@
 Water quality measurements provide the foundation of environmental monitoring programs designed to protect or restore aquatic resources.
-In the United States, these programs are broadly guided by the federal Clean Water Act with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union.
+In the United States, these programs are broadly guided by the federal Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim)) with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
+Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union [Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000, @pollard1998].
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances identified from water quality measurements require additional regulatory action to ensure compliance.
@@
 
+To our knowledge, there are no existing R packages on the Comprehensive R Archive Network ([CRAN](https://cran.r-project.org/)) that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
+However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN [Hydrology](https://cran.r-project.org/web/views/Hydrology.html) Task View).
+In particular, the *dataRetrieval* R package [@DeCicco22] has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
+This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
+The *TADA* R package [@Mullin22] is also currently under development as a resource for for compiling and evaluating data from the WQP.
+*TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP.
+As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.
+Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like *dataRetrieval* by increasing the amount of data that can be accessed through the WQP.
+The *MassWateR* package was developed to provide this benefit.
+
+Other software platforms outside of the R environment provide various services for quality control of water quality data.
+The [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
+Functionality is provided to pre-process and synthesize multiple data streams, manually correct erroneous values, and to visualize results for decision-making.
+A graphical user interface is provided to access the various features of the software as compared to a programmatic approach for building custom routines.
+Moreover, the software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
+Similar platforms are available from companies that manufacture data loggers (e.g., [YSI](https://www.ysi.com/), [HOBO](https://www.onsetcomp.com/products/software/hoboware)), all of which are specific to the monitoring equipment and not broadly transferable.
+Alternative publicly funded software and data services are provided by the Consortium of Universities for the Advancement of Hydrologic Science ([CUAHSI](https://www.cuahsi.org/data-services/solutions)).
+Services provided by CUAHSI include data discovery, archiving, cloud computing, and analysis, with many of the services available in open source environments (e.g., [Python](https://www.python.org/)).
+However, the services provided by CUAHSI are meant to address a variety of different resources and use cases, none of which are immediately related to quality control reporting and data submission to public institutions.
+As such, Specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed.
+
 This paper describes the *MassWateR* package developed to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data for surface waters.
@@
 
-To our knowledge, there are no existing R packages on CRAN that can be used to facilitate QC of water quality data, nor are any available that facilitate submission to existing databases.
-However, there are several that can be used to retrieve and analyze data from existing sources (see the CRAN [Hydrology](https://cran.r-project.org/web/views/Hydrology.html) Task View).
-In particular, the *dataRetrieval* package [@DeCicco22] has been used widely to retrieve data from the WQP, which is the interface for accessing data submitted using WQX.
-This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
-As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.
-Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like *dataRetrieval* by increasing the amount of data that can be accessed through the WQP.
-The *MassWateR* package was developed to provide this benefit.
-
 Users can engage with *MassWateR* to achieve different goals.
@@
 @fig-workflow demonstrates how a user may apply the functions in *MassWateR* once the required data are imported.
-The functions allow a user to engage with their data several ways.
-The first step, QC screening, is often iterative as a user can modify parts of the raw data based on input checks or outliers.
+The functions allow a user to engage with their data in several ways.
+The first step, QC screening, is often iterative as a user can modify parts of the raw data based on messages from the data import functions or checks for outliers.
 The second step can be used to create a QC report for submission to a regulatory agency.
@@
 ![Workflow demonstrating how a user could engage with the *MassWateR* package.
-WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.tif){#fig-workflow width=100% fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
+WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.tif){#fig-workflow width="100%" fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
 
@@
 The following sections describe the basic approach to using functions in *MassWateR* for any of the processes in the workflow.
-The naming convention for the functions is meant to provide users with an intuitive format for understanding what each funcfiletion does and the step of the workflow for which the function applies.
+The naming convention for the functions is meant to provide users with an intuitive format for understanding what each function does and the step of the workflow for which the function applies.
 Although there are some exceptions to this nomenclature, the general format includes a prefix for each function as follows.
@@
 
-* `read`: Read input files
-* `check`: Check input files for formatting issues, used internally to the read functions 
-* `form`: Format input files for downstream functions, used internally to the read functions once the checks have passed
-* `anlz`: Analyze imported data
-* `tab`: Create formatted tables for QC analysis
-* `qc`: QC functions for summarizing QC results, used internally to the table functions
-* `util`: Various utility functions that accomplish routine tasks, possibly useful as standalone functions
+-   `read`: Read input files
+-   `check`: Check input files for formatting issues, used internally to the read functions
+-   `form`: Format input files for downstream functions, used internally to the read functions once the checks have passed
+-   `anlz`: Analyze imported data
+-   `tab`: Create formatted tables for QC analysis
+-   `qc`: QC functions for summarizing QC results, used internally to the table functions
+-   `util`: Various utility functions that accomplish routine tasks, possibly useful as standalone functions
 
@@
 
-* `results`: The results input file
-* `acc`: The data quality objectives file for accuracy
-* `frecom`: The data quality objectives file for frequency and completeness
-* `sites`: The site metadata file
-* `wqx`: The WQX metadata file
+-   `results`: The results input file
+-   `acc`: The data quality objectives file for accuracy
+-   `frecom`: The data quality objectives file for frequency and completeness
+-   `sites`: The site metadata file
+-   `wqx`: The WQX metadata file
 
@@
 The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.
-After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.tif){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width=100%}
+After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).](images/importflow.tif){#fig-importflow fig-alt="Diagram showing pseudocode for importing and fixing a data file with *MassWateR*" width="100%"}
 
@@
 ```
+
 ```         
@@
 In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
-The QC checks for frequency and completeness evaluate if a sufficient number of records in the results file satisfy the accuracy checks and that sufficient QC data have been collected.
+The QC checks for frequency and completeness can be used to evaluate if a sufficient number of records in the results file satisfy the accuracy checks and that sufficient QC data have been collected.
 The values in the `accdat` and `frecomdat` inputs are collectively described as data quality objectives (DQOs), such that the QC samples in `resdat` must satisfy these objectives to be considered accurate and precise data for use in regulatory or other assessments by water quality professionals.
@@
 
-* *Field Blanks*: Measurements in the field to verify absence of a parameter, i.e., the parameter is not detected by the field method when it is not present
-* *Lab Blanks*: Laboratory samples to verify absence a parameter, i.e., the parameter is not detected by the lab method when it is not present
-* *Field Duplicates*: Duplicate measurements in the field to assess similar values, i.e., precision between measurements is comparable
-* *Lab Duplicates*: Duplicate laboratory samples to assess similar values, i.e., precision between samples is comparable
-* *Calibration Checks*: Measurements in the field to verify an instrument returns a known quantity of a parameter, i.e., to verify accuracy of field sampling equipment
-* *Lab Spikes*: Laboratory samples to verify if the processing equipment returns a known quantity of a parameter, i.e., to verify accuracy of laboratory equipment
+-   *Field Blanks*: Measurements in the field to verify that the parameter is below a certain threshold, e.g., below the detection limit of the field equipment
+-   *Lab Blanks*: Laboratory samples to verify that the parameter is below a certain threshold, e.g., below the detection limit of the laboratory analysis method
+-   *Field Duplicates*: Duplicate measurements in the field to assess the similarity of values, i.e. precision is high
+-   *Lab Duplicates*: Duplicate laboratory samples to assess the similarity of values, i.e., precision is high
+-   *Calibration Checks*: Measurements in the field to verify an instrument returns a known quantity of a parameter, i.e., to verify accuracy of field sampling equipment
+-   *Lab Spikes*: Laboratory samples to verify if the processing equipment returns a known quantity of a parameter, i.e., to verify accuracy of laboratory equipment
 
@@
 ```
+
 ![The first two of sixteen pages of the quality control report created by `qcMWRreview()` that evaluates the results data relative to data quality objectives.
@@
 Parameters shown in red or marked as 'MISS' failed the data quality objectives.
-Users can edit the Word file as needed, e.g., entering the organization name or adding notes.
-](images/qcex.tif){#fig-qcex}
+Users can edit the Word file as needed, e.g., entering the organization name or adding notes.](images/qcex.tif){#fig-qcex}
 
@@
 ```
+
 ```{r}
@@
 
-The cells in red show that four of the QC checks for three of the parameters did not meet the accuracy DQOs.
+The cells in red in Table 3 show that four of the QC checks for three of the parameters did not meet the accuracy DQOs.
 All other parameters and checks in green had enough QC checks to satisfy the DQOs (note that the table colors are color-blind friendly).
@@
 In the above example, the threshold line applies to class A or B freshwater environments that support warmwater fisheries, as defined by MADEP.
-Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can de added using additional *ggplot2* functionality (i.e., with `geom_hline()` added to the plot output).
+Threshold lines can be suppressed (`thresh = "none"`) or user-specific thresholds can be added using additional *ggplot2* functionality (i.e., with `geom_hline()` added to the plot output).
 
@@
 Submitting the data to WQX simply requires uploading the output file into the data portal.
-After passing checks within WQX, the data are archived in the portal within 3-5 business days and made accessible to downstream users for public consumption.
+After passing checks within WQX, the data are archived in the portal within 3-5 business days and made accessible for public use.
 
@@
 We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments and WQX staff at USEPA for consult on submitting data formatted with *MassWateR*.
+We also thank two reviewers and the academic editor of the journal for helpful comments that improved the manuscript.
 

### 2023-09-14 manu-draft.qmd
figure 1 as flow diagram

@@
 As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.
-Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like *dataRetrieval* by increasing the amount of data that can be accessed through the WQP.
+Developing a robust tool that can facilitate the upload of data to WQX, in addition to streamlining QC processes, would further the value of packages like *dataRetrieval* and *TADA* by increasing the amount of data that can be accessed through the WQP.
 The *MassWateR* package was developed to provide this benefit.

### 2023-09-18 revision/review-response.qmd
figure 1 as flow diagram
adding references

@@
 
-"The *TADA* R package [@Mullin22] is also currently under development as a resource for for compiling and evaluating data from the WQP.
+"The *TADA* R package [@Mullin22] is also currently under development as a resource for compiling and evaluating data from the WQP.
 *TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP."
@@
 "Other software platforms outside of the R environment provide various services for quality control of water quality data.
-The [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
+For example, the [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
 Functionality is provided to pre-process and synthesize multiple data streams, manually correct erroneous values, and to visualize results for decision-making.
-A graphical user interface is provided to access the various features of the software as compared to a programmatic approach for building custom routines.
+A graphical user interface is provided to access the various features of the software, as compared to a programmatic approach for building custom routines.
 Moreover, the software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
@@
 However, the services provided by CUAHSI are meant to address a variety of different resources and use cases, none of which are immediately related to quality control reporting and data submission to public institutions.
-As such, Specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed."
+As such, specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed."
 
@@
 **Response**: We have added citations where needed.
-Specifically, line 26 includes a link to a description of the US Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim), note that there is no citation provided in the references because this is legislative code), line 29 includes a citation to the European Water Framework Directive [Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000, @pollard1998],
+
+Line 26 includes a link to a description of the US Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim), note that there is no citation provided in the references because this is legislative code).
+
+Line 29 includes a citation to the European Water Framework Directive [Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000, @pollard1998]
+
+Line 40 includes the following citations: @kinzelman2003, @Wagner06, @zhang2006.
+
+Lines 521-547 include ciitations:
 
@@
 
-**Response**:
+**Response**: Figure 1 has been reconfigured as a flow diagram, although emphasis remains in the text that a user can engage with the package using one to any of the steps in the diagram.
 
@@
 We are confident that the software can be broadly applied given the relatively minor limitations for its use outside of Massachusetts.
-Additionally, the software has been downloaded over 4000 times from CRAN as of this wwriting, which suggests many others have found the software transferable.
+Additionally, the software has been downloaded over 4000 times from CRAN as of this writing, which suggests many others have found the software transferable.
 

### 2023-09-18 manu-draft.qmd
adding references

@@
 In the United States, these programs are broadly guided by the federal Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim)) with the singular goal of restoring and maintaining the chemical, physical, and biological integrity of the nation's surface waters.
-Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union [Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000, @pollard1998].
+Similarly, the Water Framework Directive provides a legislative foundation for the protection of aquatic resources in member states of the European Union (Directive 2000/60/EC of the European Parliament and of the Council of 23 October 2000) [@pollard1998].
 Numeric standards that define critical thresholds for protecting recreational, aquatic life, industrial, navigational, and consumptive uses of the resource are often established by government agencies, such that exceedances identified from water quality measurements require additional regulatory action to ensure compliance.
@@
 Many state or regional institutions that assess water quality rely on decentralized data sources, often combining datasets from local watershed groups or participatory science programs rather than a single database that contains adequate coverage of all areas of interest [@Buytaert14; @Kelly22].
-Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control (QC) requirements.
+Use of these monitoring data in a regulatory context is not possible unless standard operating procedures are adopted and the data fulfill quality control (QC) requirements [e.g., @kinzelman2003; @Wagner06; @zhang2006].
 
@@
 This package leverages a robust API to query existing water quality data in standardized format provided by the WQP.
-The *TADA* R package [@Mullin22] is also currently under development as a resource for for compiling and evaluating data from the WQP.
+The *TADA* R package [@Mullin22] is also currently under development as a resource for compiling and evaluating data from the WQP.
 *TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP.
@@
 Other software platforms outside of the R environment provide various services for quality control of water quality data.
-The [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
+For example, the [Aquarius](https://aquaticinformatics.com/products/aquarius-environmental-water-data-management/) software environment is a proprietary resource for managing hydrologic and water quality data and is used by several private and public institutions.
 Functionality is provided to pre-process and synthesize multiple data streams, manually correct erroneous values, and to visualize results for decision-making.
-A graphical user interface is provided to access the various features of the software as compared to a programmatic approach for building custom routines.
+A graphical user interface is provided to access the various features of the software, as compared to a programmatic approach for building custom routines.
 Moreover, the software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
@@
 However, the services provided by CUAHSI are meant to address a variety of different resources and use cases, none of which are immediately related to quality control reporting and data submission to public institutions.
-As such, Specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed.
+As such, specific software solutions to address these needs and that leverage existing tools available in a rich open-source environment are clearly needed.
 
@@
 ![Workflow demonstrating how a user could engage with the *MassWateR* package.
-WQX: Water Quality Exchange; QC: Quality Control.](images/workflow.tif){#fig-workflow width="100%" fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
+DQO: Data Quality Objectives; QC: Quality Control; WQX: Water Quality Exchange.](images/workflow.tif){#fig-workflow width="100%" fig-alt="Workflow diagram showing four ways to engage with *MassWateR*"}
 

### 2023-09-19 revision/review-response.qmd
more revisions, added supplement

@@
 bibliography: ../refs.bib
-csl: ../plos-one.csl
 
@@
 
-Lines 521-547 include ciitations:
+Lines 521-537 include the following citations: @Meyer22, @whitehead2007, @list2017, @Wickham16
+
+Additional citations were added later in the discussion: @DeCicco22, @Wagner06
 
@@
 
-**Response**:
+**Response**: A supplement file was created to accompany the main manuscript, including tables for the parameters used by MassWateR and the sample files included with the package for the data quality objectives for accuracy, frequency, and completeness.
+Also note that the specific QC checks used by the package were previously described in the main text (e.g., lab spikes, lab blanks, etc.).
 

### 2023-09-19 manu-draft.qmd
more revisions, added supplement

@@
 For the former approach, the beginning of a script for using the package could appear as follows.
-Example files included with the package are imported, whereas a user will specify paths to their own files.
+Example files included with the package are imported (see the supplement for the example data quality objective files for accuracy, frequency and completeness), whereas a user will specify paths to their own files.
 
@@
 A final note about the data inputs is that many types of water quality measurements can be included for analysis, although the package is currently limited to working with discrete samples as compared to data from continuous monitoring equipment.
-The `paramsMWR` dataset included with *MassWateR* provides a lookup table of the parameters that can be used with the package.
+The `paramsMWR` dataset included with *MassWateR* provides a lookup table of the parameters that can be used with the package (see supplement).
 On data import, this dataset is referenced to ensure that only relevant parameters are included and that appropriate units of measurement are provided.
@@
 
-The quality control functions in *MassWateR* are designed to create a single report that compares the water quality data in the results file (`resdat`) to data quality objectives in the accuracy (`accdat`) and frequency and completeness (`frecomdat`) files.
+The quality control functions in *MassWateR* are designed to create a single report that compares the water quality data in the results file (`resdat`) to data quality objectives in the accuracy (`accdat`, see the supplement for the sample file included with the package) and frequency and completeness (`frecomdat`, see the supplement for the sample file included with the package) files.
 In general, the QC checks for accuracy evaluate if laboratory and field duplicates, blanks, or spikes are within acceptable ranges.
@@
 
-To ensure that *MassWateR* is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice was established during package development and following its initial release on CRAN (January, 2023).
-This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package.
+To ensure that *MassWateR* is a known resource for potential users and to encourage its use for QC reporting, analysis, and data submission, a community of practice [e.g., @Meyer22] was established during package development and following its initial release on CRAN (January, 2023).
+This included several beta testing and training workshops to gather feedback on anticipated data analysis workflows and to educate potential users on appropriate use of the package [@whitehead2007; @list2017].
 Many users have not previously been exposed to R for data analysis and a substantial portion of the trainings included an [introduction](https://massbays-tech.github.io/intro-to-r/) to R, as well as *MassWateR*.
 Emphasis was placed on simple use of the core functions, as opposed to developing custom workflows that combined core R functions with *MassWateR*.
-However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as *ggplot2* to create additional visualizations for modifying the existing analysis plots in *MassWateR*.
+However, users were encouraged to learn how to extend the use of the package by leveraging additional R packages, such as *ggplot2* [@Wickham16] to create additional visualizations for modifying the existing analysis plots in *MassWateR*.
 For example, a [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html) was included on the package website to demonstrate how these plots can be modified for custom output using *ggplot2*.
 Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., StackOverflow) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
+This approach followed the model used by other popular web forums (e.g., \[StackOverflow\](https://stackoverflow.com/)) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
 
@@
 This enhancement would require the extraction of existing data included in the WQP, which would not be significantly challenging given the robust web retrieval tools already available.
-Existing R packages leverage these tools (e.g., *dataRetrieval*) and a similar approach could be used by *MassWateR*.
-A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed *in situ*.
+Existing R packages leverage these tools [e.g., *dataRetrieval,* @DeCicco22] and a similar approach could be used by *MassWateR*.
+A second and more challenging enhancement would be the ability to work with continuous monitoring data collected at high temporal resolution with equipment deployed *in situ* [e.g., @Wagner06].
 These data present additional challenges not encountered with routine samples collected at longer time intervals, including increased data volume and additional QC needs [@Wagner06; @Horsburgh15].

### 2023-09-19 supplement.qmd
more revisions, added supplement

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* MassWateR: Improving quality control, analysis, and sharing of water quality data"
bibliography: refs.bib
csl: plos-one.csl
crossref:
  fig-title: Fig
  fig-prefix: Fig 
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Benjamen Wetherill:
      email: bwetherill@acasak.com 
      institute: [ACA]
      correspondence: false
  - Jillian Carr:
      email: Jillian.Carr@umb.edu
      institute: [MASS]
      correspondence: false

institute:
  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida, USA
  - ACA: ACASAK Consulting, Boston, Massachusetts USA
  - MASS: Massachusetts Bays National Estuary Partnership, Boston, Massachusetts, USA

filters: 
  - templates/scholarly-metadata.lua
  - templates/author-info-blocks.lua

knitr:
  opts_chunk: 
    fig.path: 'images/'

execute: 
  echo: false
  warning: false
  message: false
  ft.keepnext: false
  ft.align: left
  fig-format: svg
  fig-dpi: 300
---

```{r}
#| include: false
library(MassWateR)
library(dplyr)
library(here)
```

```{r}
#| tbl-cap: "Complete list of parameters and units that can be used with MassWateR.  Parameters can be named using the `Simple Parameter` or the `WQX Parameter` convention.  Only one unit of measure can be used per parameter. WQX: Water Quality Exchange."
#| label: tbl-params
paramsMWR %>% 
  select(`Simple Parameter`, `WQX Parameter`, `Units of measure`) %>% 
  arrange(`Simple Parameter`, .locale = 'en') %>% 
  knitr::kable(.)
```

```{r}
#| tbl-cap: "The sample file included with MassWateR for the data quality objectives for accuracy."
#| label: tbl-acc

accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
accdat <- readMWRacc(accpth, warn = F, runchk = F)
knitr::kable(accdat)
```

```{r}
#| tbl-cap: "The sample file included with MassWateR for the data quality objectives for frequency and completeness."
#| label: tbl-frecom
frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
frecomdat <- readMWRfrecom(frecompth, warn = F, runchk = F)
knitr::kable(frecomdat)
```

### 2023-09-21 revision/review-response.qmd
revisions done, need to proof

@@
 
-**Response**:
+**Response**: We have verified that our manuscript adheres to the utility, validation, and availability criteria for the article type. Below are descriptions of how these criteria are met:
+
+*Utility:* The MassWateR package provides needed utility for the community, as established in the introductory text.
+both in the original submission and the additions provided in the revision.
+In particular, the package provides a repeatable and efficient means for generating QC reports to ensure the water quality data are of sufficient accuracy and precision needed for integration into larger databases (i.e., WQX).
+As noted, we are unaware of any existing tools that provide this functionality.
+
+*Validation*: MassWateR achieves its intended uses as verified by adoption by the larger community of practice, detailed in the text.
+In addition, the package has been downloaded over 4000 times since its availability on CRAN in January 2023.
+This provides a robust indication that those outside of our community of practice are also applying MassWateR for its intended use.
+Finally, we describe the possible applications for the package in detail in the manuscript (e.g., QC report generation including a figure showing a portion of the report, submission to WQX, etc.).
+
+*Availability*: The software is entirely open -source and available for download through [CRAN](https://cran.r-project.org/package=MassWateR), [GitHub](https://github.com/massbays-tech/MassWateR), and [R-Universe](https://fawda123.r-universe.dev/MassWateR) Numerous links and citations are included throughout the text.
+The license applied to MassWateR is CC0 1.0, making the code available to the world-wide public domain.
 

### 2023-09-21 revision/review-response.qmd
proof revisions

@@
 
-We sincerely thank the academic editor and two reviewers for providing thoughtful comments on our manuscript.
+**Response**: We sincerely thank the academic editor and two reviewers for providing thoughtful comments on our manuscript.
 We provide a point-by-point response to these comments below.
@@
 As noted in the original submission on line 88, there are no other R packages that we are aware of that provide similar functionality.
-As such, there is no basis of comparison of MassWateR to determine relative strengths/weakness with other packages.
+As such, there is no basis of comparison for MassWateR to determine relative strengths/weakness with other packages.
 However, we have added text describing other R packages that are somewhat related and have included a description of software packages outside of the R environment to provide a more comprehensive discussion of alternatives.
@@
 "The *TADA* R package [@Mullin22] is also currently under development as a resource for compiling and evaluating data from the WQP.
-*TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP."
+*TADA* is similar to *dataRetrieval* in that it can be used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP."
 
@@
 A graphical user interface is provided to access the various features of the software, as compared to a programmatic approach for building custom routines.
-Moreover, the software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
+The software is not open-source, which implicitly limits its development to a core set of maintainers and is not freely accessible to the broader community [e.g., @schrape2017a].
 Similar platforms are available from companies that manufacture data loggers (e.g., [YSI](https://www.ysi.com/), [HOBO](https://www.onsetcomp.com/products/software/hoboware)), all of which are specific to the monitoring equipment and not broadly transferable.
@@
 
-Line 26 includes a link to a description of the US Clean Water Act ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim), note that there is no citation provided in the references because this is legislative code).
+Line 26 includes a link to a description of the US Clean Water Act legislation ([33 USC § 1251 et seq.](https://uscode.house.gov/view.xhtml?path=/prelim@title33/chapter26&edition=prelim), note that there is no citation provided in the references because this is legislative code).
 
@@
 
-**Response**: Figure 1 has been reconfigured as a flow diagram, although emphasis remains in the text that a user can engage with the package using one to any of the steps in the diagram.
+**Response**: Figure 1 has been reconfigured as a flow diagram, although emphasis remains in the text that a user does not have to engage in all steps of the workflow.
 
@@
 
-*Utility:* The MassWateR package provides needed utility for the community, as established in the introductory text.
-both in the original submission and the additions provided in the revision.
-In particular, the package provides a repeatable and efficient means for generating QC reports to ensure the water quality data are of sufficient accuracy and precision needed for integration into larger databases (i.e., WQX).
+*Utility:* The MassWateR package provides needed utility for the community, as established in the introductory text, both in the original submission and the additions provided in the revision.
+In particular, the package provides a repeatable and efficient means for generating QC reports to ensure water quality data are of sufficient accuracy and precision needed for integration into larger databases (i.e., WQX) or additional applications (e.g., regulatory, assessment).
 As noted, we are unaware of any existing tools that provide this functionality.
@@
 
-*Availability*: The software is entirely open -source and available for download through [CRAN](https://cran.r-project.org/package=MassWateR), [GitHub](https://github.com/massbays-tech/MassWateR), and [R-Universe](https://fawda123.r-universe.dev/MassWateR) Numerous links and citations are included throughout the text.
+*Availability*: The software is entirely open-source and available for download through [CRAN](https://cran.r-project.org/package=MassWateR), [GitHub](https://github.com/massbays-tech/MassWateR), and [R-Universe](https://fawda123.r-universe.dev/MassWateR) Numerous links and citations are included throughout the text.
 The license applied to MassWateR is CC0 1.0, making the code available to the world-wide public domain.
@@
 This information was provided in the discussion on lines 538-556, where specific considerations were noted for how users could apply the software to novel datasets.
-Truthfully, we are not yet aware of specific applications of MassWateR outside of our core user base, but our intention of publishing this work in the primary literature was to reach a broader audience and thereby promote transferibility of the software.
+Truthfully, we are not yet aware of specific applications of MassWateR outside of our core user base, but our intention of publishing this work in the primary literature was to reach a broader audience and thereby promote transferability of the software.
 We are confident that the software can be broadly applied given the relatively minor limitations for its use outside of Massachusetts.

### 2023-09-21 manu-draft.qmd
proof revisions

@@
 The *TADA* R package [@Mullin22] is also currently under development as a resource for compiling and evaluating data from the WQP.
-*TADA* is similar to *dataRetrieval* in that it can used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP.
+*TADA* is similar to *dataRetrieval* in that it can be used for importing data, but the package is also expected to provide more comprehensive methods for cleaning, filtering, and processing data using the rich qualifier codes provided by WQP.
 As such, data retrieval using existing web services is much simpler than data submission, as data formatting requirements do not apply when retrieving data.

### 2023-09-26 manu-draft.qmd
resubmitted

@@
   ft.align: left
-  fig-format: svg
+  fig-format: tiff
   fig-dpi: 300
@@
 Further, a [community forum](https://massbays.discourse.group/c/masswater-r-tools/5) was created as a resource for users to post questions about the package and for others to view the discussion if similar issues were encountered.
-This approach followed the model used by other popular web forums (e.g., \[StackOverflow\](https://stackoverflow.com/)) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
+This approach followed the model used by other popular web forums (e.g., [StackOverflow](https://stackoverflow.com/)) for troubleshooting software issues by minimizing duplication of topics through sharing solutions in a public forum.
 

### 2023-10-08 revision2/review-response.qmd
revision2 resubmitted

---
format: 
  docx:
    reference-doc: response_styles.docx
bibliography: ../refs.bib

execute: 
  echo: false
  warning: false
  message: false
---

```{r}
#| echo: false
#| cache: false
#| eval: true
library(MassWateR)

#| results: 'hide'
#| echo: true
# import results data
respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
resdat <- readMWRresults(respth, warn = F, runchk = F)

# import accuracy data
accpth <- system.file("extdata/ExampleDQOAccuracy.xlsx", package = "MassWateR")
accdat <- readMWRacc(accpth, warn = F, runchk = F)

# import frequency and completeness data
frecompth <- system.file("extdata/ExampleDQOFrequencyCompleteness.xlsx", package = "MassWateR")
frecomdat <- readMWRfrecom(frecompth, warn = F, runchk = F)

# import site data
sitpth <- system.file("extdata/ExampleSites.xlsx", package = "MassWateR")
sitdat <- readMWRsites(sitpth, runchk = F)

# import WQX metadata
wqxpth <- system.file("extdata/ExampleWQX.xlsx", package = "MassWateR")
wqxdat <- readMWRwqx(wqxpth, warn = F, runchk = F)

# a list of input data frames
fsetls <- list(res = resdat, acc = accdat, frecom = frecomdat, sit = sitdat, wqx = wqxdat)
```

**Response**: We again thank the reviewers for evaluating our manuscript. Please see our responses below. Note that reviewer 1 suggested publication without further comment.

## Reviewer 2

The authors have improved over the previous version, but there are still some issues that need to be revised, the main comments are as follows:

1.  It is recommended to add information about the data of the mean values as well as information about the true values in Figures 3 and 6, so that the reader can understand more information;

    **Response**: Figure 3 shows boxplot distributions of selected parameters to aid package users in identifying potential outlier observations. Boxplots are common visualization tools that can quickly demonstrate central tendency and spread of a group of observations [@tukey1977; @mcgill1978], in addition to outliers as intended by the plot in Figure 3. Therefore, we do not consider it necessary to show mean values in this plot. Further, Figure 6 currently shows mean values. The values shown are considered "true" as these are sampled values from *in situ* or laboratory-based methods and not those from modeled or other predictive techniques.

2.  The quality of Figure 4 is very low and it is not even possible to see any content information;

    **Response**: As noted in our responses to comments in the previous revision, the figure quality is substantially reduced in the PDF that is generated by the article submission system. High-resolution figures were included with the submission and can be downloaded by selecting the link that appears at the top-right of each page for each figure.

3.  The dimensions of Figure 8 are recommended to use vertical arrangement; and the scale labeling form is not standardized; the DO color labeling colors of the sites are more distinguishable;

    **Response**: The figures produced by *MassWateR* are all `ggplot` class objects and can be modified using conventional *ggplot2* functions. A vertical arrangement can be achieved as follows, assuming the reviewer means that the legend should appear above and arranged horizontally on the plot.

    ```{r}
    #| fig-height: 5
    #| fig-width: 5
    #| echo: true
    #| out-width: '95%'
    #| fig-align: 'center'
    library(ggplot2)

    anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium") + 
      theme(legend.position = 'top')
    ```

    The online website includes a vignette about modifying *MassWateR* plots with *ggplot2* code. We have added the following text on line 445 to make this clear.

    "Additionally, all plots returned by *MassWateR* are `ggplot` class objects and can be modified accordingly using conventional *ggplot2* functions (see the website [vignette](https://massbays-tech.github.io/MassWateR/articles/modifying.html))."

4.  How do the predictions of water quality parameters in this study compare with other common models?

    **Response**: The functions in *MassWateR* rely on data collected *in situ* and there are no aspects related to predictive modeling included in the package. The primary goals of *MassWateR* are to improve how environmental professionals perform quality control, analysis, and sharing of monitoring data. As such, the intent is to support the use of data for environmental decision-making.  No predictions are provided by the package.

5.  Some recent deep learning models for water quality prediction should be mentioned, e.g., 10.1016/j.ejrh.2023.101331; 10.1007/s11783-023-1688-y; 10.1016/j.ecolind.2023.109882; 10.1016/j.jhydrol.2023. 129649.

    **Response**: Please see our response to the previous comment.

# References {.unnumbered}
